---
title: "02_Calculating_Posterior_Distributions"
author: "Arthur M. Albuquerque"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
          code_folding: show
          toc: yes
          toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this document, we will provide the rationale underlying the **effect sizes**
used in our project. We will focus on the **mortality outcome**.

First, we will load the data and calculate the **log-odds ratio** of the RECOVERY
trial and its corresponding prior. Then, we will calculate the
**posterior distributions** in log-odds ratio scale. Lastly, we will derive the
**risk differences** from these posterior distributions.

If you are not interested in the code, you can select the "Hide all code" option
on the upper-right corner.

```{r}
# Load packages

# Ensures the package "pacman" is installed
if (!require("pacman")) install.packages("pacman")

# p_load() installs (if necessary) and loads the following packages

pacman::p_load(plyr, # for the Varying baseline risk calculations
               magrittr, # same as above
               rio, # to import/export files
               tidyverse, # Data wrangling and plotting
               kableExtra, # To create tables
               flextable, # To create tables
               here, # To find file paths within R project
               metafor, # To create priors from meta-analysis
               janitor, # To change column names
               ggdist, # To plot distributions
               patchwork # To arrange plots
               )

# Load data on respiratory support subgroups

d1 = import((here("02_preprint", "output", "data", # file path
                   "respiratory-data.csv")),           # file name
             header = T)

# Load data on corticosteroids subgroups

d2 = import(here("02_preprint", "data", # file path
                            "corticosteroids_subgroup_extracted-data.xlsx")) 

d2 = clean_names(d2)
```

# Log-odds ratio, then odds ratio, then risk difference

Our ultimate goal in this project is to report posterior distributions of risk
difference (RD) for each subgroup. We will eventually compile multiple studies
in our analyses and each have their own baseline risk (BR). Notably, RD is
intrinsically related to BR. Therefore, different studies with
distinct RDs are not comparable between each other.

To overcome this limitation regarding RD, we have decided to use a fixed
BR for each subgroup. We will use the BR in the respective
control group from the RECOVERY trial. 

[Doi et al.](https://www.jclinepi.com/article/S0895-4356(20)31171-9/fulltext)
stated that RD should be derived from the odds ratio (OR). Thus, in combination
with a fixed BR, we will calculate RDs from OR. Here is the formula provided by
Doi et al., where $R D$ is risk difference, $B R$ is baseline risk from the
control group (no-exposure) and $O R$ is odds ratio:

$$R D=\frac{B R \cdot \left(B R-1\right)\cdot \left(O R-1\right)}{B R \cdot O R-B R+1}$$

First, we will calculate the log-odds ratio for the RECOVERY trial and its
corresponding prior in each subgroup.

## Use of corticosteroids subgroups

### Not using 

First, let's calculate and visualize the **log-odds ratio** from the
RECOVERY trial.

```{r}

logOR_recovery_not_using =
  rma(
    # Outcome
    measure = "OR", # Log-odds ratio
    
    # Tocilizumab group
    ai = events_toci,
    n1i = total_toci,

    # Control group
    ci = events_control,
    n2i = total_control,
    
    data = d2 %>% filter(outcome == "mortality",
                         corticosteroids == 0,
                         trial == "RECOVERY"),
    
     method = "REML",

    slab = paste(trial)
  )

forest(logOR_recovery_not_using)
```

Now, let's calculate and visualize the **log-odds ratio** from the
other trials. The pooled result from this random-effect meta-analysis will be
used as the estimate for the distribution of prior regarding this subgroup.

```{r}

# Simple oxygen

logOR_prior_not_using =
  rma(
    # Outcome
    measure = "OR", # Log-odds ratio
    
    # Tocilizumab group
    ai = events_toci,
    n1i = total_toci,

    # Control group
    ci = events_control,
    n2i = total_control,
    
    data = d2 %>% filter(outcome == "mortality",
                         corticosteroids == 0,
                         trial != "RECOVERY"),
    
     method = "REML",

    slab = paste(trial)
  )

forest(logOR_prior_not_using)
```

### Using 

Let's calculate and visualize the **log-odds ratio** from the
RECOVERY trial.

```{r}

logOR_recovery_using =
  rma(
    # Outcome
    measure = "OR", # Log-odds ratio
    
    # Tocilizumab group
    ai = events_toci,
    n1i = total_toci,

    # Control group
    ci = events_control,
    n2i = total_control,
    
    data = d2 %>% filter(outcome == "mortality",
                         corticosteroids == 1,
                         trial == "RECOVERY"),
    
     method = "REML",

    slab = paste(trial)
  )

forest(logOR_recovery_using)
```

Now, let's calculate and visualize the **log-odds ratio** from the
other trials. The pooled result from this random-effect meta-analysis will be
used as the estimate for the distribution of prior regarding this subgroup.

```{r}

# Simple oxygen

logOR_prior_using =
  rma(
    # Outcome
    measure = "OR", # Log-odds ratio
    
    # Tocilizumab group
    ai = events_toci,
    n1i = total_toci,

    # Control group
    ci = events_control,
    n2i = total_control,
    
    data = d2 %>% filter(outcome == "mortality",
                         corticosteroids == 1,
                         trial != "RECOVERY"),
    
     method = "REML",

    slab = paste(trial)
  )

forest(logOR_prior_using)
```

## Respiratory support subgroups

### Simple oxygen only

Let's calculate and visualize the **log-odds ratio** from the
RECOVERY trial.

```{r}

logOR_recovery_simple =
  rma(
    # Outcome
    measure = "OR", # Log-odds ratio
    
    # Tocilizumab group
    ai = events_toci,
    n1i = total_toci,

    # Control group
    ci = events_control,
    n2i = total_control,
    
    data = d1 %>% filter(outcome == "mortality",
                         oxygen == "simple oxygen",
                         trial == "RECOVERY"),
    
     method = "REML",

    slab = paste(trial)
  )

forest(logOR_recovery_simple)
```

Now, let's calculate and visualize the **log-odds ratio** from the
other trials. The pooled result from this random-effect meta-analysis will be
used as the estimate for the distribution of prior regarding this subgroup.

```{r}

logOR_prior_simple =
  rma(
    # Outcome
    measure = "OR", # Log-odds ratio
    
    # Tocilizumab group
    ai = events_toci,
    n1i = total_toci,

    # Control group
    ci = events_control,
    n2i = total_control,
    
    data = d1 %>% filter(outcome == "mortality",
                         oxygen == "simple oxygen",
                         trial != "RECOVERY"),
    
     method = "REML",

    slab = paste(trial)
  )

forest(logOR_prior_simple)
```

### Non-invasive ventilation

Let's calculate and visualize the **log-odds ratio** from the
RECOVERY trial.

```{r}

logOR_recovery_noninvasive =
  rma(
    # Outcome
    measure = "OR", # Log-odds ratio
    
    # Tocilizumab group
    ai = events_toci,
    n1i = total_toci,

    # Control group
    ci = events_control,
    n2i = total_control,
    
    data = d1 %>% filter(outcome == "mortality",
                         oxygen == "non-invasive ventilation",
                         trial == "RECOVERY"),
    
     method = "REML",

    slab = paste(trial)
  )

forest(logOR_recovery_noninvasive)
```

Now, let's calculate and visualize the **log-odds ratio** from the
other trials. The pooled result from this random-effect meta-analysis will be
used as the estimate for the distribution of prior regarding this subgroup.

```{r}

logOR_prior_noninvasive =
  rma(
    # Outcome
    measure = "OR", # Log-odds ratio
    
    # Tocilizumab group
    ai = events_toci,
    n1i = total_toci,

    # Control group
    ci = events_control,
    n2i = total_control,
    
    data = d1 %>% filter(outcome == "mortality",
                         oxygen == "non-invasive ventilation",
                         trial != "RECOVERY"),
    
     method = "REML",

    slab = paste(trial)
  )

forest(logOR_prior_noninvasive)
```

### Invasive mechanical ventilation

Let's calculate and visualize the **log-odds ratio** from the
RECOVERY trial.

```{r}

logOR_recovery_invasive =
  rma(
    # Outcome
    measure = "OR", # Log-odds ratio
    
    # Tocilizumab group
    ai = events_toci,
    n1i = total_toci,

    # Control group
    ci = events_control,
    n2i = total_control,
    
    data = d1 %>% filter(outcome == "mortality",
                         oxygen == "invasive ventilation",
                         trial == "RECOVERY"),
    
     method = "REML",

    slab = paste(trial)
  )

forest(logOR_recovery_invasive)
```

Now, let's calculate and visualize the **log-odds ratio** from the
other trials. The pooled result from this random-effect meta-analysis will be
used as the estimate for the distribution of prior regarding this subgroup.

```{r}

logOR_prior_invasive =
  rma(
    # Outcome
    measure = "OR", # Log-odds ratio
    
    # Tocilizumab group
    ai = events_toci,
    n1i = total_toci,

    # Control group
    ci = events_control,
    n2i = total_control,
    
    data = d1 %>% filter(outcome == "mortality",
                         oxygen == "invasive ventilation",
                         trial != "RECOVERY"),
    
     method = "REML",

    slab = paste(trial)
  )

forest(logOR_prior_invasive)
```

## Calculating Posterior Distributions

Now, we will first calculate the posterior distributions from log-odds ratio.
We will combine mean and variance from likelihood (RECOVERY) and prior in a
conjugate normal analysis to get the posterior distributions
([Spiegelhalter et al., 2004](https://onlinelibrary.wiley.com/doi/book/10.1002/0470092602)).

Assuming each prior is normal distributed

$$N(\theta,\sigma^2)$$

and so is the data (likelihood).

$$N(\hat{\theta},\hat{\sigma}^2)$$
The mean and variance of the posterior distributions can be estimated by the
following formulas:

* Mean

$$\frac{\frac{\theta}{\sigma^2} + \frac{\hat\theta}{\hat\sigma^2}}{\frac{1}{\sigma^2}+\frac{1}{\hat\sigma^2}}$$

* Variance 

$$\frac{1}{\frac{1}{\sigma^2}+\frac{1}{\hat\sigma^2}}$$

We will first load custom functions. You can find these in the
[GitHub repository](https://github.com/arthur-albuquerque/tocilizumab_reanalysis/tree/master/02_preprint/script)
of this project.

```{r}
## Load custom functions

# To generate normal conjugate posterior probabilities

source(here("02_preprint", "script", "functions", "analyses", # file path
            "conjugate_normal_posterior.R"))                     # file name

# To generate posterior probabilities with an evidence-based prior
# (it requires "conjugate_normal_posterior.R" )

source(here("02_preprint", "script", "functions", "analyses", # file path
            "normal_approximation_logOR.R"))                     # file name

# To generate posterior probabilities with multiple priors
# (it requires "conjugate_normal_posterior.R" )

source(here("02_preprint", "script", "functions", "analyses", # file path
            "logOR_normal_approximation_multiple_priors.R"))     # file name

# To compile all posteriors into a tibble

source(here("02_preprint", "script", "functions", "analyses", # file path
            "tibble_all_posteriors_logOR.R"))                      # file name
```


```{r include=FALSE}
### Apply custom functions

## Use of corticosteroids

# Not using
posterior_not_using_death = normal_approximation_logOR(
  logOR_recovery_not_using, # Data object with RECOVERY data
  logOR_prior_not_using, # Output from the rma() in the previous code chunk

  posterior_not_using_death # Repeat the name of the object you are creating
)

# Using
posterior_using_death = normal_approximation_logOR(
  logOR_recovery_using, # Data object with RECOVERY data
  logOR_prior_using, # Output from the rma() in the previous code chunk

  posterior_using_death # Repeat the name of the object you are creating
)

## Respiratory support

# Simple oxygen only
posterior_simple_death = normal_approximation_logOR(
  logOR_recovery_simple, # Data object with RECOVERY data
  logOR_prior_simple, # Output from the rma() in the previous code chunk

  posterior_simple_death # Repeat the name of the object you are creating
)

# Non-invasive ventilation
posterior_noninvasive_death = normal_approximation_logOR(
  logOR_recovery_noninvasive, # Data object with RECOVERY data
  logOR_prior_noninvasive, # Output from the rma() in the previous code chunk

  posterior_noninvasive_death # Repeat the name of the object you are creating
)

# Invasive mechanical ventilation
posterior_invasive_death = normal_approximation_logOR(
  logOR_recovery_invasive, # Data object with RECOVERY data
  logOR_prior_invasive, # Output from the rma() in the previous code chunk

  posterior_invasive_death # Repeat the name of the object you are creating
)

```

We also [pre-planned](https://osf.io/qhvcp/) to perform **sensitivity analyses**
using different priors. In addition to the ones calculated above (hereafter,
**evidence-based priors**), we will also generate posterior distributions using
four extra priors: **non-informative, skeptical, optimistic and pessimistic**.

The non-informative and skeptical priors' mean equals to $0$ ( = *log(1)* ).
The optimistic prior's mean equals to $-0.223$ ( = *log(0.8)* ).
The pessimistic prior's mean equals to $0.223$ ( = *log(1.25)* ).

We decided to use *log(0.8)* as the mean for the **optimistic** prior because the
RECOVERY trial was designed to be well-powered for 20% relative risk reduction.
In turn, we used the symmetrical opposite from *log(0.8)* in the log scale for
the pessimistic mean, which is *log(1.25)*.

Of note, these priors are normally distributed, thus they are described by a mean
and a variance. We also pre-planned to use the respective **evidence-based prior's**
**variance** for the variance in all other prior distributions, but the
non-informative. Instead, the latter will have a variance of $10,000$.

Now, let's calculate the posterior distributions using these extra priors. 

```{r message=FALSE, warning=FALSE}
## Use of corticosteroids

# Not using
posteriors_not_using_death =
  logOR_normal_approximation_multiple_priors(
  # Data object with evidence-based posterior from normal_approximation()
  posterior_not_using_death, 
  "mortality", # Outcome (within quotes)
  posteriors_not_using_death # Name for the final output with data+prior+posterior
  )

# Using
posteriors_using_death =
  logOR_normal_approximation_multiple_priors(
  # Data object with evidence-based posterior from normal_approximation()
  posterior_using_death, 
  "mortality", # Outcome (within quotes)
  posteriors_using_death # Name for the final output with data+prior+posterior
  )

## Respiratory support

# Simple oxygen only
posteriors_simple_death =
  logOR_normal_approximation_multiple_priors(
  # Data object with evidence-based posterior from normal_approximation()
  posterior_simple_death, 
  "mortality", # Outcome (within quotes)
  posteriors_simple_death # Name for the final output with data+prior+posterior
  )

# Non-invasive ventilation
posteriors_noninvasive_death =
  logOR_normal_approximation_multiple_priors(
  # Data object with evidence-based posterior from normal_approximation()
  posterior_noninvasive_death, 
  "mortality", # Outcome (within quotes)
  posteriors_noninvasive_death # Name for the final output with data+prior+posterior
  )

# Invasive mechanical ventilation
posteriors_invasive_death =
  logOR_normal_approximation_multiple_priors(
  # Data object with evidence-based posterior from normal_approximation()
  posterior_invasive_death, 
  "mortality", # Outcome (within quotes)
  posteriors_invasive_death # Name for the final output with data+prior+posterior
  )

```

```{r include=FALSE}
## Save 

# save(posteriors_not_using_death,
#      posteriors_using_death,
#      posteriors_simple_death,
#      posteriors_noninvasive_death,
#      posteriors_invasive_death,
#      
#      file = here("02_preprint", "output", "data", "analyses", # file path
#                  "data_prior_posteriors_mean_sd_death.RData"))   # file name
```


Here is an example from one subgroup:

```{r}
posteriors_not_using_death %>% flextable()
```

Notably, the data (likelihood), priors and posteriors are normal-distributed.
Thus, we will get the mean and variance from each posterior distribution and
draw 100,000 samples. I will store these results in one data-frame per subgroup.

```{r}
## Use of corticosteroids

# Not using
samples_logOR_posteriors_not_using_death = 
  tibble_all_posteriors_logOR(posteriors_not_using_death)

# Using
samples_logOR_posteriors_using_death = 
  tibble_all_posteriors_logOR(posteriors_using_death)

## Respiratory support

# Simple oxygen only
samples_logOR_posteriors_simple_death = 
  tibble_all_posteriors_logOR(posteriors_simple_death)

# Non-invasive ventilation
samples_logOR_posteriors_noninvasive_death = 
  tibble_all_posteriors_logOR(posteriors_noninvasive_death)

# Invasive mechanical ventilation
samples_logOR_posteriors_invasive_death = 
  tibble_all_posteriors_logOR(posteriors_invasive_death)
```

Here is an example of a data-frame using head(), in which there is one sample
per row:

```{r}
samples_logOR_posteriors_not_using_death %>% head() %>% flextable() %>% autofit()
```

### Calculating risk difference

As mentioned before, we will use the formula provided by [Doi et al.](https://www.jclinepi.com/article/S0895-4356(20)31171-9/fulltext)
to calculate the risk difference (RD) from a fixed baseline risk (BR) and odds
ratio (OR).

$$R D=\frac{B R * \left(B R-1\right)* \left(O R-1\right)}{B R*O R-B R+1}$$

In the sections before, we calculated the log-odds ratio for the RECOVEY trial
and prior distributions in each subgroup. We then calculated the posterior
distributions in the log-odds ratio scale. 

Now, we will exponentiate these values to obtain the odds ratio for the
posterior distributions. We will first get the data frames (wide format) from
the section before and transform them into the long format.

```{r}
## Use of corticosteroids

# Not using
samples_posteriors_not_using_death = 
  samples_logOR_posteriors_not_using_death %>% 
  pivot_longer(
    cols = c('Non-informative':'Pessimistic'),
    names_to = "Underlying_Prior", values_to = "log(OR)"
  )

# Using
samples_posteriors_using_death = 
  samples_logOR_posteriors_using_death %>% 
  pivot_longer(
    cols = c('Non-informative':'Pessimistic'),
    names_to = "Underlying_Prior", values_to = "log(OR)"
  )

## Respiratory support

# Simple oxygen only
samples_posteriors_simple_death = 
  samples_logOR_posteriors_simple_death %>% 
  pivot_longer(
    cols = c('Non-informative':'Pessimistic'),
    names_to = "Underlying_Prior", values_to = "log(OR)"
  )

# Non-invasive ventilation
samples_posteriors_noninvasive_death = 
  samples_logOR_posteriors_noninvasive_death %>% 
  pivot_longer(
    cols = c('Non-informative':'Pessimistic'),
    names_to = "Underlying_Prior", values_to = "log(OR)"
  )

# Invasive mechanical ventilation
samples_posteriors_invasive_death = 
  samples_logOR_posteriors_invasive_death %>% 
  pivot_longer(
    cols = c('Non-informative':'Pessimistic'),
    names_to = "Underlying_Prior", values_to = "log(OR)"
  )
  
```

We will now calculate the odds ratio from log(OR) with the exponentiation
function.

```{r}
## Use of corticosteroids

# Not using
samples_posteriors_not_using_death = 
  samples_posteriors_not_using_death %>% 
  mutate(OR = exp(`log(OR)`))

# Using
samples_posteriors_using_death = 
  samples_posteriors_using_death %>% 
  mutate(OR = exp(`log(OR)`))

## Respiratory support

# Simple oxygen only
samples_posteriors_simple_death = 
  samples_posteriors_simple_death %>% 
  mutate(OR = exp(`log(OR)`))

# Non-invasive ventilation
samples_posteriors_noninvasive_death = 
  samples_posteriors_noninvasive_death %>% 
  mutate(OR = exp(`log(OR)`))

# Invasive mechanical ventilation
samples_posteriors_invasive_death = 
  samples_posteriors_invasive_death %>% 
  mutate(OR = exp(`log(OR)`))
  
```

Here is an example of a data-frame using head()

```{r}
samples_posteriors_not_using_death %>% head() %>% flextable() %>% autofit()
```

Lastly, we will apply the formula mentioned above to calculate the corresponding
risk difference for each odds ratio.

$$R D=\frac{B R * \left(B R-1\right)* \left(O R-1\right)}{B R*O R-B R+1}$$

As you can see, we have to set a fixed baseline risk (BR) to calculate the risk
difference from odds ratio.

In this project, we are analyzing 2 different subgroups regarding use of
corticosteroids: not using and using. We are also analyzing 3 different
subgroups regarding respiratory support: simple oxygen only, non-invasive
ventilation and invasive mechanical ventilation.

We have decided that we will use the BRs from the respective control group in the
RECOVERY trial as our references. You can see these BRs below:

```{r echo=FALSE}
tibble(
  
  "Subgroup" = c("Not using",
                 "Using",
                 
                 "Simple oxygen only",
                 "Non-invasive ventilation",
                 "Invasive mechanical"
                 ),
  
  "Baseline Risk in Control Group (%)" = c(
    
    d2 %>% 
    filter(trial == "RECOVERY",
           corticosteroids == 0,
           outcome == "mortality") %>% 
      summarise(n = 100*(events_control/total_control)) %>% 
      round(., 1) %>% 
      pull(),
    d2 %>% 
    filter(trial == "RECOVERY",
           corticosteroids == 1,
           outcome == "mortality") %>% 
      summarise(n = 100*(events_control/total_control)) %>% 
      round(., 1) %>% 
      pull(),
    
    d1 %>% 
    filter(trial == "RECOVERY",
           oxygen == "simple oxygen",
           outcome == "mortality") %>% 
      summarise(n = 100*(events_control/total_control)) %>% 
      round(., 1) %>% 
      pull(),
    d1 %>% 
    filter(trial == "RECOVERY",
           oxygen == "non-invasive ventilation",
           outcome == "mortality") %>% 
      summarise(n = 100*(events_control/total_control)) %>% 
      round(., 1) %>% 
      pull(),
    d1 %>% 
    filter(trial == "RECOVERY",
           oxygen == "invasive ventilation",
           outcome == "mortality") %>% 
      summarise(n = 100*(events_control/total_control)) %>% 
      round(., 1) %>% 
      pull()
  )
  
) %>% 
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  pack_rows("Use of corticosteroids", 1, 2) %>% 
  pack_rows("Respiratory support", 3, 5)
```

Let's apply the formula from Doi et al., 2020 to derive the posterior
distributions in the risk difference scale.

```{r}
# BR = Baseline Risk
# OR = Odds Ratio

RD_fun = function(BR,OR)
  {
( BR*(BR-1)*(OR-1) ) / ( BR*OR - BR+1)
}
```


```{r}
# Calculating the risk differences

### Use of corticosteroids

## Not using

# Define baseline risk
BR_not_using = d2 %>% 
    filter(trial == "RECOVERY",
           corticosteroids == 0, # Not using
           outcome == "mortality") %>% 
      summarise(n = events_control/total_control) %>%
      pull()

samples_posteriors_not_using_death = 
  samples_posteriors_not_using_death %>% 
  # Apply formula from Doi et al., 2020
  mutate(RD = RD_fun(BR_not_using,
                     OR))

## Using

# Define baseline risk
BR_using = d2 %>% 
    filter(trial == "RECOVERY",
           corticosteroids == 1, # Using
           outcome == "mortality") %>% 
      summarise(n = events_control/total_control) %>%
      pull()

samples_posteriors_using_death = 
  samples_posteriors_using_death %>% 
  # Apply formula from Doi et al., 2020
  mutate(RD = RD_fun(BR_using,
                     OR))

### Respiratory support

## Simple oxygen

# Define baseline risk
BR_simple = d1 %>% 
    filter(trial == "RECOVERY",
           oxygen == "simple oxygen",
           outcome == "mortality") %>% 
      summarise(n = events_control/total_control) %>% 
      pull()

samples_posteriors_simple_death = 
  samples_posteriors_simple_death %>% 
  # Apply formula from Doi et al., 2020
  mutate(RD = RD_fun(BR_simple,
                     OR))

## Non-invasive

# Define baseline risk
BR_noninvasive = d1 %>% 
    filter(trial == "RECOVERY",
           oxygen == "non-invasive ventilation",
           outcome == "mortality") %>% 
      summarise(n = events_control/total_control) %>% 
      pull()

samples_posteriors_noninvasive_death = 
  samples_posteriors_noninvasive_death %>% 
  # Apply formula from Doi et al., 2020
  mutate(RD = RD_fun(BR_noninvasive,
                     OR))

## Invasive mechanical ventilation

# Define baseline risk
BR_invasive = d1 %>% 
    filter(trial == "RECOVERY",
           oxygen == "invasive ventilation",
           outcome == "mortality") %>% 
      summarise(n = events_control/total_control) %>% 
      pull()

samples_posteriors_invasive_death = 
  samples_posteriors_invasive_death %>% 
  # Apply formula from Doi et al., 2020
  mutate(RD = RD_fun(BR_invasive,
                     OR))
```

```{r include=FALSE}
## Save 

# save(samples_posteriors_not_using_death,
#      samples_posteriors_using_death,
#      samples_posteriors_simple_death,
#      samples_posteriors_noninvasive_death,
#      samples_posteriors_invasive_death,
#      
#      file = here("02_preprint", "output", "data", "analyses", # file path
#                  "samples_posteriors_death.RData"))        # file name

# Although I saved this file to my PC, I uploaded it to OSF
# (https://osf.io/3qexw/), since it is 56MB
# In the next analysis documents, I will load this file directly from OSF,
# without the need of downloading it to your PC
```

### Plotting

To display some of our calculations, we will now plot the posterior distributions
for log-odds ratio, odds ratio and risk difference for a single subgroup
(not using corticosteroids).

We note that **log-odds ratios** *less* than $0$, **odds-ratios** *less* than $1$
and **risk differences** *greater* than $0$ mean benefit for the mortality
outcome.


```{r echo=FALSE}
# Underlying a Non-informative prior

p1 = samples_posteriors_not_using_death %>% 
  filter(`Underlying_Prior` == "Non-informative") %>% 
  ggplot(aes(`log(OR)`)) +
  stat_halfeye(fill = "#C7CCF4") +
  labs(x = "log(OR)", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(-0.5, 0.8, 0.25)) +
  coord_cartesian(x = c(-0.5, 0.8)) 

p2 = samples_posteriors_not_using_death %>% 
  filter(`Underlying_Prior` == "Non-informative") %>% 
  ggplot(aes(`OR`)) +
  stat_halfeye(fill = "#C7CCF4") +
  labs(x = "OR", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(0.5, 2.5, 0.5)) +
  coord_cartesian(x = c(0.5, 2.5)) 

p3 = samples_posteriors_not_using_death %>% 
  filter(`Underlying_Prior` == "Non-informative") %>% 
  ggplot(aes(`RD`)) +
  stat_halfeye(fill = "#C7CCF4") +
  labs(x = "RD", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(-0.2, 0.1, 0.05)) +
  coord_cartesian(x = c(-0.2, 0.1)) 

```

```{r echo=FALSE}
# Underlying an Evidence-based prior

p4 = samples_posteriors_not_using_death %>% 
  filter(`Underlying_Prior` == "Evidence-based") %>% 
  ggplot(aes(`log(OR)`)) +
  stat_halfeye(fill = "#E7B03C") +
  labs(x = "log(OR)", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(-0.5, 0.8, 0.25)) +
  coord_cartesian(x = c(-0.5, 0.8)) 

p5 = samples_posteriors_not_using_death %>% 
  filter(`Underlying_Prior` == "Evidence-based") %>% 
  ggplot(aes(`OR`)) +
  stat_halfeye(fill = "#E7B03C") +
  labs(x = "OR", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(0.5, 2.5, 0.5)) +
  coord_cartesian(x = c(0.5, 2.5)) 

p6 = samples_posteriors_not_using_death %>% 
  filter(`Underlying_Prior` == "Evidence-based") %>% 
  ggplot(aes(`RD`)) +
  stat_halfeye(fill = "#E7B03C") +
  labs(x = "RD", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(-0.2, 0.1, 0.05)) +
  coord_cartesian(x = c(-0.2, 0.1)) 

```

```{r echo=FALSE}
# Underlying an Skeptical prior

p7 = samples_posteriors_not_using_death %>% 
  filter(`Underlying_Prior` == "Skeptical") %>% 
  ggplot(aes(`log(OR)`)) +
  stat_halfeye() +
  labs(x = "log(OR)", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(-0.5, 0.8, 0.25)) +
  coord_cartesian(x = c(-0.5, 0.8)) 

p8 = samples_posteriors_not_using_death %>% 
  filter(`Underlying_Prior` == "Skeptical") %>% 
  ggplot(aes(`OR`)) +
  stat_halfeye() +
  labs(x = "OR", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(0.5, 2.5, 0.5)) +
  coord_cartesian(x = c(0.5, 2.5)) 

p9 = samples_posteriors_not_using_death %>% 
  filter(`Underlying_Prior` == "Skeptical") %>% 
  ggplot(aes(`RD`)) +
  stat_halfeye() +
  labs(x = "RD", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(-0.2, 0.1, 0.05)) +
  coord_cartesian(x = c(-0.2, 0.1)) 

```

```{r echo=FALSE}
# Underlying an Optimistic prior

p10 = samples_posteriors_not_using_death %>% 
  filter(`Underlying_Prior` == "Optimistic") %>% 
  ggplot(aes(`log(OR)`)) +
  stat_halfeye(fill = "#479D8B") +
  labs(x = "log(OR)", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(-0.5, 0.8, 0.25)) +
  coord_cartesian(x = c(-0.5, 0.8)) 

p11 = samples_posteriors_not_using_death %>% 
  filter(`Underlying_Prior` == "Optimistic") %>% 
  ggplot(aes(`OR`)) +
  stat_halfeye(fill = "#479D8B") +
  labs(x = "OR", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(0.5, 2.5, 0.5)) +
  coord_cartesian(x = c(0.5, 2.5)) 

p12 = samples_posteriors_not_using_death %>% 
  filter(`Underlying_Prior` == "Optimistic") %>% 
  ggplot(aes(`RD`)) +
  stat_halfeye(fill = "#479D8B") +
  labs(x = "RD", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(-0.2, 0.1, 0.05)) +
  coord_cartesian(x = c(-0.2, 0.1)) 

```

```{r echo=FALSE}
# Underlying an Pessimistic prior

p13 = samples_posteriors_not_using_death %>% 
  filter(`Underlying_Prior` == "Pessimistic") %>% 
  ggplot(aes(`log(OR)`)) +
  stat_halfeye(fill = "#D36883") +
  labs(x = "log(OR)", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(-0.5, 0.8, 0.25)) +
  coord_cartesian(x = c(-0.5, 0.8)) 

p14 = samples_posteriors_not_using_death %>% 
  filter(`Underlying_Prior` == "Pessimistic") %>% 
  ggplot(aes(`OR`)) +
  stat_halfeye(fill = "#D36883") +
  labs(x = "OR", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(0.5, 2.5, 0.5)) +
  coord_cartesian(x = c(0.5, 2.5)) 

p15 = samples_posteriors_not_using_death %>% 
  filter(`Underlying_Prior` == "Pessimistic") %>% 
  ggplot(aes(`RD`)) +
  stat_halfeye(fill = "#D36883") +
  labs(x = "RD", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(-0.2, 0.1, 0.05)) +
  coord_cartesian(x = c(-0.2, 0.1)) 

```

```{r echo=FALSE, fig.align='center', fig.height=2, fig.width=8}
(p1 + p2 + p3) +  plot_annotation(
  title = "Posterior distributions using a non-informative prior")

(p4 + p5 + p6) +  plot_annotation(
  title = "Posterior distributions using an evidence-based prior")

(p7 + p8 + p9) +  plot_annotation(
  title = "Posterior distributions using a skeptical prior")

(p10 + p11 + p12) +  plot_annotation(
  title = "Posterior distributions using an optimistic prior")

(p13 + p14 + p15) +  plot_annotation(
  title = "Posterior distributions using a pessimistic prior")
```
