---
title: 'A Bayesian Interpretation of Subgroup Analyses: RECOVERY Trial on Tocilizumab
  and COVID-19'
thanks: '`r format(Sys.time(), "%B %d, %Y")`'
author:
- name: Arthur M. Albuquerque
  affiliation: Universidade Federal do Rio de Janeiro, Brazil
- name: Lucas Tramujas, MD
  affiliation: Research Institute, HCor‐Hospital do Coração, Brazil
- name: Lorenzo R. Sewanan, MD, PhD
  affiliation: Columbia University, U.S.A.
- name: James M. Brophy, MD, PhD
  affiliation: McGill University Health Center, Canada
output:
  pdf_document:
    extra_dependencies: ["float"]
    citation_package: natbib
    keep_tex: no
    fig_caption: yes
    latex_engine: pdflatex
    template: svm-latex-ms2.tex # source: https://github.com/cmcr-class/example_article
  word_document: default
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
bibliography: master.bib
biblio-style: apsr
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H", out.extra = "")

# https://bookdown.org/yihui/rmarkdown-cookbook/figure-placement.html
```

```{r include=FALSE}
library(here)
library(tidyverse)
library(cowplot)
library(patchwork)
library(kableExtra)
library(ggtext)
```

# Introduction

The Randomised Evaluation of COVID-19 Therapy (RECOVERY) is a platform trial
testing several treatments for COVID-19 since the beginning of the pandemics
in 2020. Preliminary results on the anti-inflammatory drug tocilizumab were
published on medRxiv on February 11, 2021 [@horby2021]. The RECOVERY was a
large, open-label randomized controlled trial (RCT) that assessed 28-day
mortality as the primary outcome in hospitalized patients with COVID-19 using a
frequentist statistical approach. Secondary outcomes were discharge from
hospital within 28 days in all patients and risk of invasive mechanical
ventilation (IMV) or death among those not receiving IMV at baseline. Overall,
tocilizumab was effective for these outcomes.

The authors also reported several pre-specified subgroups analyses. Two clusters
of subgroups are of substantial clinical interest: respiratory support and days
since symptom onset. For COVID-19 infection, duration of disease and use of
oxygen are crucial to stratify the risk of patients. Respiratory support should
be interpreted as a direct proxy for the severity of the disease. Patients on
invasive mechanical ventilation are naturally at greater risk of death than
patients on only simple oxygen. Previous research has shown that dyspnea most
commonly develops after a median of 5-7 days since the onset of symptoms
[@wang2020].

It has been postulated that the severity of COVID-19 disease is closely related
to the degree of inflammation and disease length [@wiersinga2020]. For
example, the results of another anti-inflammatory drug -- dexamethasone --
showed strikingly different results between subgroups
[@therecoverycollaborativegroup2021]. Thus, one could also expect different
results between the subgroups in the tocilizumab trial. However, this trial's
subgroup results were consistent with each other.

Subgroup analyses are fundamental to clinical practice. These analyses inform
clinicians about the effect of treatments in specific subsets of patients and
thus yield to the opportunity of precision medicine. They also allow one to
explore or confirm hypotheses. In the context of tocilizumab and COVID-19, it is
clinically and economically important to determine if there is sufficient
discrepancy to ascertain different treatments for specific subgroups.

Notably, frequentist subgroup analyses pose several limitations. Their low
statistical power increases both type 2 error, leading to false-negatives
results [@schulz2005], and type 1 error risk, inflating treatment effect
[@ioannidis2005]. Estimations suggest that clinical trials designed to
have 80% power for the primary outcome are anticipated to have 30% power for the
interaction term [@kent2018]. Thus, one could quickly draw misleading
conclusions about the effect of tocilizumab in specific subgroups if these
analyses are not appropriately interpreted.

Also, it is of utmost importance to define if results from a study are
clinically meaningful. The frequentist statistical inference relies on p-values
and confidence intervals (CIs) to report results. Unfortunately, p-values only
provide information about the data's compatibility to the null hypothesis
(usually zero effect). It is impossible to infer whether the actual effect size
is large or what is the probability of the alternative hypothesis (result
different from zero) of being true based on p-values [@rafi2020]. Also, the
frequentist approach to subgroup analysis can lead to multiplicity issues
[@schulz2005]. CIs can improve the interpretation of results beyond p-values.
However, they are also easily misinterpreted. CIs contain a range of parameter
values that are more compatible with the data than are values outside the
interval [@rafi2020]. CIs do not indicate what the probability of a range of
effects is (e.g., RR \< 1, 0.9, 0.8 etc.) to be true. Thus, the frequentist
statistical framework poorly aids clinicians to analyze data from subgroups in
RCTs thoroughly.

# Bayesian re-analysis

We believe that Bayesian analyses can clarify the interpretation of the RECOVERY
trial [@wijeysundera2009]. In brief, the Bayesian statistical framework relies
on the use of *priors* that represent our belief in the actual effect. Then,
these are combined with data (*likelihood*), generating *posterior
probabilities* (PP). PP can be described with credible intervals, which, in
contrast to confidence intervals, actually inform the probability of an effect
within a specified interval. We can also perform multiple looks at the PP
without worrying about multiplicity issues. Because of this, Bayesian analyses
allows one to assess the probability of numerous effect sizes at once
[@spiegelhalter2004].

Here, we aim to describe the priors we will use in our re-analysis of the
RECOVERY trial on tocilizumab. We will re-analyze the primary outcome -- 28-day
mortality -- and a secondary outcome, risk of being discharged alive from the
hospital within 28 days. We will analyze these outcomes in all patients and each
subgroup regarding respiratory support (no ventilator support, non-invasive
mechanical ventilation, and invasive mechanical ventilation) and days since
symptom onset ($\leq$ 7 days and $>$ 7 days). We will primarily report the
risk difference between the tocilizumab and control groups.

## Methods

We will extract data from RCTs on tocilizumab and COVID-19 included in a
Cochrane's systematic living review [@ghosn2021]. Then, we will use these
results to create evidence-based priors (EBP) for each subgroup if specific data
is available. We will also pool data from every subgroup to create an EBP for
all patients. In case data is not available for a particular subgroup, we will
use the pooled data as the EBP for these subgroups. To dampen this adaptation's
influence on the final results, we will also analyze these specific subgroups
with both 10% and 50% weight of this adapted prior [@brophy1995;
@goligher2018]. We described the entire data extraction protocol elsewhere
([https://osf.io/upd4q/](https://osf.io/upd4q/)).

Thus, every prior will be normally distributed and described by a *mean* and a
*variance*. To test our results' robustness, we will also perform sensitivity
analyses using different priors [@sung2005; @zampieri2021]. We will create
four extra priors: skeptical, optimistic, pessimistic, and non-informative.
While the latter will have the same parameters (*mean* and *variance*) for every
subgroup, we will adapt each subgroup's original EBP to create priors
accordingly [@white2005]. The skeptical prior uses the EBP's *variance*, but
the *mean* equals $0$. The optimistic prior uses the EBP's *variance*, but the
*mean* equals $-0.05$. Lastly, the pessimistic prior uses the EBP's *variance*,
but the *mean* equals $0.05$. We decided on the absolute *mean* value of $0.05$
because the RECOVERY group estimated risk difference would be $0.05$ for their
sample size calculation [@therecoverycollaborativegroup2021; @zampieri2021].
We note that these are values for the analyses regarding the mortality outcome
because negative results mean tocilizumab is better. Thus, we will use opposite
mean values for the secondary outcome because, in this case, positive results
mean tocilizumab is better.

## A simulation

```{r include=FALSE}
#Skeptical prior parameters

mean_data_prior = -0.02 # Prior ARD mean
sd_data_prior = 0.04 # Prior SD

#Skeptical prior parameters
mean_skeptical_prior = 0 # Prior ARD mean
sd_skeptical_prior = sd_data_prior # Prior SD

#Optimistic prior parameters

mean_optimistic_prior = -0.05   # Prior ARD mean
sd_optimistic_prior = sd_data_prior # Prior SD

#Pessimistic prior parameters

mean_pessimistic_prior = 0.05  # Prior ARD mean
sd_pessimistic_prior = sd_data_prior # Prior SD

#Non-informative prior parameters

mean_noninformative_prior = 0  # Prior ARD mean
sd_noninformative_prior = 10 # Prior SD

```

To aid in the interpretation of our methods, we simulated data to create
multiple priors. In this example, we analyzed the mortality outcome of a
fictitious subgroup. The evidence-based prior for this subgroup is described by
a *mean* of $`r mean_data_prior`$ and *standard deviation* of
$`r sd_data_prior`$. We then created the priors following the instructions
mentioned above. These priors can be visualized in *Figure 1* and their parameters
in *Table 1*.

# Conclusion

Here, we discussed the rationale and the methods of a pre-planned Bayesian
re-analysis of the RECOVERY trial on tocilizumab and COVID-19.

\newpage



```{r include=FALSE}
priors = tibble(
  
  "Prior Belief" = c("Evidence-based",
                     "Skeptical",
                     "Optimistic",
                     "Pessimistic",
                     "Non-informative"),
  
  "Mean RD"= c(mean_data_prior,
                mean_skeptical_prior,
                mean_optimistic_prior,
                mean_pessimistic_prior,
                mean_noninformative_prior),
  
  "SD of RD" = c(round(sd_data_prior,2),
                  round(sd_skeptical_prior,2),
                  round(sd_optimistic_prior,2),
                  round(sd_pessimistic_prior,2),
                  round(sd_noninformative_prior,2)),
  
  "Pr(< 0)" = c(round(pnorm(0,mean_data_prior,sd_data_prior),2),
                round(pnorm(0,mean_skeptical_prior,sd_skeptical_prior),2),
                round(pnorm(0,mean_optimistic_prior,sd_optimistic_prior),2),
                round(pnorm(0,mean_pessimistic_prior,sd_pessimistic_prior),2),
                round(pnorm(0,mean_noninformative_prior,sd_noninformative_prior),2)),
  
  "Pr(< -0.05)" = c(round(pnorm(-.05,mean_data_prior,sd_data_prior),2),
                    round(pnorm(-.05,mean_skeptical_prior,sd_skeptical_prior),2),
                    round(pnorm(-.05,mean_optimistic_prior,sd_optimistic_prior),2),
                    round(pnorm(-.05,mean_pessimistic_prior,sd_pessimistic_prior),2),
                    round(pnorm(-.05,mean_noninformative_prior,sd_noninformative_prior),2)),
  
  "Pr(< -0.10)" = c(round(pnorm(-.1,mean_data_prior,sd_data_prior),2),
                    round(pnorm(-.1,mean_skeptical_prior,sd_skeptical_prior),2),
                    round(pnorm(-.1,mean_optimistic_prior,sd_optimistic_prior),2),
                    round(pnorm(-.1,mean_pessimistic_prior,sd_pessimistic_prior),2),
                    round(pnorm(-.1,mean_noninformative_prior,sd_noninformative_prior),2)),
)

priors_table =
  priors %>% 
  kbl(caption = "Parameters of priors",
      booktabs = T, align = 'c') %>% 
  kable_styling(latex_options = "striped")  %>% 
  add_header_above(c(" " = 3, "Probability of Treatment Effect" = 3)) %>% 
  footnote(general = "SD = Standard Deviation; RD = Risk Difference")
  
```

```{r echo=FALSE}
priors_table
```

\newpage

```{r echo=FALSE, fig.cap = "Simulation of priors derived from a fictitious evidence-based prior. Negative values mean tocilizumab is better."}

#### Data plot

pal = c("Evidence-based" = "#3C4D54",   
        "Skeptical" = "#D49352", 
        "Optimistic" = "#479ED0",
        "Pessimistic" = "#A64E49",
        "Non-informative" = "#85AD99") 

plot_prior = ggplot(data = data.frame(x = c(-0.2, 0.2)), aes(x)) +
  
  stat_function(fun = dnorm, n = 1000,
                args = list(mean = mean_data_prior,
                            sd = sd_data_prior), aes(colour = "Evidence-based"),
                linetype = 1, size = 1) + 
  
  stat_function(fun = dnorm, n = 1000,
                args = list(mean = mean_skeptical_prior,
                            sd = sd_skeptical_prior), aes(colour = "Skeptical"),
                linetype = 1, size = 1) + 
    
  stat_function(fun = dnorm, n = 1000,
                 args = list(mean = mean_optimistic_prior,
                            sd = sd_optimistic_prior), aes(colour = "Optimistic"),
                linetype = 1, size = 1) +
  
  stat_function(fun = dnorm, n = 1000,
                args = list(mean = mean_pessimistic_prior,
                            sd = sd_pessimistic_prior), aes(colour = "Pessimistic"),
                linetype = 1, size = 1) +
    
  stat_function(fun = dnorm, n = 1000,
                 args = list(mean =mean_noninformative_prior,
                            sd = sd_noninformative_prior), aes(colour = "Non-informative"),
                linetype = 1, size = 1) + 
  geom_vline(xintercept = 0, color="grey70", linetype = 2) +
  
  scale_colour_manual("",values = pal) +   # legend
  guides(col = guide_legend(nrow = 2)) +   # to split legend in two rows https://ggplot2.tidyverse.org/reference/guide_legend.html
  labs(x="Risk difference", y = "") +
  
  scale_x_continuous(breaks=seq(from = -0.2, to = 0.2, 0.1)) +
  scale_y_continuous(limits=c(0, 13)) +
  
  theme_classic() +
  theme(axis.line.y=element_blank(),
        axis.title = element_text(size = 13),
        axis.text.y=element_blank(),
        axis.text.x = element_text(size = 11),
        axis.ticks.y=element_blank(),
        plot.title = element_text(hjust = 0.5),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 12),
        legend.position = "top",
        plot.margin = margin(25,25,10,25)) +
  
  coord_cartesian(expand = T, clip = 'off')


plot_prior

```

\newpage


