---
title: "Supplementary Material"
author: "Arthur M. Albuquerque"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  pdf_document:
    highlight: tango
    number_sections: no
    toc: yes
    toc_depth: 3
    keep_tex: TRUE
    includes:
      in_header: preamble.tex
geometry: margin=1in
header-includes:
   - \usepackage{tikz}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r message=FALSE, warning=FALSE}
# Load packages

# Ensures the package "pacman" is installed
if (!require("pacman")) install.packages("pacman")

# p_load() installs (if necessary) and loads the following packages

pacman::p_load(here, # file paths
               rio, # To import data
               tidyverse, # Data wrangling
               kableExtra, # Tables
               metagear # PRISMA plot
)
```

# Data extraction

```{r}
d = import(here("final_analyses", "data", "data_extraction_notes.xls"))

d = d %>% 
  mutate(subgroup = factor(subgroup,
                           levels = c("Not using corticosteroids",
                                      "Using corticosteroids",
                                      "Simple oxygen only",
                                      "Non-invasive ventilation",
                                      "Invasive mechanical ventilation",
                                      "Use of corticosteroids",
                                      "Respiratory support"
                                      )),
         study = factor(study,
                        levels = c("RECOVERY",
                                   "COVACTA",
                                   "REMAP-CAP",
                                   "CORIMUNO-19",
                                   "Salvarini",
                                   "TOCIBRAS",
                                   "Stone",
                                   "EMPACTA",
                                   "COVINTOC")))

```

In this section, we will elaborate the details underlying our data extraction 
process. 

We pre-registered our protocol in the OpenScienceFramework
(<https://osf.io/cytq8/>). In brief, we extracted summary data from randomized
controlled trials (RCT) included in a living systematic review on Cochrane. We
accessed each individual RCT manuscript to extract data. We
contacted the authors by e-mail to obtain relevant data not available in the
manuscript. However, we did not have success to obtain any extra information by 
e-mail.

The tables below show what studies were included and excluded. We will also
show the direct source (Figure/Table) of the extracted data in each RCT. Lastly,
we show relevant notes about details from each study and why we did not extract data
from certain RCTs that were included in the living systematic.

The diagram below show the workflow regarding studies that were used to create prior distributions.

```{r fig.align='center', fig.height=7, fig.width=10, out.width='0.7\\linewidth'}
  phases = c("START_PHASE: 7 studies identified from the living systematic review",
              "START_PHASE: 1 additional study identified in RECOVERY's manuscript",
              "8 studies with title and abstract screened",
              "EXCLUDE_PHASE: 0 studies excluded",
              "8 full-text articles assessed for eligibility",
              "EXCLUDE_PHASE: 0 full-text articles excluded, not fitting eligibility # criteria",
            "8 of studies included in qualitative synthesis",
            "EXCLUDE_PHASE: 4 studies excluded, incomplete data reported",
            "4 of studies included in quantitative synthesis (Prior distributions)")
 thePlot = plot_PRISMA(phases)

```

\newpage


```{r}
d %>% 
  filter(action == "included",
         outcome == "Mortality") %>% 
  arrange(subgroup,study) %>% 
  select(-action, -outcome, -subgroup) %>% 
  rename("Study" = study,
         "Source" = source,
         "Notes" = notes) %>% 
  kbl(booktabs = T,
      align = 'c',
      caption = "Included studies for the mortality outcome") %>% 
  kable_styling(latex_options = c("striped")) %>%
  column_spec(1, width = "18em") %>%
  column_spec(2, width = "6em") %>%
  column_spec(3, width = "40em") %>% 
  pack_rows("Invasive mechanical ventilation", 14, 16) %>% 
  pack_rows("Non-invasive ventilation", 10, 13) %>% 
  pack_rows("Simple oxygen only", 7, 9) %>% 
  pack_rows("Using corticosteroids", 4, 6) %>% 
  pack_rows("Not using corticosteroids", 1, 3) %>% 
  landscape() 

```

```{r}
d %>% 
  filter(action == "included",
         outcome == "Hospital discharge") %>% 
  arrange(subgroup,study) %>% 
  select(-action, -outcome, -subgroup) %>% 
  rename("Study" = study,
         "Source" = source,
         "Notes" = notes) %>% 
  kbl(booktabs = T,
      align = 'c',
      caption = "Included studies for the hospital discharge outcome") %>% 
  kable_styling(latex_options = c("striped")) %>%
  column_spec(1, width = "18em") %>%
  column_spec(2, width = "6em") %>%
  column_spec(3, width = "40em") %>% 
  pack_rows("Invasive mechanical ventilation", 11, 12) %>% 
  pack_rows("Non-invasive ventilation", 8, 10) %>% 
  pack_rows("Simple oxygen only", 5, 7) %>% 
  pack_rows("Using corticosteroids", 3, 4) %>% 
  pack_rows("Not using corticosteroids", 1, 2)%>% 
  landscape()
```

```{r}
d %>% 
  filter(action == "excluded",
         outcome == "Mortality") %>% 
  arrange(subgroup,study) %>% 
  select(study, notes) %>% 
  rename("Study" = study,
         "Notes" = notes) %>% 
  kbl(booktabs = T,
      caption = "Excluded studies for the mortality outcome") %>% 
  kable_styling(latex_options = c("striped")) %>%
  column_spec(1, width = "18em") %>%
  column_spec(2, width = "20em") %>%
  pack_rows("Respiratory support subgroups", 5, 8) %>% 
  pack_rows("Use of corticosteroids subgroups", 1, 4) %>% 
  landscape()
```

```{r}
d %>% 
  filter(action == "excluded",
         outcome == "Hospital discharge") %>% 
  arrange(subgroup,study) %>% 
  select(study, notes) %>% 
  rename("Study" = study,
         "Notes" = notes) %>% 
  kbl(booktabs = T,
      caption = "Excluded studies for the hospital discharge outcome") %>% 
  kable_styling(latex_options = c("striped")) %>%
  column_spec(1, width = "18em") %>%
  column_spec(2, width = "20em") %>% 
  pack_rows("Respiratory support subgroups", 6, 10) %>% 
  pack_rows("Use of corticosteroids subgroups", 1, 5) %>% 
  landscape()
```

\newpage

As mentioned in the tables above, we will now discuss further details about data
on the use of corticosteroids subgroups from REMAP-CAP. 

The relevant data from these subgroups are shown in Figure 9 in their supplementary
material.
Unfortunately, the authors do not provide the raw number of events per subgroup.
Instead, the data is displayed visually in stacked bars. Thus, we used the [{juicr} package](https://cran.r-project.org/web/packages/juicr/index.html) to extract
data directly from Figure 9. The raw data and extraction report generated by
{juicr} can be found in this project's
[GitHub repository](https://github.com/arthur-albuquerque/tocilizumab_reanalysis/tree/master/final_analyses/data).

Of note, REMAP-CAP was a three-arm randomized controlled trial that tested
tocilizumab and sarilumab (both are IL-6 antagonists) vs. usual care. The authors
only provided pooled data from these IL-6 antagonists vs. usual care in
Figure 9. Thus, we decided to perform sensitivity analyses with this data to
dampen the influence of sarilumab in final results.

We created evidence-based priors for these subgroups using data from
REMAP-CAP with different weights: 100%, 75% and 50%. This approach implies that 
the numbers of events and sample sizes from REMAP-CAP were
multiplied by 1, 0.75 or 0.5, respectively. 

As mentioned in the Methods section, we pooled data from similar studies with
a random-effect meta-analysis using a restricted maximum-likelihood estimator
to create evidence-based priors. We will now display evidence-based prior
distributions for both "Not using corticosteroids" and "Using corticosteroids"
subgroups that were generated with different weights on REMAP-CAP. Top
panels regards "Not using corticosteroids" and the bottom panels "Using
corticosteroids". We show these distributions in both log-odds ratio and odds
ratio scales to ease interpretation.


```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1.1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "weight_remap_cap_corticosteroids.pdf")) # File name

knitr::include_graphics(path) 
```

Point estimates depict the median and interval bars depict the 95% highest
density interval.

Because prior distributions are notably similar regardless of the weight used,
we have decided to only use the ones with 100% weight for our analyses.

\newpage

# Overall characteristics

```{r message=FALSE, warning=FALSE}
d1 = import(here("final_analyses", "data", "characteristics_data-extraction-table.xlsx"))

multiply100 = function(x){x*100}


# First wrangling

t = d1 %>% 
  rename("Year" = year,
         "Trial design" = blind,
         "Follow-up period (days)" = length_mortality,
         "Control treatment" = type_control) %>% 
  # Transform fractions to integers
  mutate(across(cortico_toci:invasive_control, ~multiply100(.))) %>% 
  # REMAP-CAP actually reports "> 80%" for corticosteroids, so let's change it
  mutate(cortico_toci = ifelse(cortico_toci == 80,"> 80",cortico_toci),
         cortico_control = ifelse(cortico_control == 80,"> 80",cortico_control)) %>%
  # REMAP-CAP actually reports "< 1%" for simple oxygen, so let's change it
  mutate(simple_toci = ifelse(simple_toci == 1,"< 1",simple_toci),
         simple_control = ifelse(simple_control == 1,"< 1",simple_control)) %>%
  # Transform all columns into character to be able to use pivot_longer()
  mutate_all(as.character) %>% 
  # Re-order columns
  select(trial, Year, "Trial design", "Follow-up period (days)", "Control treatment",
         age_toci:total_control) %>%
  pivot_longer(cols = Year:`Control treatment`,
               values_to = "characteristic",
               names_to = "columns") %>% 
  # Re-order again
  select(trial, columns, characteristic, age_toci:total_control)

# Break in two separate tables
# This half is all set
first_half = t %>% 
  select(trial:characteristic)

# This second half needs some wrangling

  
control = 
  t %>%
  select(trial, age_toci:total_control) %>%
  # remove repeated rows
  distinct(trial, .keep_all = T) %>%
  # Only control
  select(trial, ends_with("control")) %>%
  pivot_longer(age_control:last_col(),
    names_to = "names_control",
    values_to = "numbers_control"
  ) %>%
  separate(names_control,
    into = c("names_control", "NA")
  ) %>%
  select(-"NA") %>%
  # Rename
  mutate(
    names_control = case_when(
      names_control == "total" ~ "Number of patients",
      names_control == "age" ~ "Age",
      names_control == "male" ~ "Male sex (%)",
      names_control == "confirmed" ~ "Confirmed SARS-CoV-2 infection (%)",
      names_control == "cortico" ~ "Use of corticosteroids (%)",
      names_control == "simple" ~ "Simple oxygen only at randomisation (%)",
      names_control == "non" ~ "Non-invasive ventilation at randomisation (%)",
      names_control == "invasive" ~ "Invasive mechanical ventilation at randomisation (%)"
    )
  ) %>%
  # Rename Age since there are two different types according to the trial
  mutate(
    names_control =
      replace(
        names_control,
        names_control == "Age" &
          trial %in% c("RECOVERY", "REMAP-CAP", "COVACTA"), "Age (SD)"
      ),
    names_control =
      replace(
        names_control,
        names_control == "Age" &
          trial %in% c("CORIMUNO-19", "Salvarini"), "Age (IQR)"
      )
  ) %>% 
  
  # Define orders
  mutate(trial =
           factor(trial,
                  levels = c("RECOVERY",
                             "COVACTA",
                             "REMAP-CAP",
                             "CORIMUNO-19",
                             "Salvarini"))) %>% 
  mutate(names_control =
           factor(names_control,
                  levels = c("Number of patients",
                             "Age (SD)",
                             "Age (IQR)",
                             "Male sex (%)",
                             "Confirmed SARS-CoV-2 infection (%)",
                             "Use of corticosteroids (%)",
                             "Simple oxygen only at randomisation (%)",
                             "Non-invasive ventilation at randomisation (%)",
                             "Invasive mechanical ventilation at randomisation (%)"
                             )
                  )
         ) %>% 
  arrange(trial, names_control)

toci = 
  t %>%
  select(trial, age_toci:total_control) %>%
  # remove repeated rows
  distinct(trial, .keep_all = T) %>%
  # Only toci
  select(trial, ends_with("toci")) %>%
  pivot_longer(age_toci:last_col(),
               names_to = "names_toci",
               values_to = "numbers_toci"
  ) %>%
  separate(names_toci,
           into = c("names_toci", "NA")
  ) %>%
  select(-"NA") %>%
  # Rename
  mutate(
    names_toci = case_when(
      names_toci == "total" ~ "Number of patients",
      names_toci == "age" ~ "Age",
      names_toci == "male" ~ "Male sex (%)",
      names_toci == "confirmed" ~ "Confirmed SARS-CoV-2 infection (%)",
      names_toci == "cortico" ~ "Use of corticosteroids (%)",
      names_toci == "simple" ~ "Simple oxygen only at randomisation (%)",
      names_toci == "non" ~ "Non-invasive ventilation at randomisation (%)",
      names_toci == "invasive" ~ "Invasive mechanical ventilation at randomisation (%)"
    )
  ) %>%
  # Rename Age since there are two different types according to the trial
  mutate(
    names_toci =
      replace(
        names_toci,
        names_toci == "Age" &
          trial %in% c("RECOVERY", "REMAP-CAP", "COVACTA"), "Age (SD)"
      ),
    names_toci =
      replace(
        names_toci,
        names_toci == "Age" &
          trial %in% c("CORIMUNO-19", "Salvarini"), "Age (IQR)"
      )
  ) %>% 
  # Define orders
  mutate(trial =
           factor(trial,
                  levels = c("RECOVERY",
                             "COVACTA",
                             "REMAP-CAP",
                             "CORIMUNO-19",
                             "Salvarini"))) %>% 
  mutate(names_toci =
           factor(names_toci,
                  levels = c("Number of patients",
                             "Age (SD)",
                             "Age (IQR)",
                             "Male sex (%)",
                             "Confirmed SARS-CoV-2 infection (%)",
                             "Use of corticosteroids (%)",
                             "Simple oxygen only at randomisation (%)",
                             "Non-invasive ventilation at randomisation (%)",
                             "Invasive mechanical ventilation at randomisation (%)"
                             )
                  )
         ) %>% 
  arrange(trial, names_toci)


# Bind treetment columns
    
t_final = bind_cols(control %>% select(trial:numbers_control),
          toci %>% select(numbers_toci)) %>% 
  rename("Study Characteristic" = names_control,
         "Control" = numbers_control,
         "Tocilizumab" = numbers_toci) %>% 
  arrange(trial, `Study Characteristic`)


circles_mort =  tibble(
  "Mortality" = c(
    # RECOVERY
    " ", " ", " ", " ",
    "\\fillCircle", # Use of corticosteroids
    "\\fillCircle", # Simple oxygen
    "\\fillCircle", # Non-invasive
    "\\fillCircle", # Invasive 
    
    # COVACTA
    " ", " ", " ", " ",
    "\\fillCircle", # Use of corticosteroids
    "\\fillCircle", # Simple oxygen
    "\\fillCircle", # Non-invasive
    "\\fillCircle", # Invasive 
    
    # REMAP-CAP
    " ", " ", " ", " ",
    "\\fillCircle", # Use of corticosteroids
    "\\emptyCircle",# Simple oxygen
    "\\fillCircle", # Non-invasive
    "\\fillCircle", # Invasive
    
    # CORIMUNO-19
    " ", " ", " ", " ",
    "\\emptyCircle", # Use of corticosteroids
    "\\fillCircle",# Simple oxygen
    "\\emptyCircle", # Non-invasive
    "\\emptyCircle", # Invasive
    
    # Salvarini
    " ", " ", " ", " ",
    "\\emptyCircle", # Use of corticosteroids
    "\\emptyCircle",# Simple oxygen
    "\\fillCircle", # Non-invasive
    "\\emptyCircle" # Invasive
  ))

circles_discharge = tibble(
  "Hospital Discharge" = c(
    
    # RECOVERY
    " ", " ", " ", " ",
    "\\fillCircle", # Use of corticosteroids
    "\\fillCircle", # Simple oxygen
    "\\fillCircle", # Non-invasive
    "\\fillCircle", # Invasive 
    
    # COVACTA
    " ", " ", " ", " ",
    "\\fillCircle", # Use of corticosteroids
    "\\fillCircle", # Simple oxygen
    "\\fillCircle", # Non-invasive
    "\\fillCircle", # Invasive 
    
    # REMAP-CAP
    " ", " ", " ", " ",
    "\\emptyCircle", # Use of corticosteroids
    "\\emptyCircle",# Simple oxygen
    "\\emptyCircle", # Non-invasive
    "\\emptyCircle", # Invasive
    
    # CORIMUNO-19
    " ", " ", " ", " ",
    "\\emptyCircle", # Use of corticosteroids
    "\\fillCircle",# Simple oxygen
    "\\emptyCircle", # Non-invasive
    "\\emptyCircle", # Invasive
    
    # Salvarini
    " ", " ", " ", " ",
    "\\emptyCircle", # Use of corticosteroids
    "\\emptyCircle",# Simple oxygen
    "\\fillCircle", # Non-invasive
    "\\emptyCircle" # Invasive
)
)

circles = bind_cols(circles_mort, circles_discharge)
  
t_final = bind_cols(t_final, circles)


```

```{r}
first_half %>% 
   rename("Study Characteristic" = columns,
         " " = characteristic) %>% 
  mutate(trial = factor(trial, levels = c("RECOVERY",
                             "COVACTA",
                             "REMAP-CAP",
                             "CORIMUNO-19",
                             "Salvarini"))) %>% 
  arrange(trial) %>% 
  select(-trial) %>% 
  kbl(caption = "Overall characteristics of included studies",
      booktabs = T,
      align = 'l') %>%
  column_spec(1, width = "15em") %>%
  kable_styling(latex_options = c("striped", "hold_position")) %>%
  pack_rows("Salvarini", 17, 20) %>% 
  pack_rows("CORIMUNO-19", 13, 16) %>% 
  pack_rows("REMAP-CAP", 9, 12) %>% 
  pack_rows("COVACTA", 5, 8) %>% 
  pack_rows("RECOVERY", 1, 4)
```

```{r}
t_final %>% 
  select(-trial) %>% 
  kbl(caption = "Patient characteristics of included studies",
      escape = F,
      booktabs = T) %>%
  kable_styling(latex_options = c("striped")) %>%
  add_header_above(c(" " = 1,
                     "Interventions" = 2,
                     "Outcomes" = 2)) %>% 
  column_spec(1, width = "25em") %>%
  column_spec(2, width = "4em") %>%
  column_spec(3, width = "6.5em") %>%
  column_spec(4, width = "3.5em") %>%
  column_spec(5, width = "6em") %>%
  pack_rows("Salvarini", 33, 40) %>% 
  pack_rows("CORIMUNO", 25, 32) %>% 
  pack_rows("REMAP-CAP", 17, 24) %>% 
  pack_rows("COVACTA", 9, 16) %>% 
  pack_rows("RECOVERY", 1, 8)
  
```

\newpage

# Results: Mortality outcome

## Prior, RECOVERY, and Posterior distributions

### Supplementary Table 1

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.6\\linewidth', fig.height=5}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable1_HDI_intervals_figure1.png")) # File name

knitr::include_graphics(path) 
```

95% highest density intervals of evidence-based prior, RECOVERY, and posterior
distributions. This table complements Figure 1.

\newpage

## Posterior probabilities using evidence-based priors

### Supplementary Table 2

```{r, echo = FALSE, message=FALSE, fig.align='center',out.width='0.9\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable2_hdi_probabilities_figure2.png")) # File name

knitr::include_graphics(path) 
```

95% highest density intervals and posterior probabilities of benefit.
This table complements Figure 2.

\newpage

## Sensitivity analyses using different priors

### Supplementary Figure 1

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.95\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure1_priors_sensitivity.pdf")) # File name

knitr::include_graphics(path) 
```

Prior distributions for each subgroup.

Panel A shows results for patients not using corticosteroids; Panel B shows
results for patients using corticosteroids. 

Panel C shows results for simple oxygen only; Panel D shows results for
non-invasive ventilation; Panel E shows results for invasive mechanical
ventilation.

Point estimates depict the median and interval bars depict
95th quantile intervals.

### Supplementary Table 3

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.5\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable3_hdi_figure3.png")) # File name

knitr::include_graphics(path) 
```

Median and 95% highest density intervals of posteriors distributions from
sensitivity analyses with different priors. This table complements Figure 3.


### Supplementary Table 4

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.8\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable4_probabilities_figure3.png")) # File name

knitr::include_graphics(path) 
```

Posterior probabilities from sensitivity analyses using different priors.
This table complements Figure 3.

\newpage

## Sensitivity analyses using different baseline risks

### Supplementary Figure 2

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.7\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure2_varying_baseline_risk_difference.pdf")) # File name
knitr::include_graphics(path) 
```

Posterior distributions from sensitivity analyses using multiple different
baseline risks.

Each line represents posterior distribution for the corresponding baseline risk.
Horizontal black dashed lines represent the respective baseline risk underlying
other analyses (Figure 2), i.e., risk in the control group in the RECOVERY trial
for each subgroup (Table 1). Vertical red dashed line represent 0% risk
difference. Point estimates depict the median and interval bars depict 95%
highest density intervals.

Panel A shows results for patients not using corticosteroids; Panel B shows
results for patients using corticosteroids. Panel C shows results for simple
oxygen only; Panel D shows results for non-invasive ventilation; Panel E shows
results for invasive mechanical ventilation.

\newpage

# Results: Hospital discharge outcome

## RECOVERY and Priors: Number of events and sample size 

### Supplementary Table 5

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.9\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable5_discharge_table1.png")) # File name
knitr::include_graphics(path) 
```

\newpage

## Prior, RECOVERY, and Posterior distributions

### Supplementary Figure 3

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1.1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure3_discharge_figure1.pdf")) # File name
knitr::include_graphics(path) 
```

Point estimates depict the median and interval bars depict 95% highest density
intervals.

### Supplementary Table 6

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.6\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable6_discharge_HDI_intervals_figureS3.png")) # File name
knitr::include_graphics(path) 
```

95% highest density intervals of evidence-based prior, RECOVERY, and posterior
distributions. This table complements Supplementary Figure 3.

\newpage

## Posterior distribution and probabilities using evidence-based priors

### Supplementary Figure 4

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure4_discharge_figure2.pdf")) # File name
knitr::include_graphics(path) 
```

Panels A and C: Point estimates depict the median. Interval bars depict the 80
and 95% highest density intervals. Panels B and D: Cumulative posterior
distributions correspond to the probabilities that the risk difference (RD)
is lower than or equal to the effect size on the X‐axis. The colors in Panels
B and D match the ones used in Panels A and C.

\newpage

## Sensitivity analyses using different priors

### Supplementary Figure 5

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.95\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure5_discharge_priors_sensitivity.pdf")) # File name

knitr::include_graphics(path) 
```

Prior distributions for each subgroup.

Panel A shows results for patients not using corticosteroids; Panel B shows
results for patients using corticosteroids. 

Panel C shows results for simple oxygen only; Panel D shows results for
non-invasive ventilation; Panel E shows results for invasive mechanical
ventilation.

Point estimates depict the median and interval bars depict
95th quantile intervals.

\newpage

### Supplementary Figure 6

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1.1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure6_discharge_figure3.pdf")) # File name

knitr::include_graphics(path) 
```

Posterior distributions from sensitivity analyses using different priors.

Point estimates depict the median. Interval bars depict the 95% highest density
intervals.

\newpage

### Supplementary Table 7

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.5\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable7_discharge_hdi_figure3.png")) # File name

knitr::include_graphics(path) 
```

Median and 95% highest density intervals of posteriors distributions from
sensitivity analyses with different priors. This table complements 
Supplementary Figure 6.

\newpage

### Supplementary Table 8

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.8\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable8_discharge_probabilities_figure3.png")) # File name

knitr::include_graphics(path) 
```

Posterior probabilities from sensitivity analyses using different priors.
This table complements Supplementary Figure 6.

\newpage

## Sensitivity analyses using different baseline risks: Use of corticosteroids

### Supplementary Figure 7

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.7\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure7_discharge_varying_baseline_risk_difference.pdf")) # File name
knitr::include_graphics(path) 
```

Posterior distributions from sensitivity analyses using multiple different
baseline risks.

Each line represents posterior distribution for the corresponding baseline risk.
Horizontal black dashed lines represent the respective baseline risk underlying
other analyses (Supplementary Figure 4), i.e., risk in the control group in the
RECOVERY trial for each subgroup (Supplementary Table 5). Vertical red dashed
line represent 0% risk difference. Point estimates depict the median and
interval bars depict 95% highest density intervals.

Panel A shows results for patients not using corticosteroids; Panel B shows
results for patients using corticosteroids. Panel C shows results for simple
oxygen only; Panel D shows results for non-invasive ventilation; Panel E shows
results for invasive mechanical ventilation.

\newpage

### Supplementary Figure 8

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure8_discharge_figure4.pdf")) # File name
knitr::include_graphics(path) 
```

Posterior probabilities from sensitivity analyses using multiple different
baseline risks.

Each line represents the posterior probability of benefit for a specific cutoff,
such as risk difference lower to 0%, 1%, 2% and 5%. Vertical black
dashed lines represent the respective baseline risk underlying other analyses
(Supplementary Figure 4), i.e., risk in the control group in the RECOVERY trial for each
subgroup (Supplementary Table 5).

Panel A shows results for patients not using corticosteroids; Panel B shows
results for patients using corticosteroids. Panel C shows results for simple
oxygen only; Panel D shows results for non-invasive ventilation; Panel E shows
results for invasive mechanical ventilation.




