---
title: "Supplementary Material"
author: "Arthur M. Albuquerque"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r message=FALSE, warning=FALSE}
library(here)
```

# Supplementary Table 1

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.6\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable1_quantile_intervals_figure1.pdf")) # File name

knitr::include_graphics(path) 
```

95th interquantile intervals of priors and RECOVERY regarding respiratory support.
This table complements Figure 1.

# Supplementary Table 2

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.6\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable2_hdi_figure2.pdf")) # File name

knitr::include_graphics(path) 
```

95% highest density intervals of posterior distributions. This table complements
Figure 2.

# Supplementary Table 3

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.6\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable3_probabilities_figure2.pdf")) # File name

knitr::include_graphics(path) 
```

Posterior probabilities of each subgroup. This table complements Figure 2.

# Supplementary Figure 1

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.6\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure1_priors_not_using.pdf")) # File name

knitr::include_graphics(path) 
```

Prior distributions of sensitivity analyses regarding patients not using 
corticosteroids.

# Supplementary Figure 2

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.75\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure2_posteriors_not_using.pdf")) # File name

knitr::include_graphics(path) 
```

Posteriors distributions from sensitivity analyses regarding patients not using 
corticosteroids.

# Supplementary Table 4

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.75\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable4_probabilities_not_using.pdf")) # File name

knitr::include_graphics(path) 
```

Posteriors probabilities from sensitivity analyses regarding patients not using 
corticosteroids. This table complements Supplementary Figures 1 and 2.

# Supplementary Table 5

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.45\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable5_hdi_not_using.pdf")) # File name

knitr::include_graphics(path) 
```

95% highest density intervals from posterior distributions regarding patients not using 
corticosteroids. This table complements Supplementary Figures 1 and 2.

# Supplementary Figure 3

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.6\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure3_priors_using.pdf")) # File name

knitr::include_graphics(path) 
```

Prior distributions of sensitivity analyses regarding patients using 
corticosteroids.

# Supplementary Figure 4

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.75\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure4_posteriors_using.pdf")) # File name

knitr::include_graphics(path) 
```

Posteriors distributions from sensitivity analyses regarding patients using 
corticosteroids.

# Supplementary Table 6

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.75\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable6_probabilities_using.pdf")) # File name

knitr::include_graphics(path) 
```

Posteriors probabilities from sensitivity analyses regarding patients using 
corticosteroids. This table complements Supplementary Figures 3 and 4.

# Supplementary Table 7

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.45\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable7_hdi_using.pdf")) # File name

knitr::include_graphics(path) 
```

95% highest density intervals from posterior distributions regarding patients using 
corticosteroids. This table complements Supplementary Figures 3 and 4.

# Supplementary Figure 5

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.6\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure5_priors_simple.pdf")) # File name

knitr::include_graphics(path) 
```

Prior distributions of sensitivity analyses regarding patients on simple oxygen
only.

# Supplementary Figure 6

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.75\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure6_posteriors_simple.pdf")) # File name

knitr::include_graphics(path) 
```

Posteriors distributions from sensitivity analyses regarding patients on
simple oxygen only.

# Supplementary Table 8

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.75\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable8_probabilities_simple.pdf")) # File name

knitr::include_graphics(path) 
```

Posteriors probabilities from sensitivity analyses regarding patients on simple
oxygen only. This table complements Supplementary Figures 5 and 6.

# Supplementary Table 9

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.45\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable9_hdi_simple.pdf")) # File name

knitr::include_graphics(path) 
```

95% highest density intervals from posterior distributions regarding patients on
simple oxygen only. This table complements Supplementary Figures 5 and 6.

# Supplementary Figure 7

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.6\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure7_priors_noninvasive.pdf")) # File name

knitr::include_graphics(path) 
```

Prior distributions of sensitivity analyses regarding patients on non-invasive
ventilation.

# Supplementary Figure 8

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.75\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure8_posteriors_noninvasive.pdf")) # File name

knitr::include_graphics(path) 
```

Posteriors distributions from sensitivity analyses regarding patients on
non-invasive ventilation.

# Supplementary Table 10

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.75\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable10_probabilities_noninvasive.pdf")) # File name

knitr::include_graphics(path) 
```

Posteriors probabilities from sensitivity analyses regarding patients on
non-invasive ventilation. This table complements Supplementary Figures 7 and 8.

# Supplementary Table 11

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.45\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable11_hdi_noninvasive.pdf")) # File name

knitr::include_graphics(path) 
```

95% highest density intervals from posterior distributions regarding patients on
non-invasive ventilation. This table complements Supplementary Figures 7 and 8.

# Supplementary Figure 9

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.6\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure9_priors_invasive.pdf")) # File name

knitr::include_graphics(path) 
```

Prior distributions of sensitivity analyses regarding patients on invasive
mechanical ventilation. This figure complements Figure 3.

# Supplementary Table 12

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.45\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable11_hdi_noninvasive.pdf")) # File name

knitr::include_graphics(path) 
```

95% highest density intervals from posterior distributions regarding patients on
invasive mechanical ventilation. This table complements Figure 3 and
Supplementary Figure 9.

# Supplementary Figure 10

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.9\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure10_varying_baseline_risk_difference_corticosteroids.pdf")) # File name

knitr::include_graphics(path) 
```

Sensitivity analyses using multiple different baseline risks for subgroups on
the use of corticosteroids. Each line represents the posterior distribution for
the corresponding baseline risk. Point estimates depict the median and interval
bars depict 50% and 95% highest density intervals.

# Supplementary Figure 11

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.9\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure11_varying_baseline_risk_difference_respiratory.pdf")) # File name

knitr::include_graphics(path) 
```

Sensitivity analyses using multiple different baseline risks for subgroups on
respiratory support. Each line represents the posterior distribution for
the corresponding baseline risk. Point estimates depict the median and interval
bars depict 50% and 95% highest density intervals.

\newpage

# Supplementary Figure 12

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.8\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure12_varying_baseline_probabilities_corticosteroids.pdf")) # File name

knitr::include_graphics(path) 
```

RD: Risk Difference

Sensitivity analyses using multiple different baseline risks for subgroups on
the use of corticosteroids. Each line represents the posterior probability of benefit
for a specific cutoff, such as risk difference greater or equal to 0%, 1%, and so on.

\newpage

# Supplementary Figure 13

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.8\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure13_varying_baseline_probabilities_respiratory.pdf")) # File name

knitr::include_graphics(path) 
```

RD: Risk Difference

Sensitivity analyses using multiple different baseline risks for subgroups on
respiratory support. Each line represents the posterior probability of benefit
for a specific cutoff, such as risk difference greater or equal to 0%, 1%, and so on.

# Supplementary Table 13

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.8\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable13_discharge_table1.pdf")) # File name

knitr::include_graphics(path) 
```

Number of events and sample size regarding the hospital discharge outcome.

# Supplementary Figure 14

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.8\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure14_discharge_figure1.pdf")) # File name

knitr::include_graphics(path) 
```

RECOVERY and Priors distributions regarding the hospital discharge outcome.
Point estimates depict the median and interval bars depict 95th quantiles.

# Supplementary Figure 15

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.8\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure15_discharge_figure2.pdf")) # File name

knitr::include_graphics(path) 
```

Posterior distributions regarding the hospital discharge outcome.

Panels A and C: Point estimates depict the median. Interval bars depict the 50
and 95% highest density intervals. Panels B and D: Cumulative posterior
distributions correspond to the probabilities that the risk difference (RD)
is greater than or equal to the effect size on the X‐axis.

# Supplementary Figure 16

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.8\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure16_discharge_posteriors_not_using.pdf")) # File name

knitr::include_graphics(path) 
```

Posteriors distributions from sensitivity analyses using different priors.
This figure regards patients not using corticosteroids for the hospital discharge
outcome.

# Supplementary Table 14

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.8\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable14_discharge_probabilities_not_using.pdf")) # File name

knitr::include_graphics(path) 
```

Posteriors probabilities from sensitivity analyses using different priors.
This table complements Supplementary Figure 16.

# Supplementary Figure 17

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.8\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure17_discharge_posteriors_using.pdf")) # File name

knitr::include_graphics(path) 
```

Posteriors distributions from sensitivity analyses using different priors.
This figure regards patients using corticosteroids for the hospital discharge
outcome.

# Supplementary Table 15

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.8\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable15_discharge_probabilities_using.pdf")) # File name

knitr::include_graphics(path) 
```

Posteriors probabilities from sensitivity analyses using different priors.
This table complements Supplementary Figure 17.

# Supplementary Figure 18

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.8\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure18_discharge_posteriors_simple.pdf")) # File name

knitr::include_graphics(path) 
```

Posteriors distributions from sensitivity analyses using different priors.
This figure regards patients on simple oxygen only for the hospital discharge
outcome.

# Supplementary Table 16

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.8\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable16_discharge_probabilities_simple.pdf")) # File name

knitr::include_graphics(path) 
```

Posteriors probabilities from sensitivity analyses using different priors.
This table complements Supplementary Figure 18.

# Supplementary Figure 19

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.8\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure19_discharge_posteriors_noninvasive.pdf")) # File name

knitr::include_graphics(path) 
```

Posteriors distributions from sensitivity analyses using different priors.
This figure regards patients on non-invasive ventilation for the hospital discharge
outcome.

# Supplementary Table 17

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.8\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable17_discharge_probabilities_noninvasive.pdf")) # File name

knitr::include_graphics(path) 
```

Posteriors probabilities from sensitivity analyses using different priors.
This table complements Supplementary Figure 19.

# Supplementary Figure 20

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.8\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure20_discharge_posteriors_invasive.pdf")) # File name

knitr::include_graphics(path) 
```

Posteriors distributions from sensitivity analyses using different priors.
This figure regards patients on invasive mechanical ventilation for the hospital discharge
outcome.

# Supplementary Table 18

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.8\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable18_discharge_probabilities_invasive.pdf")) # File name

knitr::include_graphics(path) 
```

Posteriors probabilities from sensitivity analyses using different priors.
This table complements Supplementary Figure 20.

# Supplementary Figure 21

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.9\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure21_discharge_varying_baseline_risk_difference_corticosteroids.pdf")) # File name

knitr::include_graphics(path) 
```

Sensitivity analyses using multiple different baseline risks for subgroups on
the use of corticosteroids for the hospital discharge outcome. Each line
represents the posterior distribution for the corresponding baseline risk.
Point estimates depict the median and interval bars depict 50% and 95% highest
density intervals.

# Supplementary Figure 22

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.9\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure22_discharge_varying_baseline_risk_difference_respiratory.pdf")) # File name

knitr::include_graphics(path) 
```

Sensitivity analyses using multiple different baseline risks for subgroups on
respiratory support for the hospital discharge outcome. Each line represents
the posterior distribution for the corresponding baseline risk. Point estimates
depict the median and interval bars depict 50% and 95% highest density intervals.

\newpage

# Supplementary Figure 23

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.8\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure23_discharge_varying_baseline_probabilities_corticosteroids.pdf")) # File name

knitr::include_graphics(path) 
```

RD: Risk Difference

Sensitivity analyses using multiple different baseline risks for subgroups on
the use of corticosteroids for the hospital discharge outcome. Each line
represents the posterior probability of benefit for a specific cutoff, such as
risk difference greater or equal to 0%, 1%, and so on.

\newpage

# Supplementary Figure 24

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.8\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure24_discharge_varying_baseline_probabilities_respiratory.pdf")) # File name

knitr::include_graphics(path) 
```

RD: Risk Difference

Sensitivity analyses using multiple different baseline risks for subgroups on
respiratory support for the hospital discharge outcome. Each line
represents the posterior probability of benefit for a specific cutoff, such as
risk difference greater or equal to 0%, 1%, and so on.