---
title: "Supplementary Material"
author: "Arthur M. Albuquerque"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r message=FALSE, warning=FALSE}
library(here)
```

\newpage

# Mortality outcome

# Supplementary Table 1

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.6\\linewidth', fig.height=5}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable1_HDI_intervals_figure1.png")) # File name

knitr::include_graphics(path) 
```

95% highest density intervals of evidence-based prior, RECOVERY, and posterior
distributions. This table complements Figure 1.

\newpage

# Supplementary Table 2

```{r, echo = FALSE, message=FALSE, fig.align='center',out.width='0.9\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable2_hdi_probabilities_figure2.png")) # File name

knitr::include_graphics(path) 
```

95% highest density intervals and posterior probabilities of benefit.
This table complements Figure 2.

\newpage

# Supplementary Figure 1

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.6\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure1_priors_not_using.pdf")) # File name

knitr::include_graphics(path) 
```

Prior distributions of sensitivity analyses regarding patients not using 
corticosteroids. Point estimates depict the median and interval bars depict
95th quantile intervals.

\newpage

# Supplementary Figure 2

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.75\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure2_posteriors_not_using.pdf")) # File name

knitr::include_graphics(path) 
```


Posteriors distributions from sensitivity analyses regarding patients not using 
corticosteroids. Point estimates depict the median and interval bars depict
80% and 95% highest density intervals.


# Supplementary Table 3

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable3_hdi_probabilities_not_using.png")) # File name

knitr::include_graphics(path) 
```

HDI: Highest density interval

Posteriors distributions and probabilities from sensitivity analyses regarding patients not using 
corticosteroids. This table complements Supplementary Figure 2.

# Supplementary Figure 3

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.6\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure3_priors_using.pdf")) # File name

knitr::include_graphics(path) 
```

Prior distributions of sensitivity analyses regarding patients using 
corticosteroids. Point estimates depict the median and interval bars depict
95th quantile intervals.

\newpage

# Supplementary Figure 4

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.75\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure4_posteriors_using.pdf")) # File name

knitr::include_graphics(path) 
```


Posteriors distributions from sensitivity analyses regarding patients using 
corticosteroids. Point estimates depict the median and interval bars depict
80% and 95% highest density intervals.


# Supplementary Table 4

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable4_hdi_probabilities_using.png")) # File name

knitr::include_graphics(path) 
```

HDI: Highest density interval

Posteriors distributions and probabilities from sensitivity analyses regarding patients not using 
corticosteroids. This table complements Supplementary Figure 4.

# Supplementary Figure 5

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.6\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure5_priors_simple.pdf")) # File name

knitr::include_graphics(path) 
```

Prior distributions of sensitivity analyses regarding patients on simple oxygen
only. Point estimates depict the median and interval bars depict
95th quantile intervals.

\newpage

# Supplementary Figure 6

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.75\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure6_posteriors_simple.pdf")) # File name

knitr::include_graphics(path) 
```


Posteriors distributions from sensitivity analyses regarding patients on simple
oxygen only. Point estimates depict the median and interval bars depict
80% and 95% highest density intervals.


# Supplementary Table 5

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable5_hdi_probabilities_simple.png")) # File name

knitr::include_graphics(path) 
```

HDI: Highest density interval

Posteriors distributions and probabilities from sensitivity analyses regarding
patients on simple oxygen only. This table complements Supplementary Figure 6.

# Supplementary Figure 7

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.6\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure7_priors_noninvasive.pdf")) # File name

knitr::include_graphics(path) 
```

Prior distributions of sensitivity analyses regarding patients on non-invasive
ventilation. Point estimates depict the median and interval bars depict 95th
quantile intervals.

\newpage

# Supplementary Figure 8

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.75\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure8_posteriors_noninvasive.pdf")) # File name

knitr::include_graphics(path) 
```


Posteriors distributions from sensitivity analyses regarding patients on
non-invasive ventilation. Point estimates depict the median and interval bars
depict 80% and 95% highest density intervals.


# Supplementary Table 6

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable6_hdi_probabilities_noninvasive.png")) # File name

knitr::include_graphics(path) 
```

HDI: Highest density interval

Posteriors distributions and probabilities from sensitivity analyses regarding
patients on non-invasive ventilation. This table complements Supplementary
Figure 8.

# Supplementary Figure 9

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.6\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure9_priors_invasive.pdf")) # File name

knitr::include_graphics(path) 
```

Prior distributions of sensitivity analyses regarding patients on invasive
mechanical  ventilation. Point estimates depict the median and interval bars
depict 95th quantile intervals.

\newpage


# Supplementary Table 7

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.6\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable7_hdi_invasive.png")) # File name

knitr::include_graphics(path) 
```

HDI: Highest density interval

Posteriors distributions from sensitivity analyses regarding
patients on invasive mechanical ventilation. This table complements
Figure 3.

\newpage

# Supplementary Figure 10

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.9\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure10_varying_baseline_risk_difference_corticosteroids.pdf")) # File name
knitr::include_graphics(path) 
```

Sensitivity analyses using multiple different baseline risks for subgroups on
the use of corticosteroids. Each line represents the posterior distribution for
the corresponding baseline risk. Point estimates depict the median and interval
bars depict 80% and 95% highest density intervals.

# Supplementary Figure 11

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.9\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure11_varying_baseline_risk_difference_respiratory.pdf")) # File name
knitr::include_graphics(path) 
```

Sensitivity analyses using multiple different baseline risks for subgroups on
respiratory support. Each line represents the posterior distribution for
the corresponding baseline risk. Point estimates depict the median and interval
bars depict 80% and 95% highest density intervals.

\newpage

# Supplementary Figure 12

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure12_varying_baseline_probabilities_corticosteroids.pdf")) # File name
knitr::include_graphics(path) 
```

Sensitivity analyses using multiple different baseline risks for subgroups
on use of corticosteroids. Each line represents the posterior probability of
benefit  for a specific cutoff, such as risk difference greater or equal to
0%, 1%, 2% and 5%. Vertical dashed lines represent the respective baseline risk
(Table 1) used in other analyses. Panel A shows results for patients not using
corticosteroids; Panel B shows results for patients using corticosteroids.

\newpage

# Hospital discharge outcome

# Supplementary Table 8

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.9\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable8_discharge_table1.png")) # File name
knitr::include_graphics(path) 
```

# Supplementary Figure 13

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure13_discharge_figure1.pdf")) # File name
knitr::include_graphics(path) 
```

Point estimates depict the median and interval bars depict 95% highest density
intervals.

# Supplementary Table 9

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.6\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable9_HDI_intervals_figureS13.png")) # File name
knitr::include_graphics(path) 
```

95% highest density intervals of evidence-based prior, RECOVERY, and posterior
distributions. This table complements Supplementary Figure 13.

# Supplementary Figure 14

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure14_discharge_figure2.pdf")) # File name
knitr::include_graphics(path) 
```

Panels A and C: Point estimates depict the median. Interval bars depict the 80
and 95% highest density intervals. Panels B and D: Cumulative posterior
distributions correspond to the probabilities that the risk difference (RD)
is lower than or equal to the effect size on the X‐axis. The colors in Panels
B and D match the ones used in Panels A and C.

# Supplementary Figure 15

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.75\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure15_discharge_posteriors_not_using.pdf")) # File name

knitr::include_graphics(path) 
```


Posteriors distributions from sensitivity analyses regarding patients not using 
corticosteroids. Point estimates depict the median and interval bars depict
80% and 95% highest density intervals.


# Supplementary Table 10

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable10_discharge_hdi_probabilities_not_using.png")) # File name

knitr::include_graphics(path) 
```

HDI: Highest density interval

Posteriors distributions and probabilities from sensitivity analyses regarding
patients not using corticosteroids. This table complements Supplementary Figure 15.

# Supplementary Figure 16

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.75\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure16_discharge_posteriors_using.pdf")) # File name

knitr::include_graphics(path) 
```


Posteriors distributions from sensitivity analyses regarding patients using 
corticosteroids. Point estimates depict the median and interval bars depict
80% and 95% highest density intervals.


# Supplementary Table 11

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable11_discharge_hdi_probabilities_using.png")) # File name

knitr::include_graphics(path) 
```

HDI: Highest density interval

Posteriors distributions and probabilities from sensitivity analyses regarding
patients using corticosteroids. This table complements Supplementary Figure 16.

# Supplementary Figure 17

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.75\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure17_discharge_posteriors_simple.pdf")) # File name

knitr::include_graphics(path) 
```


Posteriors distributions from sensitivity analyses regarding patients on simple
oxygen only. Point estimates depict the median and interval bars depict
80% and 95% highest density intervals.


# Supplementary Table 12

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable12_discharge_hdi_probabilities_simple.png")) # File name

knitr::include_graphics(path) 
```

HDI: Highest density interval

Posteriors distributions and probabilities from sensitivity analyses regarding
patients on simple oxygen only. This table complements Supplementary Figure 17.

# Supplementary Figure 18

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.75\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure18_discharge_posteriors_noninvasive.pdf")) # File name

knitr::include_graphics(path) 
```


Posteriors distributions from sensitivity analyses regarding patients on
non-invasive ventilation. Point estimates depict the median and interval bars depict
80% and 95% highest density intervals.


# Supplementary Table 13

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable13_discharge_hdi_probabilities_noninvasive.png")) # File name

knitr::include_graphics(path) 
```

HDI: Highest density interval

Posteriors distributions and probabilities from sensitivity analyses regarding
patients on non-invasive ventilation. This table complements Supplementary Figure 18.

# Supplementary Figure 19

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.75\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure19_discharge_posteriors_invasive.pdf")) # File name

knitr::include_graphics(path) 
```


Posteriors distributions from sensitivity analyses regarding patients on
invasive mechanical ventilation. Point estimates depict the median and
interval bars depict 80% and 95% highest density intervals.


# Supplementary Table 14

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "STable14_discharge_hdi_probabilities_invasive.png")) # File name

knitr::include_graphics(path) 
```

HDI: Highest density interval

Posteriors distributions and probabilities from sensitivity analyses regarding
patients on invasive mechanical ventilation. This table complements
Supplementary Figure 19.

# Supplementary Figure 20

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.9\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure20_discharge_varying_baseline_risk_difference_corticosteroids.pdf")) # File name
knitr::include_graphics(path) 
```

Sensitivity analyses using multiple different baseline risks for subgroups on
the use of corticosteroids. Each line represents the posterior distribution for
the corresponding baseline risk. Point estimates depict the median and interval
bars depict 80% and 95% highest density intervals.

# Supplementary Figure 21

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.9\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure21_discharge_varying_baseline_risk_difference_respiratory.pdf")) # File name
knitr::include_graphics(path) 
```

Sensitivity analyses using multiple different baseline risks for subgroups on
respiratory support. Each line represents the posterior distribution for
the corresponding baseline risk. Point estimates depict the median and interval
bars depict 80% and 95% highest density intervals.

\newpage

# Supplementary Figure 22

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure22_discharge_varying_baseline_probabilities_corticosteroids.pdf")) # File name
knitr::include_graphics(path) 
```

Sensitivity analyses using multiple different baseline risks for subgroups
on use of corticosteroids. Each line represents the posterior probability of
benefit  for a specific cutoff, such as risk difference greater or equal to
0%, 1%, 2% and 5%. Vertical dashed lines represent the respective baseline risk
(Table 1) used in other analyses. Panel A shows results for patients not using
corticosteroids; Panel B shows results for patients using corticosteroids.

# Supplementary Figure 23

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "appendix", # File path
                                 "SFigure23_discharge_varying_baseline_probabilities_respiratory.pdf")) # File name
knitr::include_graphics(path) 
```

Sensitivity analyses using multiple different baseline risks for subgroups
on respiratory support. Each line represents the posterior probability of
benefit  for a specific cutoff, such as risk difference greater or equal to
0%, 1%, 2% and 5%. Vertical dashed lines represent the respective baseline risk
(Table 1) used in other analyses. Panel A shows results for simple oxygen only;
Panel B shows results for non-invasive ventilation; Panel C shows results for
invasive mechanical ventilation.