---
title: "01_Data_overview"
author: "Arthur M. Albuquerque"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
          code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(tidyverse) # Data wrangling and plotting
library(here) # To find file paths within R project
library(janitor) # To change quickly change names of columns
library(flextable) # To create tables
```

```{r}
# Load the data
d = readxl::read_excel(here("final_analyses", "data", # file path
                            "extracted-data.xlsx"),   # file name
                       na = "NA")   
d = clean_names(d) # to change the names of columns
```
**The purpose of this document is to get an overall view of how each trial will**
**contribute to our analyses.**
<br>

Let's check the dimensions of the original data extraction table.
```{r}
tibble(
  rows = dim(d)[1],
  columns = dim(d)[2]
  ) %>% 
  flextable()
```

<br>

Here is a sneak peek into the format of the table. There is one row per
subgroup/outcome.

```{r}
d %>% 
  slice(1) %>% 
  flextable() %>% 
  autofit()
```

<br>

Let's check from what trials we have data regarding **"respiratory support"** subgroups
for the **mortality** outcome.

```{r}
d %>% 
  filter(!is.na(oxygen),
         outcome == "mortality") %>% 
  group_by(trial) %>% 
  count() %>%
  arrange(desc(n)) %>% 
  rename("number of rows" = n) %>%
  flextable() %>% 
  autofit()

```

<br>

Let's check from what trials we have data regarding **"respiratory support"** subgroups
for the **hospital discharge** outcome.

```{r}
d %>% 
  filter(!is.na(oxygen),
         outcome == "discharge") %>% 
  group_by(trial) %>% 
  count() %>%
  arrange(desc(n)) %>% 
  rename("number of rows" = n) %>%
  flextable() %>% 
  autofit()

```

<br>

Let's check from what trials we have data regarding **"days since symptom onset"**
subgroups for the **mortality** outcome

```{r}
d %>% 
  filter(!is.na(symptom_cutoff),
         outcome == "mortality") %>% 
  group_by(trial) %>% 
  count() %>%
  arrange(desc(n)) %>% 
  rename("number of rows" = n) %>%
  flextable() %>% 
  autofit()

```

<br>

Let's check from what trials we have data regarding **"days since symptom onset"**
subgroups for the **hospital discharge** outcome

```{r}
d %>% 
  filter(!is.na(symptom_cutoff),
         outcome == "discharge") %>% 
  group_by(trial) %>% 
  count() %>%
  arrange(desc(n)) %>% 
  rename("number of rows" = n) %>%
  flextable() %>% 
  autofit()

```

<br>

Since we only have data from the RECOVERY trial regarding **"days since symptom onset"**
subgroups, we **will not further analyze** these in this project.

```{r}
d_respiratory = d %>% 
  filter(!is.na(oxygen)) %>% 
  select(!starts_with("symptom"))
```

<br>

Let's check the dimensions of the new data frame without data from
**"days since symptom onset"** subgroups.

```{r}
tibble(
  rows = dim(d_respiratory)[1],
  columns = dim(d_respiratory)[2]
  ) %>% 
  flextable()
```

<br>

Now, let's check from what trials (other than RECOVERY) we have data
regarding **"respiratory support"** subgroups for **both outcomes**.

```{r}
d_respiratory %>% 
  filter(trial != "RECOVERY") %>% 
  group_by(trial) %>% 
  count() %>% 
  arrange(desc(n)) %>% 
  rename("number of rows" = n) %>%
  flextable() %>%
  autofit()
  
```

<br>

Let's break it down and check what type of data we have from each trial.

```{r}
d_respiratory %>%
  filter(!str_detect(oxygen, "pooled"),
         outcome == "mortality") %>%
  group_by(outcome, trial, oxygen) %>%
  arrange(oxygen) %>%
  count() %>%
  ungroup() %>% 
  select(-n) %>% 
  flextable() %>%
  autofit()
```

<br>

```{r}
d_respiratory %>%
  filter(!str_detect(oxygen, "pooled"),
         outcome == "discharge") %>%
  group_by(outcome, trial, oxygen) %>%
  arrange(oxygen) %>%
  count() %>%
  select(-n) %>% 
  flextable() %>%
  autofit()
```

<br>

Lastly, let's check from what trials we have **pooled data available** 
(in addition to what was described above).

```{r}
d_respiratory %>%
  filter(str_detect(oxygen, "pooled")) %>%
  group_by(outcome, trial, oxygen) %>%
  arrange(oxygen) %>%
  count() %>%
  select(-n) %>% 
  flextable() %>%
  autofit()
```

As displayed above, there are trials that only provide pooled data and trials
that provide both subgroup and pooled data.


```{r}
# Let's save our output with only data regarding respiratory support

#write.csv(d_respiratory, paste(here(
#  "final_analyses", "output", "data", # file path
#  "respiratory-data.csv")) # file name
#  ) 
```

<br><br>

```{r echo=TRUE}
sessionInfo()
```

