---
title: "11_Posteriors_Corticosteroids_Hospital_Discharge"
author: "Arthur M. Albuquerque"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
          code_folding: hide
          toc: yes
          toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
# Ensures the package "pacman" is installed
if (!require("pacman")) install.packages("pacman")

# p_load() installs (if necessary) and loads the following packages

pacman::p_load(janitor, # To clean column names
               tidyverse, # Data wrangling and plotting
               ggdist, # To plot distributions
               patchwork, # To arrange multiple plots
               here, # To find file paths within R project
               metafor, # To create priors from meta-analysis
               flextable, # To create quick tables
               kableExtra # To create nice tables
               )
```

```{r}
## Load objects with the posterior distributions using non-informative priors

load(here("final_analyses", "output", "data",
                 "noninformative_recovery_using_cortico_discharge.RData"))

load(here("final_analyses", "output", "data",
                 "noninformative_recovery_not_cortico_discharge.RData"))

## Load objects with rma() outputs for forest plots

load(here("final_analyses", "output", "data",
                 "priors_using_cortico_discharge.RData"))

load(here("final_analyses", "output", "data",
                 "priors_not_cortico_discharge.RData"))

## Load objects with mean + SD of multiple priors along with
## RECOVERY data and posterior distributions

load(file = here("final_analyses", "output", "data",
                 "multiple_priors_using_cortico_discharge.RData"))

load(file = here("final_analyses", "output", "data",
                 "multiple_priors_not_cortico_discharge.RData"))

## Load objets with all the posterior for summary plot

load(here("final_analyses", "output", "data",
                 "all_posteriors_using_cortico_discharge.RData"))

load(here("final_analyses", "output", "data",
                 "all_posteriors_not_cortico_discharge.RData"))

```

```{r}
## Load functions to plot

# To create summary table

source(here("final_analyses", "script", "functions", # file path
            "summary_table_discharge.R"))               # file name


# To plot risk distributions side-by-side

source(here("final_analyses", "script", "functions", # file path
            "risk_comparison_plot.R"))               # file name

# To plot risk difference distribution

source(here("final_analyses", "script", "functions", # file path
            "risk_difference_plot.R"))               # file name

# To plot cumulative probability of risk difference

source(here("final_analyses", "script", "functions", # file path
            "cumulative_risk_difference_plot.R"))    # file name

# To plot prior, data and posterior distributions side-by-side

source(here("final_analyses", "script", "functions", # file path
            "data_prior_posterior_plot.R"))          # file name

# To plot the posterior distribution

source(here("final_analyses", "script", "functions", # file path
            "posterior_difference_plot.R"))          # file name

# To plot the cumulative probability of the posterior distribution

source(here("final_analyses", "script", "functions", # file path
            "posterior_cumulative_plot.R"))          # file name

```

# Summary

Let's take a look at how many patients we have by trial and subgroup

```{r warning=FALSE, include=FALSE}
d = read_csv(here("final_analyses", "data",                      # file path
                  "corticosteroids_subgroup_extracted-data.csv") # file name
             )

d = clean_names(d)

t = d %>%
  filter(outcome == "discharge") %>% 
  select(-outcome) %>% 
  flextable() %>% 
  autofit()

```

```{r}
t
```


The following analyses were not pre-registered.

<br>

**Regarding the hospital discharge outcome, positive risk differences mean benefit.**

```{r}

# X axis
xlim_inf = -12.5
xlim_sup = 12.5
ticks_spacing = 2.5

# Assure subgroup order
# https://stackoverflow.com/questions/12774210/
# how-do-you-specifically-order-ggplot2-x-axis-instead-of-alphabetical-order

level_order = c("Pessimistic",
                "Optimistic",
                "Skeptical",
                "Evidence-based",
                "Non-informative")

p1 = all_posteriors_using_cortico_discharge %>%
  
  # make it tidy for ggplot
  pivot_longer(
    cols = c("Non-informative":"Pessimistic"),
    names_to = "dist", values_to = "samples"
  ) %>%
  
  ggplot(aes(x = 100 * samples, y = factor(dist, level = level_order))) +

  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(aes(fill = stat(x > 0)),
               .width = c(0.5, 0.95)
  ) +
  scale_fill_manual(values = c("#E98A33", "gray90")) +
  labs(x = "\nRisk difference (%)",
       y = "Underlying prior\n",
       title = "Using corticosteroids\n"
  ) +
  scale_x_continuous(breaks = seq(from = xlim_inf, to = xlim_sup, ticks_spacing)) +
  scale_y_discrete(expand = c(0, 0.3)) +
  theme(
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    legend.position = "none",
    plot.title.position = 'plot',
    plot.margin = margin(20, 25, 10, 20)
  ) +
  coord_cartesian(xlim = c(xlim_inf, xlim_sup))

```

```{r}
p2 = all_posteriors_not_cortico_discharge %>%
  
  # make it tidy for ggplot
  pivot_longer(
    cols = c("Non-informative":"Pessimistic"),
    names_to = "dist", values_to = "samples"
  ) %>%
  
  ggplot(aes(x = 100 * samples, y = factor(dist, level = level_order))) +

  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(aes(fill = stat(x > 0)),
               .width = c(0.5, 0.95)
  ) +
  scale_fill_manual(values = c("gray90", "#DCA3C2")) +
  labs(x = "\nRisk difference (%)",
       y = "Underlying prior\n",
       title = "Not using corticosteroids\n"
  ) +
  scale_x_continuous(breaks = seq(from = xlim_inf, to = xlim_sup, ticks_spacing)) +
  scale_y_discrete(expand = c(0, 0.3)) +
  theme(
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    legend.position = "none",
    plot.title.position = 'plot',
    plot.margin = margin(20, 25, 10, 20)
  ) +
  coord_cartesian(xlim = c(xlim_inf, xlim_sup))
```

```{r, fig.align='center', fig.height=7, fig.width=9, fig.cap="Interval bars depict 50% and 95% credible intervals"}
p1 + plot_annotation(title = "Posterior distributions on hospital discharge",
                          theme = theme(plot.title = element_text(size = 20)))

```

```{r}
# Summary table
table_posterior = summary_table_discharge(all_posteriors_using_cortico_discharge)

# Use kableExtra to have a nice table

table_posterior %>% 
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>% 
  column_spec(7, bold = T, color = "#E98A33") %>%
  add_header_above(c(" " = 3,
                     "Probability of Harm" = 3,
                     "Probability of Benefit" = 4)) %>% 
  footnote(general = "RD = Risk Difference; SD = Standard Deviation")
```


```{r, fig.align='center', fig.height=7, fig.width=9, fig.cap="Interval bars depict 50% and 95% credible intervals"}
p2
```

```{r}
# Summary table
table_posterior = summary_table_discharge(all_posteriors_not_cortico_discharge)

# Use kableExtra to have a nice table

table_posterior %>% 
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>% 
  column_spec(7, bold = T, color = "#A263A9") %>%
  add_header_above(c(" " = 3,
                     "Probability of Harm" = 3,
                     "Probability of Benefit" = 4)) %>%  
  footnote(general = "RD = Risk Difference; SD = Standard Deviation")
```

# Per subgroup

## Using corticosteroids

### Non-informative prior

```{r, fig.align='center', fig.height=4, fig.width=7, fig.cap="While the darker shaded area depicts the 50% credible interval (CI), the interval bar depicts the 95% CI."}

## Plot!

# I will use my own functions to standardize my plots

risk_comparison_plot(
  noninformative_recovery_using_cortico_discharge, # Data object

  ### start using quotes
  
  "gray50", # Color code for control group
  "#D3A464", # Color code for other group
  "\nRisk (%)", # X axis label
  "RECOVERY trial", # Title
  "Using corticosteroids\n", # Subtitle
  
  ### stop using quotes

  42, # X axis inferior limit
  62, # X axis superior limit
  2 # X axis spacing for ticks
)
```

```{r, fig.align='center', fig.height=4, fig.width=7}
xlabel = "\nRisk difference (%)"
xlim_inf = 0
xlim_sup = 16

p1 = risk_difference_plot(
  noninformative_recovery_using_cortico_discharge, # Data object

  ## start using quotes
  "#7EBAC2", # fill color code
  xlabel, # X axis label
  ### stop using quotes

  xlim_inf, # X axis inferior limit
  xlim_sup, # X axis superior limit
  4 # X axis label
) 

p2 = cumulative_risk_difference_plot(
  noninformative_recovery_using_cortico_discharge, # Data object
  xlabel, # X axis label (in quotes)
  xlim_inf, # X axis inferior limit
  xlim_sup, # X axis superior limit
  2, # Spacing between ticks in X axis
  "discharge" # Outcome (within quotes)
  )
```

```{r, fig.align='center', fig.height=4, fig.width=7, warning=FALSE, fig.cap="The interval bar depicts the 95% credible interval. The cumulative posterior distribution corresponds to the probabilities that the risk difference (RD) is less than or equal to the effect size on the X‐axis."}
p1 + p2 + plot_annotation(
  title = "Posterior distribution: RECOVERY trial + Non-informative prior",
  subtitle = "Risk difference between groups using corticosteroids"
)
```

### Evidence-based prior

```{r, fig.align='center', fig.height=4, fig.width=5, warning=FALSE}
forest(priors_using_cortico_discharge)
```

```{r, fig.align='center', fig.height=4, fig.width=7, warning=FALSE, fig.cap="While the darker shaded area depicts the 50% credible interval (CI), the interval bar depicts the 95% CI."}

xlabel = "\nRisk difference (%)"

data_prior_posterior_plot(
  multiple_priors_using_cortico_discharge %>% # Output from normal_approximation()
    filter(type == "evidence-based"), 
  
  # start using quotes
           "#364D55", # Color for the prior
           "#7EBAC2", # Color for RECOVERY
           "#A65041", # Color for the posterior
           xlabel, # X axis label
           "Posterior distribution: RECOVERY + Evidence-based prior", # Title
           "Using corticosteroids", # Subtitle
           # stop using quotes
           -10, # X axis inferior limit
           20, # X axis superior limit
           5 # Spacing between ticks in X axis
  ) 

```

```{r}
xlim_inf = 0
xlim_sup = 16

p1 = posterior_difference_plot(
  multiple_priors_using_cortico_discharge %>% # Output from normal_approximation()
    filter(type == "evidence-based"), 

  ## start using quotes
  "#A65041", # fill color code
  xlabel, # X axis label
  ### stop using quotes

  xlim_inf, # X axis inferior limit
  xlim_sup, # X axis superior limit
  4 # Spacing between ticks in X axis
) 

p2 = posterior_cumulative_plot(
  multiple_priors_using_cortico_discharge %>% # Output from normal_approximation()
    filter(type == "evidence-based"), 
  xlabel, # X axis label (in quotes)
  xlim_inf, # X axis inferior limit
  xlim_sup, # X axis superior limit
  2, # Spacing between ticks in X axis
  "discharge" # Outcome (within quotes)
  )
```

```{r, fig.align='center', fig.height=4, fig.width=7, warning=FALSE, fig.cap="The interval bar depicts the 95% credible interval. The cumulative posterior distribution corresponds to the probabilities that the risk difference (RD) is less than or equal to the effect size on the X‐axis."}
p1 + p2 + plot_annotation(
  title = "Posterior distribution: RECOVERY trial + Evidence-based prior",
  subtitle = "Using corticosteroids"
)
```

### Skeptical prior

```{r, fig.align='center', fig.height=4, fig.width=7, warning=FALSE, fig.cap="While the darker shaded area depicts the 50% credible interval (CI), the interval bar depicts the 95% CI."}

xlabel = "\nRisk difference (%)"

data_prior_posterior_plot(
  
  # Output from normal_approximation_multiple_priors()
  multiple_priors_using_cortico_discharge %>%
    filter(type == "skeptical"), 
  
  # start using quotes
           "gray60", # Color for the prior
           "#7EBAC2", # Color for RECOVERY
           "#A65041", # Color for the posterior
           xlabel, # X axis label
           "Posterior distribution: RECOVERY trial + Skeptical prior", # Title
           "Using corticosteroids", # Subtitle
           # stop using quotes
           -15, # X axis inferior limit
           15, # X axis superior limit
           5 # Spacing between ticks in X axis
  ) 

```

```{r}
xlim_inf = 0
xlim_sup = 16

p1 = posterior_difference_plot(
  
  multiple_priors_using_cortico_discharge %>% # Output from normal_approximation()
    filter(type == "skeptical"), 

  ## start using quotes
  "gray50", # fill color code
  xlabel, # X axis label
  ### stop using quotes

  xlim_inf, # X axis inferior limit
  xlim_sup, # X axis superior limit
  4 # Spacing between ticks in X axis
) 

p2 = posterior_cumulative_plot(
  
  multiple_priors_using_cortico_discharge %>% # Output from normal_approximation()
    filter(type == "skeptical"), 
  
  xlabel, # X axis label (in quotes)
  xlim_inf, # X axis inferior limit
  xlim_sup, # X axis superior limit
  2, # Spacing between ticks in X axis
  "discharge" # Outcome (within quotes)
  )
```

```{r, fig.align='center', fig.height=4, fig.width=7, warning=FALSE, fig.cap="The interval bar depicts the 95% credible interval. The cumulative posterior distribution corresponds to the probabilities that the risk difference (RD) is less than or equal to the effect size on the X‐axis."}
p1 + p2 + plot_annotation(
  title = "Posterior distribution: RECOVERY trial + Skeptical prior",
  subtitle = "Using corticosteroids"
)
```

### Optimistic prior

```{r, fig.align='center', fig.height=4, fig.width=7, warning=FALSE, fig.cap="While the darker shaded area depicts the 50% credible interval (CI), the interval bar depicts the 95% CI."}

xlabel = "\nRisk difference (%)"

data_prior_posterior_plot(
  
  # Output from normal_approximation_multiple_priors()
  multiple_priors_using_cortico_discharge %>%
    filter(type == "optimistic"), 
  
  # start using quotes
  "#5CA881", # Color for the prior
  "#7EBAC2", # Color for RECOVERY
  "#A65041", # Color for the posterior
  xlabel, # X axis label
  "Posterior distribution: RECOVERY trial + Optimistic prior", # Title
  "Using corticosteroids", # Subtitle
  # stop using quotes
  -10, # X axis inferior limit
  20, # X axis superior limit
  5 # Spacing between ticks in X axis
) 

```

```{r}
xlim_inf = 0
xlim_sup = 16

p1 = posterior_difference_plot(
  
  multiple_priors_using_cortico_discharge %>% # Output from normal_approximation()
    filter(type == "optimistic"), 
  
  ## start using quotes
  "#5CA881", # fill color code
  xlabel, # X axis label
  ### stop using quotes
  
  xlim_inf, # X axis inferior limit
  xlim_sup, # X axis superior limit
  4 # Spacing between ticks in X axis
) 

p2 = posterior_cumulative_plot(
  
  multiple_priors_using_cortico_discharge %>% # Output from normal_approximation()
    filter(type == "optimistic"), 
  
  xlabel, # X axis label (in quotes)
  xlim_inf, # X axis inferior limit
  xlim_sup, # X axis superior limit
  2, # Spacing between ticks in X axis
  "discharge" # Outcome (within quotes)
)
```

```{r, fig.align='center', fig.height=4, fig.width=7, warning=FALSE, fig.cap="The interval bar depicts the 95% credible interval. The cumulative posterior distribution corresponds to the probabilities that the risk difference (RD) is less than or equal to the effect size on the X‐axis."}
p1 + p2 + plot_annotation(
  title = "Posterior distribution: RECOVERY trial + Optimistic prior",
  subtitle = "Using corticosteroids"
)
```

### Pessimistic prior

```{r, fig.align='center', fig.height=4, fig.width=7, warning=FALSE, fig.cap="While the darker shaded area depicts the 50% credible interval (CI), the interval bar depicts the 95% CI."}

xlabel = "\nRisk difference (%)"

data_prior_posterior_plot(
  
  # Output from normal_approximation_multiple_priors()
  multiple_priors_using_cortico_discharge %>%
    filter(type == "pessimistic"), 
  
  # start using quotes
  "#523C84", # Color for the prior
  "#7EBAC2", # Color for RECOVERY
  "#A65041", # Color for the posterior
  xlabel, # X axis label
  "Posterior distribution: RECOVERY trial + Pessimistic prior", # Title
  "Using corticosteroids", # Subtitle
  # stop using quotes
  -20, # X axis inferior limit
  15, # X axis superior limit
  5 # Spacing between ticks in X axis
) 

```

```{r}
xlim_inf = 0
xlim_sup = 16

p1 = posterior_difference_plot(
  
  multiple_priors_using_cortico_discharge %>% # Output from normal_approximation()
    filter(type == "pessimistic"), 
  
  ## start using quotes
  "#523C84", # fill color code
  xlabel, # X axis label
  ### stop using quotes
  
  xlim_inf, # X axis inferior limit
  xlim_sup, # X axis superior limit
  4 # Spacing between ticks in X axis
) 

p2 = posterior_cumulative_plot(
  
  multiple_priors_using_cortico_discharge %>% # Output from normal_approximation()
    filter(type == "pessimistic"), 
  
  xlabel, # X axis label (in quotes)
  xlim_inf, # X axis inferior limit
  xlim_sup, # X axis superior limit
  2, # Spacing between ticks in X axis
  "discharge" # Outcome (within quotes)
)
```

```{r, fig.align='center', fig.height=4, fig.width=7, warning=FALSE, fig.cap="The interval bar depicts the 95% credible interval. The cumulative posterior distribution corresponds to the probabilities that the risk difference (RD) is less than or equal to the effect size on the X‐axis."}
p1 + p2 + plot_annotation(
  title = "Posterior distribution: RECOVERY trial + Pessimistic prior",
  subtitle = "Using corticosteroids"
)
```

## Not using corticosteroids

### Non-informative prior

```{r, fig.align='center', fig.height=4, fig.width=7, fig.cap="While the darker shaded area depicts the 50% credible interval (CI), the interval bar depicts the 95% CI."}

## Plot!

# I will use my own functions to standardize my plots

risk_comparison_plot(
  noninformative_recovery_not_cortico_discharge, # Data object
  
  ### start using quotes
  
  "gray50", # Color code for control group
  "#D3A464", # Color code for other group
  "\nRisk (%)", # X axis label
  "RECOVERY trial", # Title
  "Not using corticosteroids\n", # Subtitle
  
  ### stop using quotes
  
  36, # X axis inferior limit
  58, # X axis superior limit
  2 # X axis spacing for ticks
)
```

```{r, fig.align='center', fig.height=4, fig.width=7}
xlabel = "\nRisk difference (%)"
xlim_inf = -12
xlim_sup = 12

p1 = risk_difference_plot(
  noninformative_recovery_not_cortico_discharge, # Data object
  
  ## start using quotes
  "#7EBAC2", # fill color code
  xlabel, # X axis label
  ### stop using quotes
  
  xlim_inf, # X axis inferior limit
  xlim_sup, # X axis superior limit
  4 # X axis label
) 

p2 = cumulative_risk_difference_plot(
  noninformative_recovery_not_cortico_discharge, # Data object
  xlabel, # X axis label (in quotes)
  xlim_inf, # X axis inferior limit
  xlim_sup, # X axis superior limit
  2, # Spacing between ticks in X axis
  "discharge" # Outcome (within quotes)
)
```

```{r, fig.align='center', fig.height=4, fig.width=7, warning=FALSE, fig.cap="The interval bar depicts the 95% credible interval. The cumulative posterior distribution corresponds to the probabilities that the risk difference (RD) is less than or equal to the effect size on the X‐axis."}
p1 + p2 + plot_annotation(
  title = "Posterior distribution: RECOVERY trial + Non-informative prior",
  subtitle = "Risk difference between groups not using corticosteroids"
)
```

### Evidence-based prior

```{r, fig.align='center', fig.height=4, fig.width=5, warning=FALSE}
forest(priors_not_cortico_discharge)
```

```{r, fig.align='center', fig.height=4, fig.width=7, warning=FALSE, fig.cap="While the darker shaded area depicts the 50% credible interval (CI), the interval bar depicts the 95% CI."}

xlabel = "\nRisk difference (%)"

data_prior_posterior_plot(
  multiple_priors_not_cortico_discharge %>% # Output from normal_approximation()
    filter(type == "evidence-based"), 
  
  # start using quotes
  "#364D55", # Color for the prior
  "#7EBAC2", # Color for RECOVERY
  "#A65041", # Color for the posterior
  xlabel, # X axis label
  "Posterior distribution: RECOVERY + Evidence-based prior", # Title
  "Not using corticosteroids", # Subtitle
  # stop using quotes
  -10, # X axis inferior limit
  25, # X axis superior limit
  5 # Spacing between ticks in X axis
) 

```

```{r}
xlim_inf = -12
xlim_sup = 12

p1 = posterior_difference_plot(
  multiple_priors_not_cortico_discharge %>% # Output from normal_approximation()
    filter(type == "evidence-based"), 
  
  ## start using quotes
  "#A65041", # fill color code
  xlabel, # X axis label
  ### stop using quotes
  
  xlim_inf, # X axis inferior limit
  xlim_sup, # X axis superior limit
  4 # Spacing between ticks in X axis
) 

p2 = posterior_cumulative_plot(
  multiple_priors_not_cortico_discharge %>% # Output from normal_approximation()
    filter(type == "evidence-based"), 
  xlabel, # X axis label (in quotes)
  xlim_inf, # X axis inferior limit
  xlim_sup, # X axis superior limit
  2, # Spacing between ticks in X axis
  "discharge" # Outcome (within quotes)
)
```

```{r, fig.align='center', fig.height=4, fig.width=7, warning=FALSE, fig.cap="The interval bar depicts the 95% credible interval. The cumulative posterior distribution corresponds to the probabilities that the risk difference (RD) is less than or equal to the effect size on the X‐axis."}
p1 + p2 + plot_annotation(
  title = "Posterior distribution: RECOVERY trial + Evidence-based prior",
  subtitle = "Not using corticosteroids"
)
```

### Skeptical prior

```{r, fig.align='center', fig.height=4, fig.width=7, warning=FALSE, fig.cap="While the darker shaded area depicts the 50% credible interval (CI), the interval bar depicts the 95% CI."}

xlabel = "\nRisk difference (%)"

data_prior_posterior_plot(
  
  # Output from normal_approximation_multiple_priors()
  multiple_priors_not_cortico_discharge %>%
    filter(type == "skeptical"), 
  
  # start using quotes
  "gray60", # Color for the prior
  "#7EBAC2", # Color for RECOVERY
  "#A65041", # Color for the posterior
  xlabel, # X axis label
  "Posterior distribution: RECOVERY trial + Skeptical prior", # Title
  "Not using corticosteroids", # Subtitle
  # stop using quotes
  -15, # X axis inferior limit
  15, # X axis superior limit
  5 # Spacing between ticks in X axis
) 

```

```{r}
xlim_inf = -10
xlim_sup = 8

p1 = posterior_difference_plot(
  
  multiple_priors_not_cortico_discharge %>% # Output from normal_approximation()
    filter(type == "skeptical"), 
  
  ## start using quotes
  "gray50", # fill color code
  xlabel, # X axis label
  ### stop using quotes
  
  xlim_inf, # X axis inferior limit
  xlim_sup, # X axis superior limit
  2 # Spacing between ticks in X axis
) 

p2 = posterior_cumulative_plot(
  
  multiple_priors_not_cortico_discharge %>% # Output from normal_approximation()
    filter(type == "skeptical"), 
  
  xlabel, # X axis label (in quotes)
  xlim_inf, # X axis inferior limit
  xlim_sup, # X axis superior limit
  1, # Spacing between ticks in X axis
  "discharge" # Outcome (within quotes)
)
```

```{r, fig.align='center', fig.height=4, fig.width=7, warning=FALSE, fig.cap="The interval bar depicts the 95% credible interval. The cumulative posterior distribution corresponds to the probabilities that the risk difference (RD) is less than or equal to the effect size on the X‐axis."}
p1 + p2 + plot_annotation(
  title = "Posterior distribution: RECOVERY trial + Skeptical prior",
  subtitle = "Not using corticosteroids"
)
```

### Optimistic prior

```{r, fig.align='center', fig.height=4, fig.width=7, warning=FALSE, fig.cap="While the darker shaded area depicts the 50% credible interval (CI), the interval bar depicts the 95% CI."}

xlabel = "\nRisk difference (%)"

data_prior_posterior_plot(
  
  # Output from normal_approximation_multiple_priors()
  multiple_priors_not_cortico_discharge %>%
    filter(type == "optimistic"), 
  
  # start using quotes
  "#5CA881", # Color for the prior
  "#7EBAC2", # Color for RECOVERY
  "#A65041", # Color for the posterior
  xlabel, # X axis label
  "Posterior distribution: RECOVERY trial + Optimistic prior", # Title
  "Using corticosteroids", # Subtitle
  # stop using quotes
  -10, # X axis inferior limit
  20, # X axis superior limit
  5 # Spacing between ticks in X axis
) 

```

```{r}
xlim_inf = -12
xlim_sup = 12

p1 = posterior_difference_plot(
  
  multiple_priors_not_cortico_discharge %>% # Output from normal_approximation()
    filter(type == "optimistic"), 
  
  ## start using quotes
  "#5CA881", # fill color code
  xlabel, # X axis label
  ### stop using quotes
  
  xlim_inf, # X axis inferior limit
  xlim_sup, # X axis superior limit
  4 # Spacing between ticks in X axis
) 

p2 = posterior_cumulative_plot(
  
  multiple_priors_not_cortico_discharge %>% # Output from normal_approximation()
    filter(type == "optimistic"), 
  
  xlabel, # X axis label (in quotes)
  xlim_inf, # X axis inferior limit
  xlim_sup, # X axis superior limit
  2, # Spacing between ticks in X axis
  "discharge" # Outcome (within quotes)
)
```

```{r, fig.align='center', fig.height=4, fig.width=7, warning=FALSE, fig.cap="The interval bar depicts the 95% credible interval. The cumulative posterior distribution corresponds to the probabilities that the risk difference (RD) is less than or equal to the effect size on the X‐axis."}
p1 + p2 + plot_annotation(
  title = "Posterior distribution: RECOVERY trial + Optimistic prior",
  subtitle = "Not using corticosteroids"
)
```

### Pessimistic prior

```{r, fig.align='center', fig.height=4, fig.width=7, warning=FALSE, fig.cap="While the darker shaded area depicts the 50% credible interval (CI), the interval bar depicts the 95% CI."}

xlabel = "\nRisk difference (%)"

data_prior_posterior_plot(
  
  # Output from normal_approximation_multiple_priors()
  multiple_priors_not_cortico_discharge %>%
    filter(type == "pessimistic"), 
  
  # start using quotes
  "#523C84", # Color for the prior
  "#7EBAC2", # Color for RECOVERY
  "#A65041", # Color for the posterior
  xlabel, # X axis label
  "Posterior distribution: RECOVERY trial + Pessimistic prior", # Title
  "Not using corticosteroids", # Subtitle
  # stop using quotes
  -20, # X axis inferior limit
  10, # X axis superior limit
  5 # Spacing between ticks in X axis
) 

```

```{r}
xlim_inf = -12
xlim_sup = 8

p1 = posterior_difference_plot(
  
  multiple_priors_not_cortico_discharge %>% # Output from normal_approximation()
    filter(type == "pessimistic"), 
  
  ## start using quotes
  "#523C84", # fill color code
  xlabel, # X axis label
  ### stop using quotes
  
  xlim_inf, # X axis inferior limit
  xlim_sup, # X axis superior limit
  4 # Spacing between ticks in X axis
) 

p2 = posterior_cumulative_plot(
  
  multiple_priors_not_cortico_discharge %>% # Output from normal_approximation()
    filter(type == "pessimistic"), 
  
  xlabel, # X axis label (in quotes)
  xlim_inf, # X axis inferior limit
  xlim_sup, # X axis superior limit
  2, # Spacing between ticks in X axis
  "discharge" # Outcome (within quotes)
)
```

```{r, fig.align='center', fig.height=4, fig.width=7, warning=FALSE, fig.cap="The interval bar depicts the 95% credible interval. The cumulative posterior distribution corresponds to the probabilities that the risk difference (RD) is less than or equal to the effect size on the X‐axis."}
p1 + p2 + plot_annotation(
  title = "Posterior distribution: RECOVERY trial + Pessimistic prior",
  subtitle = "Not using corticosteroids"
)
```

<br><br>

```{r}
sessionInfo()
```

