---
title: "12_Difference_Posteriors_Corticosteroids"
author: "Arthur M. Albuquerque"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
          code_folding: hide
          toc: yes
          toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(janitor)
library(tidyverse)
library(ggdist)
library(rcartocolor)
library(here)
library(patchwork)
```

```{r}
## Load objets with all the posterior for summary plot

# Absolute risks

load(here("final_analyses", "output", "data",
                 "noninformative_recovery_using_cortico_death.RData"))

load(here("final_analyses", "output", "data",
                 "noninformative_recovery_not_cortico_death.RData"))

load(here("final_analyses", "output", "data",
                 "noninformative_recovery_using_cortico_discharge.RData"))

load(here("final_analyses", "output", "data",
                 "noninformative_recovery_not_cortico_discharge.RData"))

# Posterior distributions

load(here("final_analyses", "output", "data",
                 "all_posteriors_100_using_cortico_death.RData"))

load(here("final_analyses", "output", "data",
                 "all_posteriors_100_not_cortico_death.RData"))

load(here("final_analyses", "output", "data",
                 "all_posteriors_using_cortico_discharge.RData"))

load(here("final_analyses", "output", "data",
                 "all_posteriors_not_cortico_discharge.RData"))

# To plot risk distributions side-by-side

source(here("final_analyses", "script", "functions", # file path
            "risk_comparison_plot.R"))               # file name

```

Here I will use the evidence-based prior with 100% weight on the REMAP-CAP trial.

## Mortality outcome

Each risk difference represents the delta between the effect on tocilizumab minus
control. Negative risk differences mean benefit.

```{r, fig.align='center', fig.height=4, fig.width=7, fig.cap="While the darker shaded area depicts the 50% credible interval (CI), the interval bar depicts the 95% CI."}

## Plot!

# I will use my own functions to standardize my plots

risk_comparison_plot(
  noninformative_recovery_using_cortico_death, # Data object

  ### start using quotes
  
  "gray50", # Color code for control group
  carto_pal(7, "Mint")[4], # Color code for other group
  "\nRisk (%)", # X axis label
  "", # Title
  "Using corticosteroids\n", # Subtitle
  
  ### stop using quotes

  24, # X axis inferior limit
  48, # X axis superior limit
  2 # X axis spacing for ticks
  

) + coord_cartesian(xlim = c(24, 48))
```

```{r, fig.align='center', fig.height=4, fig.width=7, fig.cap="While the darker shaded area depicts the 50% credible interval (CI), the interval bar depicts the 95% CI."}

## Plot!

# I will use my own functions to standardize my plots

risk_comparison_plot(
  noninformative_recovery_not_cortico_death, # Data object
  
  ### start using quotes
  
  "gray50", # Color code for control group
  carto_pal(7, "PurpOr")[4], # Color code for other group
  "\nRisk (%)", # X axis label
  "", # Title
  "Not using corticosteroids\n", # Subtitle
  
  ### stop using quotes
  
  24, # X axis inferior limit
  48, # X axis superior limit
  2 # X axis spacing for ticks
)
```

```{r}
# all_posteriors data frame 1
posteriors_group1 = all_posteriors_100_using_cortico_death 
# all_posteriors data frame 2
posteriors_group2 = all_posteriors_100_not_cortico_death
# X axis limits (inf + sup) and ticks spacing (a+b)
xlim_inf_ab = -12.5
xlim_sup_ab = 12.5
ticks_spacing_ab = 2.5
# X axis limits (inf + sup) and ticks spacing (p1~p4)
xlim_inf_diff = -21
xlim_sup_diff = 3
ticks_spacing_diff = 3
# Colors for plot a
color1 = carto_pal(7, "Mint")[3]
color2 = carto_pal(7, "Mint")[5]
# Colors for plot b
color3 = carto_pal(7, "PurpOr")[3]
color4 = carto_pal(7, "PurpOr")[5]
# Colors for plot p1 + p2
color5 = carto_pal(7, "Mint")[6]
color6 = carto_pal(7, "PurpOr")[6]

```

```{r}
# Plot!

both_posteriors_non_informative = 
  # Posterior distribution on risk differences between patients on
  # tocilizumab vs. usual care (both using corticosteroids)
  posteriors_group1 %>% 
  select("Non-informative") %>% 
  rename("Using" = "Non-informative") %>% 
  # Posterior distribution on risk differences between patients on
  # tocilizumab vs. usual care (both NOT using corticosteroids)
  bind_cols(posteriors_group2 %>% select("Non-informative")) %>% 
  rename("Not using" = "Non-informative")

both_posteriors_evidence = 
  # Posterior distribution on risk differences in mortality between patients on
  # tocilizumab vs. usual care (both using corticosteroids)
  posteriors_group1 %>% 
  select("Evidence-based") %>% 
  rename("Using" = "Evidence-based") %>% 
  # Posterior distribution on risk differences in mortality between patients on
  # tocilizumab vs. usual care (both NOT using corticosteroids)
  bind_cols(posteriors_group2 %>% select("Evidence-based")) %>% 
  rename("Not using" = "Evidence-based")


#### Plot risk differences side-by-side

# Assure subgroup order
# https://stackoverflow.com/questions/12774210/
# how-do-you-specifically-order-ggplot2-x-axis-instead-of-alphabetical-order

level_order = c("Not using",
                "Using")

a = both_posteriors_non_informative %>%
  
  # make it tidy for ggplot
  pivot_longer(
    cols = c(everything()),
    names_to = "dist", values_to = "samples"
  ) %>%
  
  ggplot(aes(x = 100 * samples, y = factor(dist, level = level_order),
             fill = dist)) +
  
  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(position = "dodge") +
  geom_vline(aes(xintercept = 0), linetype = 2) + 
  scale_fill_manual(values = c(color1, color2)) +
  labs(x = "\n",
       y = "Corticosteroids\n",
       title = "Posterior distributions using non-informative priors"
  ) +
  scale_x_continuous(breaks = seq(from = xlim_inf_ab, to = xlim_sup_ab,
                                  ticks_spacing_ab)) +
  scale_y_discrete(expand = c(0, 0.3)) +
  theme(
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    legend.position = "none",
    plot.title.position = 'plot',
    plot.margin = margin(20, 25, 10, 20)
  ) +
  coord_cartesian(xlim = c(xlim_inf_ab, xlim_sup_ab))


b = both_posteriors_evidence %>%
  
  # make it tidy for ggplot
  pivot_longer(
    cols = c(everything()),
    names_to = "dist", values_to = "samples"
  ) %>%
  
  ggplot(aes(x = 100 * samples, y = factor(dist, level = level_order), fill = dist)) +
  
  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(position = "dodge") +
  geom_vline(aes(xintercept = 0), linetype = 2) + 
  scale_fill_manual(values = c(color3, color4)) +
  labs(x = "\nRisk difference (%)",
       y = "Corticosteroids\n",
       title = "Posterior distributions using evidence-based priors"
  ) +
  scale_x_continuous(breaks = seq(from = xlim_inf_ab, to = xlim_sup_ab,
                                  ticks_spacing_ab)) +
  scale_y_discrete(expand = c(0, 0.3)) +
  theme(
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    legend.position = "none",
    plot.title.position = 'plot',
    plot.margin = margin(20, 25, 10, 20)
  ) +
  coord_cartesian(xlim = c(xlim_inf_ab, xlim_sup_ab))

p1 = both_posteriors_non_informative %>% 
  summarise(difference = (`Using` - `Not using`) * 100) %>% 
  
  ggplot(aes(difference)) +
  
  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(
    .width = 0.95,
    fill = color5
  ) +
  labs(x = "Difference (%)", y = "Density",
       title = "Non-informative priors") +
  scale_x_continuous(breaks = seq(from = xlim_inf_diff, to = xlim_sup_diff,
                                  ticks_spacing_diff)) +
  scale_y_discrete(
    breaks = NULL,
    expand = c(0, .03)
  ) +
  theme(
    axis.ticks.x = element_blank(),
    # axis.ticks.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    legend.position = "none"
  ) +
  coord_cartesian(xlim = c(xlim_inf_diff, xlim_sup_diff))

p2 = both_posteriors_non_informative %>%
  summarise(difference = (`Using` - `Not using`) * 100) %>%
  
  ggplot(aes(difference)) +
  stat_ecdf(geom = "step") +
  
  labs( x = "Difference (%)",
        y = "Probability RD \u2264 X"
  ) +
  scale_x_continuous(
    breaks = seq(from = xlim_inf_diff, to = xlim_sup_diff, ticks_spacing_diff),
    limits = c(xlim_inf_diff, xlim_sup_diff)
  ) +
  scale_y_continuous(
    breaks = seq(from = 0, to = 1, .1),
    expand = c(0, .03)
  ) +
  theme(
    axis.ticks.x = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    panel.grid.major.y = element_line(color = "gray80", size = 0.3),
    plot.title.position = "plot",
    legend.position = "none",
  )

p3 = both_posteriors_evidence %>% 
  summarise(difference = (`Using` - `Not using`) * 100) %>% 
  
  ggplot(aes(difference)) +
  
  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(
    .width = 0.95,
    fill = color6
  ) +
  labs(x = "Difference (%)", y = "Density",
       title = "Evidence-based priors") +
  scale_x_continuous(breaks = seq(from = xlim_inf_diff, to = xlim_sup_diff,
                                  ticks_spacing_diff)) +
  scale_y_discrete(
    breaks = NULL,
    expand = c(0, .03)
  ) +
  theme(axis.ticks.x = element_blank(),
        # axis.ticks.y = element_blank(),
        panel.background = element_blank(),
        panel.grid.major.x = element_line(color = "gray80", size = 0.3),
        legend.position = "none"
  ) +
  coord_cartesian(xlim = c(xlim_inf_diff, xlim_sup_diff))

p4 = both_posteriors_evidence %>%
  summarise(difference = (`Using` - `Not using`) * 100) %>%
  
  ggplot(aes(difference)) +
  stat_ecdf(geom = "step") +
  
  labs(
    x = "Difference (%)",
    y = "Probability RD \u2264 X"
  ) +
  scale_x_continuous(
    breaks = seq(from = xlim_inf_diff, to = xlim_sup_diff, ticks_spacing_diff),
    limits = c(xlim_inf_diff, xlim_sup_diff)
  ) +
  scale_y_continuous(
    breaks = seq(from = 0, to = 1, .1),
    expand = c(0, .03)
  ) +
  theme(
    axis.ticks.x = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    panel.grid.major.y = element_line(color = "gray80", size = 0.3),
    plot.title.position = "plot",
    legend.position = "none",
  )
```

```{r, fig.align='center', fig.cap = "Interval bars depict 50% and 95% credible intervals"}
a / b
```

```{r fig.align='center', fig.height=7.5, fig.width=6, warning=FALSE, fig.cap="The interval bar depicts the 95% credible interval. The cumulative posterior distribution corresponds to the probabilities that the risk difference (RD) is less than or equal to the effect size on the X‐axis."}
(p1 + p2) / (p3 + p4)
```

## Hospital discharge outcome

**The baseline risks are very different between groups. Thus, we have decided that the following results are not trustworthy. They will be displayed below  just for the sake of completion, but they will not be included in the final manuscript.**

Each risk difference represents the delta between the effect on tocilizumab minus
control. Positive risk differences mean benefit.

```{r, fig.align='center', fig.height=4, fig.width=7, fig.cap="While the darker shaded area depicts the 50% credible interval (CI), the interval bar depicts the 95% CI."}

## Plot!

# I will use my own functions to standardize my plots

risk_comparison_plot(
  noninformative_recovery_using_cortico_discharge, # Data object

  ### start using quotes
  
  "gray50", # Color code for control group
  carto_pal(7, "Peach")[4], # Color code for other group
  "\nRisk (%)", # X axis label
  "", # Title
  "Using corticosteroids\n", # Subtitle
  
  ### stop using quotes

  36, # X axis inferior limit
  62, # X axis superior limit
  2 # X axis spacing for ticks
  

) + coord_cartesian(xlim = c(36, 62))
```

```{r, fig.align='center', fig.height=4, fig.width=7, fig.cap="While the darker shaded area depicts the 50% credible interval (CI), the interval bar depicts the 95% CI."}

## Plot!

# I will use my own functions to standardize my plots

risk_comparison_plot(
  noninformative_recovery_not_cortico_discharge, # Data object
  
  ### start using quotes
  
  "gray50", # Color code for control group
  carto_pal(7, "Purp")[4], # Color code for other group
  "\nRisk (%)", # X axis label
  "", # Title
  "Not using corticosteroids\n", # Subtitle
  
  ### stop using quotes
  
  36, # X axis inferior limit
  62, # X axis superior limit
  2 # X axis spacing for ticks
) + coord_cartesian(xlim = c(36, 62))
```

```{r}
# all_posteriors data frame 1
posteriors_group1 = all_posteriors_using_cortico_discharge
# all_posteriors data frame 2
posteriors_group2 = all_posteriors_not_cortico_discharge
# X axis limits (inf + sup) and ticks spacing (a+b)
xlim_inf_ab = -12.5
xlim_sup_ab = 12.5
ticks_spacing_ab = 2.5
# X axis limits (inf + sup) and ticks spacing (p1~p4)
xlim_inf_diff = -6
xlim_sup_diff = 21
ticks_spacing_diff = 3
# Colors for plot a
color1 = carto_pal(7, "Peach")[3]
color2 = carto_pal(7, "Peach")[5]
# Colors for plot b
color3 = carto_pal(7, "Purp")[3]
color4 = carto_pal(7, "Purp")[5]
# Colors for plot p1 + p2
color5 = carto_pal(7, "Peach")[6]
color6 = carto_pal(7, "Purp")[6]

```

```{r}
# Plot!

both_posteriors_non_informative = 
  # Posterior distribution on risk differences between patients on
  # tocilizumab vs. usual care (both using corticosteroids)
  posteriors_group1 %>% 
  select("Non-informative") %>% 
  rename("Using" = "Non-informative") %>% 
  # Posterior distribution on risk differences between patients on
  # tocilizumab vs. usual care (both NOT using corticosteroids)
  bind_cols(posteriors_group2 %>% select("Non-informative")) %>% 
  rename("Not using" = "Non-informative")

both_posteriors_evidence = 
  # Posterior distribution on risk differences in mortality between patients on
  # tocilizumab vs. usual care (both using corticosteroids)
  posteriors_group1 %>% 
  select("Evidence-based") %>% 
  rename("Using" = "Evidence-based") %>% 
  # Posterior distribution on risk differences in mortality between patients on
  # tocilizumab vs. usual care (both NOT using corticosteroids)
  bind_cols(posteriors_group2 %>% select("Evidence-based")) %>% 
  rename("Not using" = "Evidence-based")


#### Plot risk differences side-by-side

# Assure subgroup order
# https://stackoverflow.com/questions/12774210/
# how-do-you-specifically-order-ggplot2-x-axis-instead-of-alphabetical-order

level_order = c("Not using",
                "Using")

a = both_posteriors_non_informative %>%
  
  # make it tidy for ggplot
  pivot_longer(
    cols = c(everything()),
    names_to = "dist", values_to = "samples"
  ) %>%
  
  ggplot(aes(x = 100 * samples, y = factor(dist, level = level_order),
             fill = dist)) +
  
  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(position = "dodge") +
  geom_vline(aes(xintercept = 0), linetype = 2) + 
  scale_fill_manual(values = c(color1, color2)) +
  labs(x = "\n",
       y = "Corticosteroids\n",
       title = "Posterior distributions using non-informative priors"
  ) +
  scale_x_continuous(breaks = seq(from = xlim_inf_ab, to = xlim_sup_ab,
                                  ticks_spacing_ab)) +
  scale_y_discrete(expand = c(0, 0.3)) +
  theme(
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    legend.position = "none",
    plot.title.position = 'plot',
    plot.margin = margin(20, 25, 10, 20)
  ) +
  coord_cartesian(xlim = c(xlim_inf_ab, xlim_sup_ab))


b = both_posteriors_evidence %>%
  
  # make it tidy for ggplot
  pivot_longer(
    cols = c(everything()),
    names_to = "dist", values_to = "samples"
  ) %>%
  
  ggplot(aes(x = 100 * samples, y = factor(dist, level = level_order), fill = dist)) +
  
  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(position = "dodge") +
  geom_vline(aes(xintercept = 0), linetype = 2) + 
  scale_fill_manual(values = c(color3, color4)) +
  labs(x = "\nRisk difference (%)",
       y = "Corticosteroids\n",
       title = "Posterior distributions using evidence-based priors"
  ) +
  scale_x_continuous(breaks = seq(from = xlim_inf_ab, to = xlim_sup_ab,
                                  ticks_spacing_ab)) +
  scale_y_discrete(expand = c(0, 0.3)) +
  theme(
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    legend.position = "none",
    plot.title.position = 'plot',
    plot.margin = margin(20, 25, 10, 20)
  ) +
  coord_cartesian(xlim = c(xlim_inf_ab, xlim_sup_ab))

p1 = both_posteriors_non_informative %>% 
  summarise(difference = (`Using` - `Not using`) * 100) %>% 
  
  ggplot(aes(difference)) +
  
  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(
    .width = 0.95,
    fill = color5
  ) +
  labs(x = "Difference (%)", y = "Density",
       title = "Non-informative priors") +
  scale_x_continuous(breaks = seq(from = xlim_inf_diff, to = xlim_sup_diff,
                                  ticks_spacing_diff)) +
  scale_y_discrete(
    breaks = NULL,
    expand = c(0, .03)
  ) +
  theme(
    axis.ticks.x = element_blank(),
    # axis.ticks.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    legend.position = "none"
  ) +
  coord_cartesian(xlim = c(xlim_inf_diff, xlim_sup_diff))

p2 = both_posteriors_non_informative %>%
  summarise(difference = (`Using` - `Not using`) * 100) %>%
  
  ggplot(aes(difference)) +
  geom_line(aes(y = 1 - ..y..), stat='ecdf') +
  
  labs( x = "Difference (%)",
        y = "Probability RD \u2265 X"
  ) +
  scale_x_continuous(
    breaks = seq(from = xlim_inf_diff, to = xlim_sup_diff, ticks_spacing_diff),
    limits = c(xlim_inf_diff, xlim_sup_diff)
  ) +
  scale_y_continuous(
    breaks = seq(from = 0, to = 1, .1),
    expand = c(0, .03)
  ) +
  theme(
    axis.ticks.x = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    panel.grid.major.y = element_line(color = "gray80", size = 0.3),
    plot.title.position = "plot",
    legend.position = "none",
  )

p3 = both_posteriors_evidence %>% 
  summarise(difference = (`Using` - `Not using`) * 100) %>% 
  
  ggplot(aes(difference)) +
  
  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(
    .width = 0.95,
    fill = color6
  ) +
  labs(x = "Difference (%)", y = "Density",
       title = "Evidence-based priors") +
  scale_x_continuous(breaks = seq(from = xlim_inf_diff, to = xlim_sup_diff,
                                  ticks_spacing_diff)) +
  scale_y_discrete(
    breaks = NULL,
    expand = c(0, .03)
  ) +
  theme(axis.ticks.x = element_blank(),
        # axis.ticks.y = element_blank(),
        panel.background = element_blank(),
        panel.grid.major.x = element_line(color = "gray80", size = 0.3),
        legend.position = "none"
  ) +
  coord_cartesian(xlim = c(xlim_inf_diff, xlim_sup_diff))

p4 = both_posteriors_evidence %>%
  summarise(difference = (`Using` - `Not using`) * 100) %>%
  
  ggplot(aes(difference)) +
  geom_line(aes(y = 1 - ..y..), stat='ecdf') +
  
  labs(
    x = "Difference (%)",
    y = "Probability RD \u2265 X"
  ) +
  scale_x_continuous(
    breaks = seq(from = xlim_inf_diff, to = xlim_sup_diff, ticks_spacing_diff),
    limits = c(xlim_inf_diff, xlim_sup_diff)
  ) +
  scale_y_continuous(
    breaks = seq(from = 0, to = 1, .1),
    expand = c(0, .03)
  ) +
  theme(
    axis.ticks.x = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    panel.grid.major.y = element_line(color = "gray80", size = 0.3),
    plot.title.position = "plot",
    legend.position = "none",
  )
```

```{r, fig.align='center', fig.cap = "Interval bars depict 50% and 95% credible intervals"}
a / b
```

```{r fig.align='center', fig.height=7.5, fig.width=6, warning=FALSE, , fig.cap="The interval bar depicts the 95% credible interval. The cumulative posterior distribution corresponds to the probabilities that the risk difference (RD) is greater than or equal to the effect size on the X‐axis."}
(p1 + p2) / (p3 + p4)
```

<br><br>

```{r}
sessionInfo()
```

