---
title: "14_Evaluating_Heterogeneity"
author: "Arthur M. Albuquerque"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
          code_folding: hide
          toc: yes
          toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(tidyverse)
library(kableExtra)
```
In this project, we are analyzing the effect of tocilizumab versus usual care for
COVID-19. We decided to focus on two clusters of subgroups: **respiratory support**
and **use of corticosteroids**. 

In this document, we will evaluate the **heterogeneity between trials**. We will
perform two separate analyses. 

First, we are going to check the **proportion** of patients in each treatment arm
and trial that were on **use of corticosteroids**. This information is of utmost
importance due to the beneficial effect of this drug class for patients with
COVID-19. Thus, any **substantial disbalance** between treatment arms would **affect**
**subgroup analyses** regarding **respiratory support**. I am only going to present data
from trials we have outcome data subgrouped by respiratory support.


```{r}
tibble(
  
  Trial = c("RECOVERY",
            "REMAP-CAP",
            "CORIMUNO-19",
            "COVACTA",
            "Salvarini",
            "TOCIBRAS"),
  
  "Tocilizumab arm" = c(82, # RECOVERY
                        90, # REMAP-CAP
                        33, # CORIMUNO-19
                        36, # COVACTA
                        10, # Salvarini
                        69  # TOCIBRAS
                        ),
    
  "Control arm" = c(82, # RECOVERY
                    91, # REMAP-CAP
                    61, # CORIMUNO-19
                    55, # COVACTA
                    11, # Salvarini
                    73  # TOCIBRAS
                    )
) %>% 
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1,
                     "Proportion of patients on corticosteroids (%)" = 2))
```

<br> 

Now, let's evaluate the **proportion** of patients in each subgroup regarding
**respiratory support**. It is important to check if there is any substantial **disbalance** 
between trials, which would **impact** the results of subgroups regarding **use of 
corticosteroids**. I am only going to present data from trials we have outcome data
subgrouped by use of corticosteroids.

```{r}
tibble(
  Trial = c(
    "RECOVERY",
    "REMAP-CAP",
    "COVACTA"
  ),
  
  ## No supplemental oxygen
  
  "Tocilizumab" = c(
    0, # RECOVERY
    0, # REMAP-CAP
    3 # COVACTA
  ),
  
  "Control" = c(
    0, # RECOVERY
    0, # REMAP-CAP
    4 # COVACTA
  ),
  
 ## Simple oxygen only
  
  "Tocilizumab " = c(
    46, # RECOVERY
    1, # REMAP-CAP
    26 # COVACTA
  ),
  
  "Control " = c(
    45, # RECOVERY
    1, # REMAP-CAP
    31 # COVACTA
  ),
 
 ## Noninvasive ventilation
  
  "Tocilizumab  " = c(
    41, # RECOVERY
    71, # REMAP-CAP
    32 # COVACTA
  ),
  
  "Control  " = c(
    41, # RECOVERY
    69, # REMAP-CAP
    27 # COVACTA
  ),
 
 ## Invasive mechanical ventilation
  
  "Tocilizumab   " = c(
    13, # RECOVERY
    29, # REMAP-CAP
    38 # COVACTA
  ),
  
  "Control   " = c(
    14, # RECOVERY
    30, # REMAP-CAP
    38 # COVACTA
  )
  
) %>% 
  kbl(booktabs = T, align = 'c') %>% 
  kable_minimal() %>% 
  add_header_above(c(" " = 1,
                     "No supplemental oxygen" = 2,
                     "Simple oxygen only" = 2,
                     "Non-invasive ventilation" = 2,
                     "Invasive mechanical ventilation" = 2)) %>% 
  add_header_above(c(" " = 1,
  "Proportion of patients (%)" = 8))
```

<br>