---
title: "15_Figures_Draft"
author: "Arthur M. Albuquerque"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
          toc: yes
          toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE) # no code
```

```{r include=FALSE}
# Ensures the package "pacman" is installed
if (!require("pacman")) install.packages("pacman")

# p_load() installs (if necessary) and loads the following packages

pacman::p_load(rio, # To import data
               here, # To find file paths within R project
               janitor, # To change column names
               tidyverse, # Data wrangling and plotting
               ggdist, # To plot distributions
               patchwork, # To arrange plots
               kableExtra # To create nice tables
               )
```


```{r}
## Load objects with mean + SD of multiple priors along with
## RECOVERY data and posterior distributions

load(file = here("final_analyses", "output", "data",
                 "multiple_priors_death.RData"))

## Load rma() objects with prior, data and posteriors for
## the corticosteroids analyses 

load(here("final_analyses", "output", "data",
                  "multiple_priors_100_using_cortico_death.RData"))

load(here("final_analyses", "output", "data",
                  "multiple_priors_100_not_cortico_death.RData"))

# Load data extraction table

d = import((here("final_analyses", "output", "data", # file path
                   "respiratory-data.csv")),           # file name
             header = T)
d = d %>% 
  as_tibble() %>% 
  select(!starts_with("X")) 

# Create different variables per subgroup

priors_simple_oxygen_raw =
  d %>%
  filter(
    trial != "RECOVERY",
    oxygen == "simple oxygen",
    outcome == "mortality"
  )

priors_noninvasive_raw =
  d %>%
  filter(
    trial != "RECOVERY",
    oxygen == "non-invasive ventilation",
    outcome == "mortality"
  )

priors_invasive_raw =
  d %>%
  filter(
    trial != "RECOVERY",
    oxygen == "invasive ventilation",
    outcome == "mortality"
  )

# Load corticosteroids raw data

d_cortico = import(here("final_analyses", "data", # file path
                            "corticosteroids_subgroup_extracted-data.xlsx"))

d_cortico = clean_names(d_cortico)

priors_not_using =
  d_cortico %>%
  filter(
    trial != "RECOVERY",
    corticosteroids == 0,
    outcome == "mortality"
  )

priors_using =
  d_cortico %>%
  filter(
    trial != "RECOVERY",
    corticosteroids == 1,
    outcome == "mortality"
  )

## Load objets with all the posterior for sensitivity analyses

load(here("final_analyses", "output", "data",
                 "all_posteriors_death.RData"))

```

```{r}
# Set seed for reproducibility

set.seed = 123 
```

<br>

**In this document, I will only present data regarding the mortality outcome. Thus, negative risk differences mean benefit.**

## Table 1: Overall view of the data

Here, the primary aim is to give an overall view of how many patients are
involved in each subgroup and study.

```{r}
t = tibble(
  
  "Subgroup" = c(
    "Not using",
    "Using",
    
    "Simple oxygen only",
    "Non-invasive ventilation",
    "Invasive mechanical ventilation"
    
  ),
  
  ## Priors
  
  "Number of studies" = c(
    
    priors_not_using %>%
      count() %>% pull(),
    priors_using %>%
      count() %>% pull(),
    
    priors_simple_oxygen_raw %>%
      count() %>% pull(),
    priors_noninvasive_raw %>%
      count() %>% pull(),
    priors_invasive_raw %>%
      count() %>% pull()
    
  ),
  
  # Control arm
  
  "Events  " = c(
    
    priors_not_using %>%
    summarise(n = sum(events_control)) %>% pull(),
    priors_using %>%
      summarise(n = sum(events_control)) %>% pull(),
    
    priors_simple_oxygen_raw %>%
      summarise(n = sum(events_control)) %>% pull(),
    priors_noninvasive_raw %>%
      summarise(n = sum(events_control)) %>% pull(),
    priors_invasive_raw %>%
      summarise(n = sum(events_control)) %>% pull()

  ),
  
  "Total  " = c(
    
    priors_not_using %>%
      summarise(n = sum(total_control)) %>% pull(),
    priors_using %>%
      summarise(n = sum(total_control)) %>% pull(),
    
    priors_simple_oxygen_raw %>%
      summarise(n = sum(total_control)) %>% pull(),
    priors_noninvasive_raw %>%
      summarise(n = sum(total_control)) %>% pull(),
    priors_invasive_raw %>%
      summarise(n = sum(total_control)) %>% pull()

  ),
  
  # Tocilizumab arm
  
  "Events   " = c(
    priors_not_using %>%
      summarise(n = sum(events_toci)) %>% pull(),
    priors_using %>%
      summarise(n = sum(events_toci)) %>% pull(),
    
    priors_simple_oxygen_raw %>%
      summarise(n = sum(events_toci)) %>% pull(),
    priors_noninvasive_raw %>%
      summarise(n = sum(events_toci)) %>% pull(),
    priors_invasive_raw %>%
      summarise(n = sum(events_toci)) %>% pull()
    
  ),
  
  "Total   " = c(
    priors_not_using %>%
      summarise(n = sum(total_toci)) %>% pull(),
    priors_using %>%
      summarise(n = sum(total_toci)) %>% pull(),
    
    priors_simple_oxygen_raw %>%
      summarise(n = sum(total_toci)) %>% pull(),
    priors_noninvasive_raw %>%
      summarise(n = sum(total_toci)) %>% pull(),
    priors_invasive_raw %>%
      summarise(n = sum(total_toci)) %>% pull()

  ),
  
  ## RECOVERY
  
  # Control arm
  
  "Events" = c(
    d_cortico %>%
      filter(trial == "RECOVERY",
             outcome == "mortality",
             corticosteroids == 0) %>% 
      select(events_control) %>% pull(),
    d_cortico %>%
      filter(trial == "RECOVERY",
             outcome == "mortality",
             corticosteroids == 1) %>% 
      select(events_control) %>% pull(),
    
    d %>%
      filter(trial == "RECOVERY",
             outcome == "mortality",
             oxygen == "simple oxygen") %>% 
      select(events_control) %>% pull(),
    d %>%
      filter(trial == "RECOVERY",
             outcome == "mortality",
             oxygen == "non-invasive ventilation") %>% 
      select(events_control) %>% pull(),
    d %>%
      filter(trial == "RECOVERY",
             outcome == "mortality",
             oxygen == "invasive ventilation") %>% 
      select(events_control) %>% pull()

  ),
  
  "Total" = c(
    
    d_cortico %>%
      filter(trial == "RECOVERY",
             outcome == "mortality",
             corticosteroids == 0) %>% 
      select(total_control) %>% pull(),
    d_cortico %>%
      filter(trial == "RECOVERY",
             outcome == "mortality",
             corticosteroids == 1) %>% 
      select(total_control) %>% pull(),
    
    d %>%
      filter(trial == "RECOVERY",
             outcome == "mortality",
             oxygen == "simple oxygen") %>% 
      select(total_control) %>% pull(),
    d %>%
      filter(trial == "RECOVERY",
             outcome == "mortality",
             oxygen == "non-invasive ventilation") %>% 
      select(total_control) %>% pull(),
    d %>%
      filter(trial == "RECOVERY",
             outcome == "mortality",
             oxygen == "invasive ventilation") %>% 
      select(total_control) %>% pull()

  ),
  
  # Tocilizumab arm
  
  "Events " = c(
    d_cortico %>%
      filter(trial == "RECOVERY",
             outcome == "mortality",
             corticosteroids == 0) %>% 
      select(events_toci) %>% pull(),
    d_cortico %>%
      filter(trial == "RECOVERY",
             outcome == "mortality",
             corticosteroids == 1) %>% 
      select(events_toci) %>% pull(),
    
    d %>%
      filter(trial == "RECOVERY",
             outcome == "mortality",
             oxygen == "simple oxygen") %>% 
      select(events_toci) %>% pull(),
    d %>%
      filter(trial == "RECOVERY",
             outcome == "mortality",
             oxygen == "non-invasive ventilation") %>% 
      select(events_toci) %>% pull(),
    d %>%
      filter(trial == "RECOVERY",
             outcome == "mortality",
             oxygen == "invasive ventilation") %>% 
      select(events_toci) %>% pull()

  ),
  
  "Total " = c(
    
    d_cortico %>%
      filter(trial == "RECOVERY",
             outcome == "mortality",
             corticosteroids == 0) %>% 
      select(total_toci) %>% pull(),
    d_cortico %>%
      filter(trial == "RECOVERY",
             outcome == "mortality",
             corticosteroids == 1) %>% 
      select(total_toci) %>% pull(),
    
    d %>%
      filter(trial == "RECOVERY",
             outcome == "mortality",
             oxygen == "simple oxygen") %>% 
      select(total_toci) %>% pull(),
    d %>%
      filter(trial == "RECOVERY",
             outcome == "mortality",
             oxygen == "non-invasive ventilation") %>% 
      select(total_toci) %>% pull(),
    d %>%
      filter(trial == "RECOVERY",
             outcome == "mortality",
             oxygen == "invasive ventilation") %>% 
      select(total_toci) %>% pull()

  )
  
)

# Use kableExtra to have a nice table

t %>% 
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 2,
                     "Control" = 2,
                     "Tocilizumab" = 2,
                     "Control" = 2,
                     "Tocilizumab" = 2)) %>% 
  add_header_above(c(" " = 1,
                     "Priors" = 5,
                     "RECOVERY" = 4)) %>% 
  pack_rows("Use of corticosteroids", 1, 2) %>% 
  pack_rows("Respiratory support", 3, 5)
```

<br><br>

## Figure 1: Overall view of the data

Here, the primary aim is to visually present our priors and the RECOVERY.
I believe it is extremely important to present this data in a figure since
they are the foundation underlying the posterior distributions in the next
figures.

```{r}
## Respiratory support

# Create data frame

# Simple oxygen subgroup

distributions_s =
  multiple_priors_simple_oxygen_death %>%
  filter(type == "evidence-based") %>%
  summarise(
    RECOVERY_s = list(rnorm(10e4,
      mean = data.mean,
      sd = data.sd
    )),
    Prior_s = list(rnorm(10e4,
      mean = prior.mean,
      sd = prior.sd
    ))
  ) %>%
  unnest(RECOVERY_s:Prior_s)

# Non-invasive ventilation

distributions_n =
  multiple_priors_noninvasive_death %>%
  filter(type == "evidence-based") %>%
  summarise(
    RECOVERY_n = list(rnorm(10e4,
      mean = data.mean,
      sd = data.sd
    )),
    Prior_n = list(rnorm(10e4,
      mean = prior.mean,
      sd = prior.sd
    ))
  ) %>%
  unnest(RECOVERY_n:Prior_n)

# Invasive mechanical ventilation subgroup

distributions_i =
  multiple_priors_invasive_death %>%
  filter(type == "evidence-based") %>%
  summarise(
    RECOVERY_i = list(rnorm(10e4,
      mean = data.mean,
      sd = data.sd
    )),
    Prior_i = list(rnorm(10e4,
      mean = prior.mean,
      sd = prior.sd
    ))
  ) %>%
  unnest(RECOVERY_i:Prior_i)

# Bind altogether

distributions_respiratory = bind_cols(
  distributions_i,
  distributions_n,
  distributions_s
)
```

```{r}
# Plot!

p1 = distributions_respiratory %>%
  # make it tidy for ggplot
  pivot_longer(
    cols = c(RECOVERY_i:Prior_s),
    names_to = "dist", values_to = "samples"
  ) %>%
  mutate(
    # Create new column to be able to use facet at the end
    subgroup = case_when(
      str_detect(dist, "_s") ~ "Simple oxygen only",
      str_detect(dist, "_n") ~ "Non-invasive ventilation",
      str_detect(dist, "_i") ~ "Invasive mechanical ventilation"
    ),

    # Set order of subgroups
    subgroup = factor(subgroup,
      levels = c(
        "Simple oxygen only",
        "Non-invasive ventilation",
        "Invasive mechanical ventilation"
      )
    ),

    # Remove "_i", "_n" and "_s"
    dist = case_when(
      str_detect(dist, "RECOVERY") ~ "RECOVERY",
      str_detect(dist, "Prior") ~ "Priors",
    ),
    # Set order of distributions
    dist = factor(dist,
      levels = c(
        "RECOVERY",
        "Priors"
      )
    )
  ) %>%
  ggplot(aes(
    x = 100 * samples, y = dist,
    fill = dist
  )) +

  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(position = "dodge",
               point_interval = median_qi,
               .width = c(0.50, 0.95)) +
  scale_fill_manual(values = c(
    "#67B8D5", # RECOVERY
    "#F8DCCA" # Prior
  )) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.6) +
  labs(
    x = "\nRisk Difference (%)",
    y = " "
  ) +
  scale_x_continuous(breaks = seq(from = -16, to = 12, 4)) +
  coord_cartesian(xlim = c(-16, 12)) +
  scale_y_discrete(expand = c(0, 0.5)) +
  theme(
    strip.background = element_rect(fill = "#E4E6E7"),
    strip.text.x = element_text(size = 12),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    legend.position = 'none',
    plot.margin = margin(20, 15, 0, 0)
  ) +
  facet_wrap(~subgroup, ncol = 1)
```

```{r}
# Corticosteroids subgroups

# Create data frame

# Using corticosteroids subgroup

distributions_u =
  multiple_priors_100_using_cortico_death %>%
  filter(type == "evidence-based") %>%
  summarise(
    RECOVERY_u = list(rnorm(10e4,
      mean = data.mean,
      sd = data.sd
    )),
    Prior_u = list(rnorm(10e4,
      mean = prior.mean,
      sd = prior.sd
    ))
  ) %>%
  unnest(RECOVERY_u:Prior_u)

# Not using corticosteroids subgroup

distributions_not =
  multiple_priors_100_not_cortico_death %>%
  filter(type == "evidence-based") %>%
  summarise(
    RECOVERY_not = list(rnorm(10e4,
      mean = data.mean,
      sd = data.sd
    )),
    Prior_not = list(rnorm(10e4,
      mean = prior.mean,
      sd = prior.sd
    ))
  ) %>%
  unnest(RECOVERY_not:Prior_not)

# Bind altogether

distributions_cortico = bind_cols(
  distributions_u,
  distributions_not
)
    

```


```{r}
# Plot!

p2 = distributions_cortico %>%
  # make it tidy for ggplot
  pivot_longer(
    cols = c(RECOVERY_u:Prior_not),
    names_to = "dist", values_to = "samples"
  ) %>%
  mutate(
    # Create new column to be able to use facet at the end
    subgroup = case_when(
      str_detect(dist, "_u") ~ "Using corticosteroids",
      str_detect(dist, "_not") ~ "Not using corticosteroids"
    ),

    # Set order of subgroups
    subgroup = factor(subgroup,
      levels = c(
        "Not using corticosteroids",
        "Using corticosteroids"
      )
    ),

    # Remove "_u" and "_not"
    dist = case_when(
      str_detect(dist, "RECOVERY") ~ "RECOVERY",
      str_detect(dist, "Prior") ~ "Priors",
    ),
    # Set order of distributions
    dist = factor(dist,
      levels = c(
        "RECOVERY",
        "Priors"
      )
    )
  ) %>%
  ggplot(aes(
    x = 100 * samples, y = dist,
    fill = dist
  )) +

  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(position = "dodge",
               point_interval = median_qi,
               .width = c(0.50, 0.95)) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.6) +
  scale_fill_manual(' ',
                    breaks=c("Priors","RECOVERY"),
                    values = c(
    "#F8DCCA", # Prior
     "#67B8D5" # RECOVERY
  )) +
  labs(
    x = "\nRisk Difference (%)",
    y = " "
  ) +
  scale_x_continuous(breaks = seq(from = -16, to = 12, 4)) +
  coord_cartesian(xlim = c(-15, 12)) +
  scale_y_discrete(expand = c(0, 0.5)) +
  theme(
    strip.background = element_rect(fill = "#E4E6E7"),
    strip.text.x = element_text(size = 12),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    legend.position = 'right',
    legend.text = element_text(size=12),
    legend.key= element_blank(),
    plot.margin = margin(20, 0, 15, 25)
  ) +
  facet_wrap(~subgroup, ncol = 1)
```

```{r, fig.align='center', fig.width=10, fig.height = 6, fig.cap="Point estimates depict the median. Interval bars depict the 50th and 95th quantiles."}
p2 + p1 + plot_annotation(tag_levels = 'A')
```

<br><br>

## Figure 2: Posterior distributions

In my opinion, this is the most important figure. I decided not to use tables,
because there are too much data and Panel B and D seem to handle well this
great amount of data.

```{r}
# Create data frame

# Using corticosteroids subgroup

distributions_u_posterior =
  multiple_priors_100_using_cortico_death %>%
  filter(type == "evidence-based") %>%
  summarise(
    Posterior_u = list(rnorm(10e4,
      mean = post.mean,
      sd = post.sd
    ))
  ) %>%
  unnest(Posterior_u)

# Not using corticosteroids subgroup

distributions_not_posterior =
  multiple_priors_100_not_cortico_death %>%
  filter(type == "evidence-based") %>%
  summarise(
    Posterior_not = list(rnorm(10e4,
      mean = post.mean,
      sd = post.sd
    ))
  ) %>%
  unnest(Posterior_not)

# Bind altogether

distributions_cortico_posterior = bind_cols(
  distributions_u_posterior,
  distributions_not_posterior
)
```

```{r}
p1 = distributions_cortico_posterior %>%
  # make it tidy for ggplot
  pivot_longer(
    cols = c(Posterior_u:Posterior_not),
    names_to = "dist", values_to = "samples"
  ) %>%
  mutate(
    # Create new column to be able to use facet at the end
    subgroup = case_when(
      str_detect(dist, "_u") ~ "Using corticosteroids",
      str_detect(dist, "_not") ~ "Not using corticosteroids"
    ),

    # Set order of subgroups
    subgroup = factor(subgroup,
      levels = c(
        "Not using corticosteroids",
        "Using corticosteroids"
      )
    )) %>%
  
  # Plot!
  ggplot(aes(
    x = 100 * samples, y = dist,
    fill = subgroup
  )) +

  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(point_interval = median_qi,
               .width = c(0.50, 0.95)) +
  scale_fill_manual(values = c("#9EA45B", "#A65041")) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.6) +
  labs(
    x = "\nRisk Difference (%)",
    y = " "
  ) +
  scale_x_continuous(breaks = seq(from = -12, to = 12, 4)) +
  coord_cartesian(xlim = c(-12, 12)) +
  scale_y_discrete(expand = c(0, 0.5)) +
  theme(
    strip.background = element_rect(fill = "#E4E6E7"),
    strip.text.x = element_text(size = 12),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    legend.position = 'none',
    plot.margin = margin(20, 10, 20, 10)
  ) +
  facet_wrap(~subgroup, ncol = 1, scales = "free_y")
```

```{r warning=FALSE, include=FALSE}
p2 = distributions_cortico_posterior %>%
  # make it tidy for ggplot
  pivot_longer(
    cols = c(Posterior_u:Posterior_not),
    names_to = "dist", values_to = "samples"
  ) %>%
  mutate(
    # Create new column to be able to use facet at the end
    subgroup = case_when(
      str_detect(dist, "_u") ~ "Using corticosteroids",
      str_detect(dist, "_not") ~ "Not using corticosteroids"
    ),

    # Set order of subgroups
    subgroup = factor(subgroup,
      levels = c(
        "Not using corticosteroids",
        "Using corticosteroids"
      )
    )) %>% 

ggplot(aes(100*samples, colour = subgroup)) +
  stat_ecdf(geom = "step",
            size = 1) +
  scale_color_manual(' ',
                    values = c("#9EA45B", "#A65041")) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.6) +
    labs(
      x = "\nRisk Difference (%)",
      y = "Probability RD \u2264 X\n"
      ) +
    scale_x_continuous(
      breaks = seq(from = -12, to = 12, 2),
      limits = c(-12, 12)) +
    scale_y_continuous(
      breaks = seq(from = 0, to = 1, .1),
      expand = c(0, .03)
    ) +
  theme(
      axis.ticks.x = element_blank(),
      panel.background = element_blank(),
      panel.grid.major.x = element_line(color = "gray80", size = 0.3),
      panel.grid.major.y = element_line(color = "gray80", size = 0.3),
      legend.position = 'none',
      plot.margin = margin(20, 10, 20, 10)
    )
```


```{r}
# Create data frame

# Simple oxygen only

distributions_s =
  multiple_priors_simple_oxygen_death %>%
  filter(type == "evidence-based") %>%
  summarise(
    Posterior_s = list(rnorm(10e4,
      mean = post.mean,
      sd = post.sd
    ))) %>%
  unnest(Posterior_s)

# Non-invasive ventilation

distributions_n =
  multiple_priors_noninvasive_death %>%
  filter(type == "evidence-based") %>%
  summarise(
    Posterior_n = list(rnorm(10e4,
      mean = post.mean,
      sd = post.sd
    ))) %>%
  unnest(Posterior_n)

# Invasive mechanical ventilation subgroup

distributions_i =
  multiple_priors_invasive_death %>%
  filter(type == "evidence-based") %>%
  summarise(
    Posterior_i = list(rnorm(10e4,
      mean = post.mean,
      sd = post.sd
    ))) %>%
  unnest(Posterior_i)

# Bind altogether

distributions_respiratory_posterior = bind_cols(
  distributions_i,
  distributions_n,
  distributions_s
)

```

```{r}

p3 = distributions_respiratory_posterior %>%
  # make it tidy for ggplot
  pivot_longer(
    cols = c(Posterior_i:Posterior_s),
    names_to = "dist", values_to = "samples"
  ) %>%
  mutate(
    # Create new column to be able to use facet at the end
    subgroup = case_when(
      str_detect(dist, "_s") ~ "Simple oxygen only",
      str_detect(dist, "_n") ~ "Non-invasive ventilation",
      str_detect(dist, "_i") ~ "Invasive mechanical ventilation"
    ),

    # Set order of subgroups
    subgroup = factor(subgroup,
      levels = c(
        "Simple oxygen only",
        "Non-invasive ventilation",
        "Invasive mechanical ventilation"
      ))
    ) %>%
  # Plot!
  ggplot(aes(
    x = 100 * samples, y = dist,
    fill = subgroup
  )) +

  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(point_interval = median_qi,
               .width = c(0.50, 0.95)) +
  scale_fill_manual(values = c("#D9BC8C", # Simple oxyge
                               "#9d95c6", # Non-invasive
                               "#7D8D87") # Invasive
                    ) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.6) +
  labs(
    x = "\nRisk Difference (%)",
    y = " "
  ) +
  scale_x_continuous(breaks = seq(from = -12, to = 12, 4)) +
  coord_cartesian(xlim = c(-12, 12)) +
  scale_y_discrete(expand = c(0, 0.5)) +
  theme(
    strip.background = element_rect(fill = "#E4E6E7"),
    strip.text.x = element_text(size = 12),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    legend.position = 'none',
    plot.margin = margin(20, 10, 20, 10)
  ) +
  facet_wrap(~ subgroup, ncol = 1, scales = "free_y")
```

```{r warning=FALSE}
p4 = distributions_respiratory_posterior %>%
  # make it tidy for ggplot
  pivot_longer(
    cols = c(Posterior_i:Posterior_s),
    names_to = "dist", values_to = "samples"
  ) %>%
  mutate(
    # Create new column to be able to use facet at the end
    subgroup = case_when(
      str_detect(dist, "_s") ~ "Simple oxygen only",
      str_detect(dist, "_n") ~ "Non-invasive ventilation",
      str_detect(dist, "_i") ~ "Invasive mechanical ventilation"
    ),

    # Set order of subgroups
    subgroup = factor(subgroup,
      levels = c(
        "Simple oxygen only",
        "Non-invasive ventilation",
        "Invasive mechanical ventilation"
      ))
    ) %>%

ggplot(aes(100*samples, colour = subgroup)) +
  stat_ecdf(geom = "step",
            size = 1) +
  scale_color_manual(' ',
                    values = c("#D9BC8C", # Simple oxyge
                               "#9d95c6", # Non-invasive
                               "#7D8D87") # Invasive
                    ) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.6) +
    labs(
      x = "\nRisk Difference (%)",
      y = "Probability RD \u2264 X\n"
      ) +
    scale_x_continuous(
      breaks = seq(from = -12, to = 12, 2),
      limits = c(-12, 12)) +
    scale_y_continuous(
      breaks = seq(from = 0, to = 1, .1),
      expand = c(0, .03)
    ) +
  theme(
      axis.ticks.x = element_blank(),
      panel.background = element_blank(),
      panel.grid.major.x = element_line(color = "gray80", size = 0.3),
      panel.grid.major.y = element_line(color = "gray80", size = 0.3),
      legend.position = 'none',
      plot.margin = margin(20, 10, 20, 10)
    )
```

```{r , fig.align='center', fig.width=10, fig.height = 8.5, warning=FALSE, fig.cap="Panels A and C: Point estimates depict the median. Interval bars depict the 50 and 95% credible intervals. Panels B and D: Cumulative posterior distributions correspond to the probabilities that the risk difference (RD) is less than or equal to the effect size on the X‐axis."}
(p1 + p2) / (p3 + p4) + plot_annotation(tag_levels = 'A')
```

<br><br>

## Figure 3: Posterior distributions; Sensitivity analysis of "invasive mechanical ventilation"

This sensitivity analysis are the ones with the greatest change across priors.
These changes can actually interfer clinical decision. Thus, I judged that these
analyses "deserve" their own figure. 

```{r, , fig.align='center', fig.width=7, fig.height = 4.5, fig.cap="Point estimates depict the median. Interval bars depict the 50 and 95% credible intervals."}

level_order = c("Pessimistic",
                "Optimistic",
                "Skeptical",
                "Evidence-based",
                "Non-informative")

all_posteriors_invasive_death %>%
  
  # make it tidy for ggplot
  pivot_longer(
    cols = c("Non-informative":"Pessimistic"),
    names_to = "dist", values_to = "samples"
  )  %>%
  
  ggplot(aes(x = 100 * samples,
             y = factor(dist, level = level_order),
             fill = dist)) +

  # https://mjskay.github.io/ggdist/articles/slabinterval.html
    stat_halfeye(aes(fill = stat(x < 0)),
                 position = "dodge",
               point_interval = median_qi,
               .width = c(0.5, 0.95)
  ) +
  scale_fill_manual(values = c("gray85", "forestgreen")) +
  labs(x = "\nRisk Difference (%)",
       y = "Underlying Prior\n"
  ) +
  scale_x_continuous(breaks = seq(from = -12, to = 12, 4)) +
  scale_y_discrete(expand = c(0, 0.3)) +
  theme(axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 13.5),
    axis.text.y = element_text(size = 12),
    axis.text.x = element_text(size = 12),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    legend.position = "none",
    plot.title.position = 'plot',
    plot.margin = margin(20, 25, 10, 20)
  ) +
  coord_cartesian(xlim = c(-12, 12))
```

<br><br>

## Table 2: Posterior distributions; Sensitivity analysis of "invasive mechanical ventilation"

This table complements Figure 3.

```{r}
t = tibble(
  
  "Underlying Prior" = c(
    "Non-informative",
    "Evidence-based",
    "Skeptical",
    "Optimistic",
    "Pessimistic"
  ),
  
  "Pr(< -5%)" = c(
    round(pnorm(-0.05,
                all_posteriors_invasive_death %>%
                  pull("Non-informative") %>% mean(),
                all_posteriors_invasive_death %>%
                  pull("Non-informative") %>% sd()), 2) * 100,
    round(pnorm(-0.05,
                all_posteriors_invasive_death %>%
                  pull("Evidence-based") %>% mean(),
                all_posteriors_invasive_death %>%
                  pull("Evidence-based") %>% sd()), 2) * 100,
    round(pnorm(-0.05,
                all_posteriors_invasive_death %>%
                  pull("Skeptical") %>% mean(),
                all_posteriors_invasive_death %>%
                  pull("Skeptical") %>% sd()), 2) * 100,
    round(pnorm(-0.05,
                all_posteriors_invasive_death %>%
                  pull("Optimistic") %>% mean(),
                all_posteriors_invasive_death %>%
                  pull("Optimistic") %>% sd()), 2) * 100,
    round(pnorm(-0.05,
                all_posteriors_invasive_death %>%
                  pull("Pessimistic") %>% mean(),
                all_posteriors_invasive_death %>%
                  pull("Pessimistic") %>% sd()), 2) * 100
    
    
  ),
  
  "Pr(< -2%)" = c(
    round(pnorm(-0.02,
                all_posteriors_invasive_death %>%
                  pull("Non-informative") %>% mean(),
                all_posteriors_invasive_death %>%
                  pull("Non-informative") %>% sd()), 2) * 100,
    round(pnorm(-0.02,
                all_posteriors_invasive_death %>%
                  pull("Evidence-based") %>% mean(),
                all_posteriors_invasive_death %>%
                  pull("Evidence-based") %>% sd()), 2) * 100,
    round(pnorm(-0.02,
                all_posteriors_invasive_death %>%
                  pull("Skeptical") %>% mean(),
                all_posteriors_invasive_death %>%
                  pull("Skeptical") %>% sd()), 2) * 100,
    round(pnorm(-0.02,
                all_posteriors_invasive_death %>%
                  pull("Optimistic") %>% mean(),
                all_posteriors_invasive_death %>%
                  pull("Optimistic") %>% sd()), 2) * 100,
    round(pnorm(-0.02,
                all_posteriors_invasive_death %>%
                  pull("Pessimistic") %>% mean(),
                all_posteriors_invasive_death %>%
                  pull("Pessimistic") %>% sd()), 2) * 100
    
  ),
  
  "Pr(< -1%)" = c(
    round(pnorm(-0.01,
                all_posteriors_invasive_death %>%
                  pull("Non-informative") %>% mean(),
                all_posteriors_invasive_death %>%
                  pull("Non-informative") %>% sd()), 2) * 100,
    round(pnorm(-0.01,
                all_posteriors_invasive_death %>%
                  pull("Evidence-based") %>% mean(),
                all_posteriors_invasive_death %>%
                  pull("Evidence-based") %>% sd()), 2) * 100,
    round(pnorm(-0.01,
                all_posteriors_invasive_death %>%
                  pull("Skeptical") %>% mean(),
                all_posteriors_invasive_death %>%
                  pull("Skeptical") %>% sd()), 2) * 100,
    round(pnorm(-0.01,
                all_posteriors_invasive_death %>%
                  pull("Optimistic") %>% mean(),
                all_posteriors_invasive_death %>%
                  pull("Optimistic") %>% sd()), 2) * 100,
    round(pnorm(-0.01,
                all_posteriors_invasive_death %>%
                  pull("Pessimistic") %>% mean(),
                all_posteriors_invasive_death %>%
                  pull("Pessimistic") %>% sd()), 2) * 100
  ),
  
  
  "Pr(< 0%)" = c(
    round(pnorm(0,
                all_posteriors_invasive_death %>%
                  pull("Non-informative") %>% mean(),
                all_posteriors_invasive_death %>%
                  pull("Non-informative") %>% sd()), 2) * 100,
    round(pnorm(0,
                all_posteriors_invasive_death %>%
                  pull("Evidence-based") %>% mean(),
                all_posteriors_invasive_death %>%
                  pull("Evidence-based") %>% sd()), 2) * 100,
    round(pnorm(0,
                all_posteriors_invasive_death %>%
                  pull("Skeptical") %>% mean(),
                all_posteriors_invasive_death %>%
                  pull("Skeptical") %>% sd()), 2) * 100,
    round(pnorm(0,
                all_posteriors_invasive_death %>%
                  pull("Optimistic") %>% mean(),
                all_posteriors_invasive_death %>%
                  pull("Optimistic") %>% sd()), 2) * 100,
    round(pnorm(0,
                all_posteriors_invasive_death %>%
                  pull("Pessimistic") %>% mean(),
                all_posteriors_invasive_death %>%
                  pull("Pessimistic") %>% sd()), 2) * 100
    
    
  ),
  
  "Pr(> 1%)" = c(
    round((1 - pnorm(0.01,
                     all_posteriors_invasive_death %>%
                       pull("Non-informative") %>% mean(),
                     all_posteriors_invasive_death %>%
                       pull("Non-informative") %>% sd())), 2) * 100,
    round((1 - pnorm(0.01,
                     all_posteriors_invasive_death %>%
                       pull("Evidence-based") %>% mean(),
                     all_posteriors_invasive_death %>%
                       pull("Evidence-based") %>% sd())), 2) * 100,
    round((1 - pnorm(0.01,
                     all_posteriors_invasive_death %>%
                       pull("Skeptical") %>% mean(),
                     all_posteriors_invasive_death %>%
                       pull("Skeptical") %>% sd())), 2) * 100,
    round((1 - pnorm(0.01,
                     all_posteriors_invasive_death %>%
                       pull("Optimistic") %>% mean(),
                     all_posteriors_invasive_death %>%
                       pull("Optimistic") %>% sd())), 2) * 100,
    round((1 - pnorm(0.01,
                     all_posteriors_invasive_death %>%
                       pull("Pessimistic") %>% mean(),
                     all_posteriors_invasive_death %>%
                       pull("Pessimistic") %>% sd())), 2) * 100
  ),
  
  "Pr(> 2%)" = c(
    round((1 - pnorm(0.02,
                     all_posteriors_invasive_death %>%
                       pull("Non-informative") %>% mean(),
                     all_posteriors_invasive_death %>%
                       pull("Non-informative") %>% sd())), 2) * 100,
    round((1 - pnorm(0.02,
                     all_posteriors_invasive_death %>%
                       pull("Evidence-based") %>% mean(),
                     all_posteriors_invasive_death %>%
                       pull("Evidence-based") %>% sd())), 2) * 100,
    round((1 - pnorm(0.02,
                     all_posteriors_invasive_death %>%
                       pull("Skeptical") %>% mean(),
                     all_posteriors_invasive_death %>%
                       pull("Skeptical") %>% sd())), 2) * 100,
    round((1 - pnorm(0.02,
                     all_posteriors_invasive_death %>%
                       pull("Optimistic") %>% mean(),
                     all_posteriors_invasive_death %>%
                       pull("Optimistic") %>% sd())), 2) * 100,
    round((1 - pnorm(0.02,
                     all_posteriors_invasive_death %>%
                       pull("Pessimistic") %>% mean(),
                     all_posteriors_invasive_death %>%
                       pull("Pessimistic") %>% sd())), 2) * 100
  ),
  
  "Pr(> 5%)" = c(
    round((1 - pnorm(0.05,
                     all_posteriors_invasive_death %>%
                       pull("Non-informative") %>% mean(),
                     all_posteriors_invasive_death %>%
                       pull("Non-informative") %>% sd())), 2) * 100,
    round((1 - pnorm(0.05,
                     all_posteriors_invasive_death %>%
                       pull("Evidence-based") %>% mean(),
                     all_posteriors_invasive_death %>%
                       pull("Evidence-based") %>% sd())), 2) * 100,
    round((1 - pnorm(0.05,
                     all_posteriors_invasive_death %>%
                       pull("Skeptical") %>% mean(),
                     all_posteriors_invasive_death %>%
                       pull("Skeptical") %>% sd())), 2) * 100,
    round((1 - pnorm(0.05,
                     all_posteriors_invasive_death %>%
                       pull("Optimistic") %>% mean(),
                     all_posteriors_invasive_death %>%
                       pull("Optimistic") %>% sd())), 2) * 100,
    round((1 - pnorm(0.05,
                     all_posteriors_invasive_death %>%
                       pull("Pessimistic") %>% mean(),
                     all_posteriors_invasive_death %>%
                       pull("Pessimistic") %>% sd())), 2) * 100
  )
) 

t %>% 
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1,
                     "Probability of Benefit" = 4,
                     "Probability of Harm" = 3))
```

