---
title: "Main Figures"
author: "Arthur M. Albuquerque"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r message=FALSE, warning=FALSE}
# Load packages

# Ensures the package "pacman" is installed
if (!require("pacman")) install.packages("pacman")

# p_load() installs (if necessary) and loads the following packages

pacman::p_load(here) # file paths
```

All figures and tables in this document regards the mortality outcome.

# Table 1

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.8\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "manuscript", # File path
                                 "table1.png"))

knitr::include_graphics(path) # File name
```

# Figure 1

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1.1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "manuscript", # File path
                                 "figure1.pdf"))

knitr::include_graphics(path) # File name
```

Point estimates depict the median and interval bars depict 95% highest density
intervals.

# Figure 2

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "manuscript", # File path
                                 "figure2.pdf"))

knitr::include_graphics(path) # File name
```

Panels A and C: Point estimates depict the median. Interval bars depict the 95%
highest density intervals. Panels B and D: Cumulative posterior
distributions correspond to the probabilities that the risk difference (RD)
is greater than or equal to the effect size on the X‐axis. The colors in Panels
B and D match the ones used in Panels A and C.

# Figure 3

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1.1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "manuscript", # File path
                                 "figure3.pdf"))

knitr::include_graphics(path) # File name
```

Posterior distributions from sensitivity analyses using different priors.

Point estimates depict the median. Interval bars depict the 95% highest density
intervals.

# Figure 4

```{r echo=FALSE, fig.align='center', message=FALSE, out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "manuscript", # File path
                                 "figure4.pdf"))

knitr::include_graphics(path) # File name
```

Posterior probabilities from sensitivity analyses using multiple different
baseline risks.

Each line represents the posterior probability of benefit for a specific cutoff,
such as risk difference greater to 0%, 1%, 2% and 5%. Vertical black
dashed lines represent the respective baseline risk underlying other analyses
(Figure 2), i.e., risk in the control group in the RECOVERY trial for each
subgroup (Table 1).

Panel A shows results for patients not using corticosteroids; Panel B shows
results for patients using corticosteroids. Panel C shows results for simple
oxygen only; Panel D shows results for non-invasive ventilation; Panel E shows
results for invasive mechanical ventilation.
