---
title: "Main Figures"
author: "Arthur M. Albuquerque"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r message=FALSE, warning=FALSE}
library(here)
```

All figures and tables in this document regards the mortality outcome.

# Table 1

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='0.8\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "manuscript", # File path
                                 "table1.png"))

knitr::include_graphics(path) # File name
```

# Figure 1

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "manuscript", # File path
                                 "figure1.pdf"))

knitr::include_graphics(path) # File name
```

Point estimates depict the median and interval bars depict 95% highest density
intervals.

# Figure 2

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "manuscript", # File path
                                 "figure2.pdf"))

knitr::include_graphics(path) # File name
```

Panels A and C: Point estimates depict the median. Interval bars depict the 80
and 95% highest density intervals. Panels B and D: Cumulative posterior
distributions correspond to the probabilities that the risk difference (RD)
is greater than or equal to the effect size on the X‐axis. The colors in Panels
B and D match the ones used in Panels A and C.

# Figure 3

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "manuscript", # File path
                                 "figure3.pdf"))

knitr::include_graphics(path) # File name
```

Point estimates depict the median.
Interval bars depict the 80 and 95% highest density intervals.

# Table 2

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "manuscript", # File path
                                 "table2.png"))

knitr::include_graphics(path) # File name
```

# Figure 4

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "manuscript", # File path
                                 "figure4.pdf"))

knitr::include_graphics(path) # File name
```

Sensitivity analyses using multiple different baseline risks for subgroups on
respiratory support. Each line represents the posterior probability of benefit 
for a specific cutoff, such as risk difference greater or equal to 0%, 1%, 2% and
5%. Vertical dashed lines represent the respective baseline risk (Table 1) used
in other analyses.

Panel A shows results for simple oxygen only; Panel B shows results for
non-invasive ventilation; Panel C shows results for invasive mechanical
ventilation.
