---
title: "Main Figures"
author: "Arthur M. Albuquerque"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r message=FALSE, warning=FALSE}
library(here)
```

# Table 1

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "manuscript", # File path
                                 "table1.pdf"))

knitr::include_graphics(path) # File name
```

# Figure 1

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "manuscript", # File path
                                 "figure1.pdf"))

knitr::include_graphics(path) # File name
```

Point estimates depict the median and interval bars depict 95th quantiles.

# Figure 2

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "manuscript", # File path
                                 "figure2.pdf"))

knitr::include_graphics(path) # File name
```

Panels A and C: Point estimates depict the median. Interval bars depict the 50 and 95% highest density intervals. Panels B and D: Cumulative posterior distributions correspond to the probabilities that the risk difference (RD) is greater than or equal to the effect size on the X‐axis.

# Figure 3

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "manuscript", # File path
                                 "figure3.pdf"))

knitr::include_graphics(path) # File name
```

Point estimates depict the median.
Interval bars depict the 50 and 95% highest density intervals.

# Table 2

```{r, echo = FALSE, message=FALSE, fig.align='center', out.width='1\\linewidth'}
path = (here("final_analyses", "output",
                                 "plots", "manuscript", # File path
                                 "table2.pdf"))

knitr::include_graphics(path) # File name
```
