---
title: "06_Analyses_on_Hospital_Discharge"
author: "Arthur M. Albuquerque"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
          code_folding: hide
          toc: yes
          toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
# Load packages

# Ensures the package "pacman" is installed
if (!require("pacman")) install.packages("pacman")

# p_load() installs (if necessary) and loads the following packages

pacman::p_load(plyr, # for the Varying baseline risk calculations
               magrittr, # same as above
               rio, # to import/export files
               tidyverse, # Data wrangling and plotting
               kableExtra, # To create tables
               flextable, # To create tables
               here, # To find file paths within R project
               metafor, # To create priors from meta-analysis
               janitor, # To change column names
               ggdist, # To plot distributions
               patchwork, # To arrange plots
               rcartocolor, # Color palettes
               Cairo # To export PDF files
               )

# Load data on respiratory support subgroups

d1 = import((here("final_analyses", "output", "data", # file path
                   "respiratory-data.csv")),           # file name
             header = T)

# Load data on corticosteroids subgroups

d2 = import(here("final_analyses", "data", # file path
                            "corticosteroids_subgroup_extracted-data.xlsx")) 

d2 = clean_names(d2)
```

In this document, we will compile most of the analyses regarding hospital
discharge. First, we will derive the risk difference from odds ratio. Next,
we will perform the main analyses and sensitivity analyses. We will be brief, so
for complete explanation on the rationale of the analyses, please check the files
on the mortality outcome.

In summary, this document shows what all other documents has shown, but now
the spotlight is on the hospital discharge outcome.

**Of note, for this outcome, positive log-odds ratio, odds ratio greater than 1, and negative risk differences mean benefit.**

# Calculating posterior distributions

## Priors and RECOVERY

### Use of corticosteroids

#### Not using 

First, let's calculate and visualize the **log-odds ratio** from the
RECOVERY trial.

```{r}

logOR_recovery_not_using =
  rma(
    # Outcome
    measure = "OR", # Log-odds ratio
    
    # Tocilizumab group
    ai = events_toci,
    n1i = total_toci,

    # Control group
    ci = events_control,
    n2i = total_control,
    
    data = d2 %>% filter(outcome == "discharge",
                         corticosteroids == 0,
                         trial == "RECOVERY"),
    
     method = "REML",

    slab = paste(trial)
  )

forest(logOR_recovery_not_using)
```

Now, let's calculate and visualize the **log-odds ratio** from the
other trials. The pooled result from this random-effect meta-analysis will be
used as the estimate for the distribution of prior regarding this subgroup.

```{r}

# Simple oxygen

logOR_prior_not_using =
  rma(
    # Outcome
    measure = "OR", # Log-odds ratio
    
    # Tocilizumab group
    ai = events_toci,
    n1i = total_toci,

    # Control group
    ci = events_control,
    n2i = total_control,
    
    data = d2 %>% filter(outcome == "discharge",
                         corticosteroids == 0,
                         trial != "RECOVERY"),
    
     method = "REML",

    slab = paste(trial)
  )

forest(logOR_prior_not_using)
```

#### Using 

Let's calculate and visualize the **log-odds ratio** from the
RECOVERY trial.

```{r}

logOR_recovery_using =
  rma(
    # Outcome
    measure = "OR", # Log-odds ratio
    
    # Tocilizumab group
    ai = events_toci,
    n1i = total_toci,

    # Control group
    ci = events_control,
    n2i = total_control,
    
    data = d2 %>% filter(outcome == "discharge",
                         corticosteroids == 1,
                         trial == "RECOVERY"),
    
     method = "REML",

    slab = paste(trial)
  )

forest(logOR_recovery_using)
```

Now, let's calculate and visualize the **log-odds ratio** from the
other trials. The pooled result from this random-effect meta-analysis will be
used as the estimate for the distribution of prior regarding this subgroup.

```{r}

# Simple oxygen

logOR_prior_using =
  rma(
    # Outcome
    measure = "OR", # Log-odds ratio
    
    # Tocilizumab group
    ai = events_toci,
    n1i = total_toci,

    # Control group
    ci = events_control,
    n2i = total_control,
    
    data = d2 %>% filter(outcome == "discharge",
                         corticosteroids == 1,
                         trial != "RECOVERY"),
    
     method = "REML",

    slab = paste(trial)
  )

forest(logOR_prior_using)
```

### Respiratory support subgroups

#### Simple oxygen only

Let's calculate and visualize the **log-odds ratio** from the
RECOVERY trial.

```{r}

logOR_recovery_simple =
  rma(
    # Outcome
    measure = "OR", # Log-odds ratio
    
    # Tocilizumab group
    ai = events_toci,
    n1i = total_toci,

    # Control group
    ci = events_control,
    n2i = total_control,
    
    data = d1 %>% filter(outcome == "discharge",
                         oxygen == "simple oxygen",
                         trial == "RECOVERY"),
    
     method = "REML",

    slab = paste(trial)
  )

forest(logOR_recovery_simple)
```

Now, let's calculate and visualize the **log-odds ratio** from the
other trials. The pooled result from this random-effect meta-analysis will be
used as the estimate for the distribution of prior regarding this subgroup.

```{r}

logOR_prior_simple =
  rma(
    # Outcome
    measure = "OR", # Log-odds ratio
    
    # Tocilizumab group
    ai = events_toci,
    n1i = total_toci,

    # Control group
    ci = events_control,
    n2i = total_control,
    
    data = d1 %>% filter(outcome == "discharge",
                         oxygen == "simple oxygen",
                         trial != "RECOVERY"),
    
     method = "REML",

    slab = paste(trial)
  )

forest(logOR_prior_simple)
```

#### Non-invasive ventilation

Let's calculate and visualize the **log-odds ratio** from the
RECOVERY trial.

```{r}

logOR_recovery_noninvasive =
  rma(
    # Outcome
    measure = "OR", # Log-odds ratio
    
    # Tocilizumab group
    ai = events_toci,
    n1i = total_toci,

    # Control group
    ci = events_control,
    n2i = total_control,
    
    data = d1 %>% filter(outcome == "discharge",
                         oxygen == "non-invasive ventilation",
                         trial == "RECOVERY"),
    
     method = "REML",

    slab = paste(trial)
  )

forest(logOR_recovery_noninvasive)
```

Now, let's calculate and visualize the **log-odds ratio** from the
other trials. The pooled result from this random-effect meta-analysis will be
used as the estimate for the distribution of prior regarding this subgroup.

```{r}

logOR_prior_noninvasive =
  rma(
    # Outcome
    measure = "OR", # Log-odds ratio
    
    # Tocilizumab group
    ai = events_toci,
    n1i = total_toci,

    # Control group
    ci = events_control,
    n2i = total_control,
    
    data = d1 %>% filter(outcome == "discharge",
                         oxygen == "non-invasive ventilation",
                         trial != "RECOVERY"),
    
     method = "REML",

    slab = paste(trial)
  )

forest(logOR_prior_noninvasive)
```

#### Invasive mechanical ventilation

Let's calculate and visualize the **log-odds ratio** from the
RECOVERY trial.

```{r}

logOR_recovery_invasive =
  rma(
    # Outcome
    measure = "OR", # Log-odds ratio
    
    # Tocilizumab group
    ai = events_toci,
    n1i = total_toci,

    # Control group
    ci = events_control,
    n2i = total_control,
    
    data = d1 %>% filter(outcome == "discharge",
                         oxygen == "invasive ventilation",
                         trial == "RECOVERY"),
    
     method = "REML",

    slab = paste(trial)
  )

forest(logOR_recovery_invasive)
```

Now, let's calculate and visualize the **log-odds ratio** from the
other trials. The pooled result from this random-effect meta-analysis will be
used as the estimate for the distribution of prior regarding this subgroup.

```{r}

logOR_prior_invasive =
  rma(
    # Outcome
    measure = "OR", # Log-odds ratio
    
    # Tocilizumab group
    ai = events_toci,
    n1i = total_toci,

    # Control group
    ci = events_control,
    n2i = total_control,
    
    data = d1 %>% filter(outcome == "discharge",
                         oxygen == "invasive ventilation",
                         trial != "RECOVERY"),
    
     method = "REML",

    slab = paste(trial)
  )

forest(logOR_prior_invasive)
```

## Posterior Distribution

```{r}
## Load custom functions

# To generate normal conjugate posterior probabilities

source(here("final_analyses", "script", "functions", "analyses", # file path
            "conjugate_normal_posterior.R"))                     # file name

# To generate posterior probabilities with an evidence-based prior
# (it requires "conjugate_normal_posterior.R" )

source(here("final_analyses", "script", "functions", "analyses", # file path
            "normal_approximation_logOR.R"))                     # file name

# To generate posterior probabilities with multiple priors
# (it requires "conjugate_normal_posterior.R" )

source(here("final_analyses", "script", "functions", "analyses", # file path
            "logOR_normal_approximation_multiple_priors.R"))     # file name

# To compile all posteriors into a tibble

source(here("final_analyses", "script", "functions", "analyses", # file path
            "tibble_all_posteriors_logOR.R"))                      # file name
```


```{r include=FALSE}
### Apply custom functions

## Use of corticosteroids

# Not using
posterior_not_using_discharge = normal_approximation_logOR(
  logOR_recovery_not_using, # Data object with RECOVERY data
  logOR_prior_not_using, # Output from the rma() in the previous code chunk

  posterior_not_using_discharge # Repeat the name of the object you are creating
)

# Using
posterior_using_discharge = normal_approximation_logOR(
  logOR_recovery_using, # Data object with RECOVERY data
  logOR_prior_using, # Output from the rma() in the previous code chunk

  posterior_using_discharge # Repeat the name of the object you are creating
)

## Respiratory support

# Simple oxygen only
posterior_simple_discharge = normal_approximation_logOR(
  logOR_recovery_simple, # Data object with RECOVERY data
  logOR_prior_simple, # Output from the rma() in the previous code chunk

  posterior_simple_discharge # Repeat the name of the object you are creating
)

# Non-invasive ventilation
posterior_noninvasive_discharge = normal_approximation_logOR(
  logOR_recovery_noninvasive, # Data object with RECOVERY data
  logOR_prior_noninvasive, # Output from the rma() in the previous code chunk

  posterior_noninvasive_discharge # Repeat the name of the object you are creating
)

# Invasive mechanical ventilation
posterior_invasive_discharge = normal_approximation_logOR(
  logOR_recovery_invasive, # Data object with RECOVERY data
  logOR_prior_invasive, # Output from the rma() in the previous code chunk

  posterior_invasive_discharge # Repeat the name of the object you are creating
)

```

Note that positive log(OR) means benefit for the hospital discharge outcome.
Thus, in this document, the optimistic prior has a positive mean and the
pessimistic the opposite.

```{r message=FALSE, warning=FALSE}
## Use of corticosteroids

# Not using
posteriors_not_using_discharge =
  logOR_normal_approximation_multiple_priors(
  # Data object with evidence-based posterior from normal_approximation()
  posterior_not_using_discharge, 
  "discharge", # Outcome (within quotes)
  posteriors_not_using_discharge # Name for the final output with data+prior+posterior
  )

# Using
posteriors_using_discharge =
  logOR_normal_approximation_multiple_priors(
  # Data object with evidence-based posterior from normal_approximation()
  posterior_using_discharge, 
  "discharge", # Outcome (within quotes)
  posteriors_using_discharge # Name for the final output with data+prior+posterior
  )

## Respiratory support

# Simple oxygen only
posteriors_simple_discharge =
  logOR_normal_approximation_multiple_priors(
  # Data object with evidence-based posterior from normal_approximation()
  posterior_simple_discharge, 
  "discharge", # Outcome (within quotes)
  posteriors_simple_discharge # Name for the final output with data+prior+posterior
  )

# Non-invasive ventilation
posteriors_noninvasive_discharge =
  logOR_normal_approximation_multiple_priors(
  # Data object with evidence-based posterior from normal_approximation()
  posterior_noninvasive_discharge, 
  "discharge", # Outcome (within quotes)
  posteriors_noninvasive_discharge # Name for the final output with data+prior+posterior
  )

# Invasive mechanical ventilation
posteriors_invasive_discharge =
  logOR_normal_approximation_multiple_priors(
  # Data object with evidence-based posterior from normal_approximation()
  posterior_invasive_discharge, 
  "discharge", # Outcome (within quotes)
  posteriors_invasive_discharge # Name for the final output with data+prior+posterior
  )

```

```{r}
## Use of corticosteroids

# Not using
samples_logOR_posteriors_not_using_discharge = 
  tibble_all_posteriors_logOR(posteriors_not_using_discharge)

# Using
samples_logOR_posteriors_using_discharge = 
  tibble_all_posteriors_logOR(posteriors_using_discharge)

## Respiratory support

# Simple oxygen only
samples_logOR_posteriors_simple_discharge = 
  tibble_all_posteriors_logOR(posteriors_simple_discharge)

# Non-invasive ventilation
samples_logOR_posteriors_noninvasive_discharge = 
  tibble_all_posteriors_logOR(posteriors_noninvasive_discharge)

# Invasive mechanical ventilation
samples_logOR_posteriors_invasive_discharge = 
  tibble_all_posteriors_logOR(posteriors_invasive_discharge)
```

```{r}
## Use of corticosteroids

# Not using
samples_posteriors_not_using_discharge = 
  samples_logOR_posteriors_not_using_discharge %>% 
  pivot_longer(
    cols = c('Non-informative':'Pessimistic'),
    names_to = "Underlying_Prior", values_to = "log(OR)"
  )

# Using
samples_posteriors_using_discharge = 
  samples_logOR_posteriors_using_discharge %>% 
  pivot_longer(
    cols = c('Non-informative':'Pessimistic'),
    names_to = "Underlying_Prior", values_to = "log(OR)"
  )

## Respiratory support

# Simple oxygen only
samples_posteriors_simple_discharge = 
  samples_logOR_posteriors_simple_discharge %>% 
  pivot_longer(
    cols = c('Non-informative':'Pessimistic'),
    names_to = "Underlying_Prior", values_to = "log(OR)"
  )

# Non-invasive ventilation
samples_posteriors_noninvasive_discharge = 
  samples_logOR_posteriors_noninvasive_discharge %>% 
  pivot_longer(
    cols = c('Non-informative':'Pessimistic'),
    names_to = "Underlying_Prior", values_to = "log(OR)"
  )

# Invasive mechanical ventilation
samples_posteriors_invasive_discharge = 
  samples_logOR_posteriors_invasive_discharge %>% 
  pivot_longer(
    cols = c('Non-informative':'Pessimistic'),
    names_to = "Underlying_Prior", values_to = "log(OR)"
  )
  
```

```{r}
## Use of corticosteroids

# Not using
samples_posteriors_not_using_discharge = 
  samples_posteriors_not_using_discharge %>% 
  mutate(OR = exp(`log(OR)`))

# Using
samples_posteriors_using_discharge = 
  samples_posteriors_using_discharge %>% 
  mutate(OR = exp(`log(OR)`))

## Respiratory support

# Simple oxygen only
samples_posteriors_simple_discharge = 
  samples_posteriors_simple_discharge %>% 
  mutate(OR = exp(`log(OR)`))

# Non-invasive ventilation
samples_posteriors_noninvasive_discharge = 
  samples_posteriors_noninvasive_discharge %>% 
  mutate(OR = exp(`log(OR)`))

# Invasive mechanical ventilation
samples_posteriors_invasive_discharge = 
  samples_posteriors_invasive_discharge %>% 
  mutate(OR = exp(`log(OR)`))
  
```

#### Baseline risks in RECOVERY

Remember that higher risks of hospital discharge is a benefitial outcome.

```{r echo=FALSE}
tibble(
  
  "Subgroup" = c("Not using",
                 "Using",
                 
                 "Simple oxygen only",
                 "Non-invasive ventilation",
                 "Invasive mechanical"
                 ),
  
  "Baseline Risk in Control Group (%)" = c(
    
    d2 %>% 
    filter(trial == "RECOVERY",
           corticosteroids == 0,
           outcome == "discharge") %>% 
      summarise(n = 100*(events_control/total_control)) %>% 
      round(., 1) %>% 
      pull(),
    d2 %>% 
    filter(trial == "RECOVERY",
           corticosteroids == 1,
           outcome == "discharge") %>% 
      summarise(n = 100*(events_control/total_control)) %>% 
      round(., 1) %>% 
      pull(),
    
    d1 %>% 
    filter(trial == "RECOVERY",
           oxygen == "simple oxygen",
           outcome == "discharge") %>% 
      summarise(n = 100*(events_control/total_control)) %>% 
      round(., 1) %>% 
      pull(),
    d1 %>% 
    filter(trial == "RECOVERY",
           oxygen == "non-invasive ventilation",
           outcome == "discharge") %>% 
      summarise(n = 100*(events_control/total_control)) %>% 
      round(., 1) %>% 
      pull(),
    d1 %>% 
    filter(trial == "RECOVERY",
           oxygen == "invasive ventilation",
           outcome == "discharge") %>% 
      summarise(n = 100*(events_control/total_control)) %>% 
      round(., 1) %>% 
      pull()
  )
  
) %>% 
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  pack_rows("Use of corticosteroids", 1, 2) %>% 
  pack_rows("Respiratory support", 3, 5)
```

```{r}
# BR = Baseline Risk
# OR = Odds Ratio

RD_fun = function(BR,OR)
  {
( BR*(BR-1)*(OR-1) ) / ( BR*OR - BR+1)
}
```


```{r}
# Calculating the risk differences

### Use of corticosteroids

## Not using

# Define baseline risk
BR_not_using = d2 %>% 
    filter(trial == "RECOVERY",
           corticosteroids == 0, # Not using
           outcome == "discharge") %>% 
      summarise(n = events_control/total_control) %>%
      pull()

samples_posteriors_not_using_discharge = 
  samples_posteriors_not_using_discharge %>% 
  # Apply formula from Doi et al., 2020
  mutate(RD = RD_fun(BR_not_using,
                     OR))

## Using

# Define baseline risk
BR_using = d2 %>% 
    filter(trial == "RECOVERY",
           corticosteroids == 1, # Using
           outcome == "discharge") %>% 
      summarise(n = events_control/total_control) %>%
      pull()

samples_posteriors_using_discharge = 
  samples_posteriors_using_discharge %>% 
  # Apply formula from Doi et al., 2020
  mutate(RD = RD_fun(BR_using,
                     OR))

### Respiratory support

## Simple oxygen

# Define baseline risk
BR_simple = d1 %>% 
    filter(trial == "RECOVERY",
           oxygen == "simple oxygen",
           outcome == "discharge") %>% 
      summarise(n = events_control/total_control) %>% 
      pull()

samples_posteriors_simple_discharge = 
  samples_posteriors_simple_discharge %>% 
  # Apply formula from Doi et al., 2020
  mutate(RD = RD_fun(BR_simple,
                     OR))

## Non-invasive

# Define baseline risk
BR_noninvasive = d1 %>% 
    filter(trial == "RECOVERY",
           oxygen == "non-invasive ventilation",
           outcome == "discharge") %>% 
      summarise(n = events_control/total_control) %>% 
      pull()

samples_posteriors_noninvasive_discharge = 
  samples_posteriors_noninvasive_discharge %>% 
  # Apply formula from Doi et al., 2020
  mutate(RD = RD_fun(BR_noninvasive,
                     OR))

## Invasive mechanical ventilation

# Define baseline risk
BR_invasive = d1 %>% 
    filter(trial == "RECOVERY",
           oxygen == "invasive ventilation",
           outcome == "discharge") %>% 
      summarise(n = events_control/total_control) %>% 
      pull()

samples_posteriors_invasive_discharge = 
  samples_posteriors_invasive_discharge %>% 
  # Apply formula from Doi et al., 2020
  mutate(RD = RD_fun(BR_invasive,
                     OR))
```

#### Summary

To display some of our calculations, we will now plot the posterior distributions
for log-odds ratio, odds ratio and risk difference for a single subgroup
(not using corticosteroids).

We note that **log-odds ratios** *greater* than $0$, **odds-ratios** *greater*
than $1$ and **risk differences** *lower* than $0$ mean benefit for the hospital
discharge outcome.


```{r echo=FALSE}
# Underlying a Non-informative prior

p1 = samples_posteriors_not_using_discharge %>% 
  filter(`Underlying_Prior` == "Non-informative") %>% 
  ggplot(aes(`log(OR)`)) +
  stat_halfeye(fill = "#C7CCF4") +
  labs(x = "log(OR)", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(-0.5, 0.5, 0.25)) +
  coord_cartesian(x = c(-0.5, 0.5)) 

p2 = samples_posteriors_not_using_discharge %>% 
  filter(`Underlying_Prior` == "Non-informative") %>% 
  ggplot(aes(`OR`)) +
  stat_halfeye(fill = "#C7CCF4") +
  labs(x = "OR", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(0.5, 1.5, 0.25)) +
  coord_cartesian(x = c(0.5, 1.5)) 

p3 = samples_posteriors_not_using_discharge %>% 
  filter(`Underlying_Prior` == "Non-informative") %>% 
  ggplot(aes(`RD`)) +
  stat_halfeye(fill = "#C7CCF4") +
  labs(x = "RD", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(-0.2, 0.1, 0.1)) +
  coord_cartesian(x = c(-0.2, 0.1)) 

```

```{r echo=FALSE}
# Underlying an Evidence-based prior

p4 = samples_posteriors_not_using_discharge %>% 
  filter(`Underlying_Prior` == "Evidence-based") %>% 
  ggplot(aes(`log(OR)`)) +
  stat_halfeye(fill = "#E7B03C") +
  labs(x = "log(OR)", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(-0.5, 0.5, 0.25)) +
  coord_cartesian(x = c(-0.5, 0.5)) 

p5 = samples_posteriors_not_using_discharge %>% 
  filter(`Underlying_Prior` == "Evidence-based") %>% 
  ggplot(aes(`OR`)) +
  stat_halfeye(fill = "#E7B03C") +
  labs(x = "OR", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(0.5, 1.5, 0.25)) +
  coord_cartesian(x = c(0.5, 1.5)) 

p6 = samples_posteriors_not_using_discharge %>% 
  filter(`Underlying_Prior` == "Evidence-based") %>% 
  ggplot(aes(`RD`)) +
  stat_halfeye(fill = "#E7B03C") +
  labs(x = "RD", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(-0.2, 0.1, 0.1)) +
  coord_cartesian(x = c(-0.2, 0.1)) 

```

```{r echo=FALSE}
# Underlying an Skeptical prior

p7 = samples_posteriors_not_using_discharge %>% 
  filter(`Underlying_Prior` == "Skeptical") %>% 
  ggplot(aes(`log(OR)`)) +
  stat_halfeye() +
  labs(x = "log(OR)", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(-0.5, 0.5, 0.25)) +
  coord_cartesian(x = c(-0.5, 0.5)) 

p8 = samples_posteriors_not_using_discharge %>% 
  filter(`Underlying_Prior` == "Skeptical") %>% 
  ggplot(aes(`OR`)) +
  stat_halfeye() +
  labs(x = "OR", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(0.5, 1.5, 0.25)) +
  coord_cartesian(x = c(0.5, 1.5)) 

p9 = samples_posteriors_not_using_discharge %>% 
  filter(`Underlying_Prior` == "Skeptical") %>% 
  ggplot(aes(`RD`)) +
  stat_halfeye() +
  labs(x = "RD", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(-0.2, 0.1, 0.1)) +
  coord_cartesian(x = c(-0.2, 0.1)) 

```

```{r echo=FALSE}
# Underlying an Optimistic prior

p10 = samples_posteriors_not_using_discharge %>% 
  filter(`Underlying_Prior` == "Optimistic") %>% 
  ggplot(aes(`log(OR)`)) +
  stat_halfeye(fill = "#479D8B") +
  labs(x = "log(OR)", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(-0.5, 0.5, 0.25)) +
  coord_cartesian(x = c(-0.5, 0.5)) 

p11 = samples_posteriors_not_using_discharge %>% 
  filter(`Underlying_Prior` == "Optimistic") %>% 
  ggplot(aes(`OR`)) +
  stat_halfeye(fill = "#479D8B") +
  labs(x = "OR", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(0.5, 1.5, 0.25)) +
  coord_cartesian(x = c(0.5, 1.5)) 

p12 = samples_posteriors_not_using_discharge %>% 
  filter(`Underlying_Prior` == "Optimistic") %>% 
  ggplot(aes(`RD`)) +
  stat_halfeye(fill = "#479D8B") +
  labs(x = "RD", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(-0.2, 0.1, 0.1)) +
  coord_cartesian(x = c(-0.2, 0.1)) 

```

```{r echo=FALSE}
# Underlying an Pessimistic prior

p13 = samples_posteriors_not_using_discharge %>% 
  filter(`Underlying_Prior` == "Pessimistic") %>% 
  ggplot(aes(`log(OR)`)) +
  stat_halfeye(fill = "#D36883") +
  labs(x = "log(OR)", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(-0.5, 0.5, 0.25)) +
  coord_cartesian(x = c(-0.5, 0.5)) 

p14 = samples_posteriors_not_using_discharge %>% 
  filter(`Underlying_Prior` == "Pessimistic") %>% 
  ggplot(aes(`OR`)) +
  stat_halfeye(fill = "#D36883") +
  labs(x = "OR", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(0.5, 1.5, 0.25)) +
  coord_cartesian(x = c(0.5, 1.5)) 

p15 = samples_posteriors_not_using_discharge %>% 
  filter(`Underlying_Prior` == "Pessimistic") %>% 
  ggplot(aes(`RD`)) +
  stat_halfeye(fill = "#D36883") +
  labs(x = "RD", y = " ") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks = seq(-0.2, 0.1, 0.1)) +
  coord_cartesian(x = c(-0.2, 0.1)) 

```

```{r echo=FALSE, fig.align='center', fig.height=2, fig.width=8}
(p1 + p2 + p3) +  plot_annotation(
  title = "Posterior distributions using a non-informative prior")

(p4 + p5 + p6) +  plot_annotation(
  title = "Posterior distributions using an evidence-based prior")

(p7 + p8 + p9) +  plot_annotation(
  title = "Posterior distributions using a skeptical prior")

(p10 + p11 + p12) +  plot_annotation(
  title = "Posterior distributions using an optimistic prior")

(p13 + p14 + p15) +  plot_annotation(
  title = "Posterior distributions using a pessimistic prior")
```

```{r include=FALSE}
## Save 

# save(posteriors_not_using_discharge,
#      posteriors_using_discharge,
#      posteriors_simple_discharge,
#      posteriors_noninvasive_discharge,
#      posteriors_invasive_discharge,
#      
#      file = here("final_analyses", "output", "data", "analyses", # file path
#                  "data_prior_posteriors_mean_sd_discharge.RData"))   # file name
```

```{r include=FALSE}
## Save 

# save(samples_posteriors_not_using_discharge,
#      samples_posteriors_using_discharge,
#      samples_posteriors_simple_discharge,
#      samples_posteriors_noninvasive_discharge,
#      samples_posteriors_invasive_discharge,
#      
#      file = here("final_analyses", "output", "data", "analyses", # file path
#                  "samples_posteriors_discharge.RData"))        # file name

# Although I saved this file to my PC, I uploaded it to OSF
# (https://osf.io/7t32f/), since it is 56MB
# In the next analysis documents, I will load this file directly from OSF,
# without the need of downloading it to your PC
```

# Analyses

We are going to replicate the same analyses done regarding the mortality
outcome. Of course, now with the hospital discharge data.

One could load all data objects generated above without the need of running
all code chunks again. THe purpose of the following code chunk is to facilitate
to this end, by loading the data objects stored elsewhere.

```{r}
## Load objects with mean + SD of multiple priors along with
## RECOVERY data and posterior distributions

#load(file = here("final_analyses", "output", "data", "analyses", # file path
#                 "data_prior_posteriors_mean_sd_discharge.RData"))   # file name

## Load posterior distributions' samples with logOR, OR and RD

# I uploaded these data objects to OSF since the .RData file is 56MB.
# Here I load all data files directly from OSF without having to download it
# to my/your PC

#samples = url("https://osf.io/7t32f/download?version=1")
#load(gzcon(samples))
```

## Main figures and tables

```{r}
# Load original data extraction table

d = import((here("final_analyses", "output", "data", # file path
                   "respiratory-data.csv")),           # file name
             header = T)
d = d %>% 
  as_tibble() %>% 
  select(!starts_with("X")) 

# Create different variables per subgroup

priors_simple_oxygen_raw =
  d %>%
  filter(
    trial != "RECOVERY",
    oxygen == "simple oxygen",
    outcome == "discharge"
  )

priors_noninvasive_raw =
  d %>%
  filter(
    trial != "RECOVERY",
    oxygen == "non-invasive ventilation",
    outcome == "discharge"
  )

priors_invasive_raw =
  d %>%
  filter(
    trial != "RECOVERY",
    oxygen == "invasive ventilation",
    outcome == "discharge"
  )

recovery_simple_oxygen = d %>%
  filter(trial == "RECOVERY",
         outcome == "discharge",
         oxygen == "simple oxygen")

recovery_noninvasive = d %>%
  filter(trial == "RECOVERY",
         outcome == "discharge",
         oxygen == "non-invasive ventilation")

recovery_invasive = d %>%
  filter(trial == "RECOVERY",
         outcome == "discharge",
         oxygen == "invasive ventilation")
  

# Load corticosteroids raw data

d_cortico = import(here("final_analyses", "data", # file path
                            "corticosteroids_subgroup_extracted-data.xlsx"))

d_cortico = clean_names(d_cortico)

priors_not_using =
  d_cortico %>%
  filter(
    trial != "RECOVERY",
    corticosteroids == 0,
    outcome == "discharge"
  )

priors_using =
  d_cortico %>%
  filter(
    trial != "RECOVERY",
    corticosteroids == 1,
    outcome == "discharge"
  )

recovery_not_using = d_cortico %>%
  filter(trial == "RECOVERY",
         outcome == "discharge",
         corticosteroids == 0)

recovery_using = d_cortico %>%
  filter(trial == "RECOVERY",
         outcome == "discharge",
         corticosteroids == 1)

```

```{r}
# Set seed for reproducibility

set.seed = 123 
```

### Overview in priors and RECOVERY

```{r}
t = tibble(
  
  "Subgroup" = c(
    "Not using",
    "Using",
    
    "Simple oxygen only",
    "Non-invasive ventilation",
    "Invasive mechanical ventilation"
    
  ),
  
  ## Priors
  
  "Number of studies" = c(
    
    priors_not_using %>%
      count() %>% pull(),
    priors_using %>%
      count() %>% pull(),
    
    priors_simple_oxygen_raw %>%
      count() %>% pull(),
    priors_noninvasive_raw %>%
      count() %>% pull(),
    priors_invasive_raw %>%
      count() %>% pull()
    
  ),
  
  # Control arm
  
  "Events  " = c(
    
    priors_not_using %>%
    summarise(n = sum(events_control)) %>% pull(),
    priors_using %>%
      summarise(n = sum(events_control)) %>% pull(),
    
    priors_simple_oxygen_raw %>%
      summarise(n = sum(events_control)) %>% pull(),
    priors_noninvasive_raw %>%
      summarise(n = sum(events_control)) %>% pull(),
    priors_invasive_raw %>%
      summarise(n = sum(events_control)) %>% pull()

  ),
  
  "Total  " = c(
    
    priors_not_using %>%
      summarise(n = sum(total_control)) %>% pull(),
    priors_using %>%
      summarise(n = sum(total_control)) %>% pull(),
    
    priors_simple_oxygen_raw %>%
      summarise(n = sum(total_control)) %>% pull(),
    priors_noninvasive_raw %>%
      summarise(n = sum(total_control)) %>% pull(),
    priors_invasive_raw %>%
      summarise(n = sum(total_control)) %>% pull()

  ),
  
   "Risk (%)" = c(
    
    priors_not_using %>%
      summarise(n = round(100*sum(events_control)/sum(total_control),1)) %>%
      pull(),
    priors_using %>%
      summarise(n = round(100*sum(events_control)/sum(total_control),1)) %>%
      pull(),
    
    priors_simple_oxygen_raw %>%
      summarise(n = round(100*sum(events_control)/sum(total_control),1)) %>%
      pull(),
    priors_noninvasive_raw %>%
      summarise(n = round(100*sum(events_control)/sum(total_control),1)) %>%
      pull(),
    priors_invasive_raw %>%
      summarise(n = round(100*sum(events_control)/sum(total_control),1)) %>%
      pull()

  ),
  
  # Tocilizumab arm
  
  "Events   " = c(
    priors_not_using %>%
      summarise(n = sum(events_toci)) %>% pull(),
    priors_using %>%
      summarise(n = sum(events_toci)) %>% pull(),
    
    priors_simple_oxygen_raw %>%
      summarise(n = sum(events_toci)) %>% pull(),
    priors_noninvasive_raw %>%
      summarise(n = sum(events_toci)) %>% pull(),
    priors_invasive_raw %>%
      summarise(n = sum(events_toci)) %>% pull()
    
  ),
  
  "Total   " = c(
    priors_not_using %>%
      summarise(n = sum(total_toci)) %>% pull(),
    priors_using %>%
      summarise(n = sum(total_toci)) %>% pull(),
    
    priors_simple_oxygen_raw %>%
      summarise(n = sum(total_toci)) %>% pull(),
    priors_noninvasive_raw %>%
      summarise(n = sum(total_toci)) %>% pull(),
    priors_invasive_raw %>%
      summarise(n = sum(total_toci)) %>% pull()

  ),
  
  "Risk (%) " = c(
  
  priors_not_using %>%
    summarise(n = round(100*sum(events_toci)/sum(total_toci),1)) %>%
    pull(),
  priors_using %>%
    summarise(n = round(100*sum(events_toci)/sum(total_toci),1)) %>%
    pull(),
  
  priors_simple_oxygen_raw %>%
    summarise(n = round(100*sum(events_toci)/sum(total_toci),1)) %>%
    pull(),
  priors_noninvasive_raw %>%
    summarise(n = round(100*sum(events_toci)/sum(total_toci),1)) %>%
    pull(),
  priors_invasive_raw %>%
    summarise(n = round(100*sum(events_toci)/sum(total_toci),1)) %>%
    pull()
  
),
  
  ## RECOVERY
  
  # Control arm
  
  "Events" = c(
    recovery_not_using %>% 
      select(events_control) %>% pull(),
    recovery_using %>% 
      select(events_control) %>% pull(),
    
    recovery_simple_oxygen %>% 
      select(events_control) %>% pull(),
    recovery_noninvasive %>% 
      select(events_control) %>% pull(),
    recovery_invasive %>% 
      select(events_control) %>% pull()

  ),
  
  "Total" = c(
    
    recovery_not_using %>% 
      select(total_control) %>% pull(),
    recovery_using %>% 
      select(total_control) %>% pull(),
    
    recovery_simple_oxygen %>% 
      select(total_control) %>% pull(),
    recovery_noninvasive %>% 
      select(total_control) %>% pull(),
    recovery_invasive %>% 
      select(total_control) %>% pull()

  ),

  "Risk (%)  " = c(
    
    recovery_not_using %>% 
      summarise(n = round(100*sum(events_control)/sum(total_control),1)) %>%
      pull(),
    recovery_using %>% 
      summarise(n = round(100*sum(events_control)/sum(total_control),1)) %>%
      pull(),
    
    recovery_simple_oxygen %>% 
      summarise(n = round(100*sum(events_control)/sum(total_control),1)) %>%
      pull(),
    recovery_noninvasive %>% 
      summarise(n = round(100*sum(events_control)/sum(total_control),1)) %>%
      pull(),
    recovery_invasive %>% 
      summarise(n = round(100*sum(events_control)/sum(total_control),1)) %>%
      pull()

  ),
  
  # Tocilizumab arm
  
  "Events " = c(
    recovery_not_using %>% 
      select(events_toci) %>% pull(),
    recovery_using %>% 
      select(events_toci) %>% pull(),
    
   recovery_simple_oxygen %>% 
      select(events_toci) %>% pull(),
    recovery_noninvasive %>% 
      select(events_toci) %>% pull(),
   recovery_invasive %>% 
      select(events_toci) %>% pull()

  ),
  
  "Total " = c(
    
    recovery_not_using %>% 
      select(total_toci) %>% pull(),
    recovery_using %>% 
      select(total_toci) %>% pull(),
    
    recovery_simple_oxygen %>% 
      select(total_toci) %>% pull(),
    recovery_noninvasive %>% 
      select(total_toci) %>% pull(),
    recovery_invasive %>% 
      select(total_toci) %>% pull()

  ),

  "Risk (%)   " = c(
    
    recovery_not_using %>% 
      summarise(n = round(100*sum(events_toci)/sum(total_toci),1)) %>%
    pull(),
    recovery_using %>% 
      summarise(n = round(100*sum(events_toci)/sum(total_toci),1)) %>%
    pull(),
    
    recovery_simple_oxygen %>% 
      summarise(n = round(100*sum(events_toci)/sum(total_toci),1)) %>%
    pull(),
    recovery_noninvasive %>% 
      summarise(n = round(100*sum(events_toci)/sum(total_toci),1)) %>%
    pull(),
    recovery_invasive %>% 
      summarise(n = round(100*sum(events_toci)/sum(total_toci),1)) %>%
    pull()

  )
  
)

# Use kableExtra to have a nice table

t1 = t %>% 
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = T) %>%
  column_spec(c(5,8,11,14), bold = T) %>% 
  add_header_above(c(" " = 2,
                     "Control" = 3,
                     "Tocilizumab" = 3,
                     "Control" = 3,
                     "Tocilizumab" = 3)) %>% 
  add_header_above(c(" " = 1,
                     "Priors" = 7,
                     "RECOVERY" = 6)) %>% 
  pack_rows("Use of corticosteroids", 1, 2) %>% 
  pack_rows("Respiratory support", 3, 5)

t1

# t1 %>% 
#   save_kable(here("final_analyses", "output", "plots", "appendix", # File path
#                   "STable13_discharge_table1.pdf")) # File name
```

### Prior and RECOVERY distributions

```{r}
# Corticosteroids subgroups

# Create data frame

# Not using corticosteroids subgroup

distributions_not =
  posteriors_not_using_discharge %>%
  filter(type == "evidence-based") %>%
  summarise(
    RECOVERY_not = list(rnorm(10e4,
      mean = data.mean,
      sd = data.sd
    )),
    Prior_not = list(rnorm(10e4,
      mean = prior.mean,
      sd = prior.sd
    ))
  ) %>%
  unnest(RECOVERY_not:Prior_not)

# Using corticosteroids subgroup

distributions_u =
  posteriors_using_discharge %>%
  filter(type == "evidence-based") %>%
  summarise(
    RECOVERY_u = list(rnorm(10e4,
      mean = data.mean,
      sd = data.sd
    )),
    Prior_u = list(rnorm(10e4,
      mean = prior.mean,
      sd = prior.sd
    ))
  ) %>%
  unnest(RECOVERY_u:Prior_u)

# Bind altogether

distributions_cortico = bind_cols(
  distributions_not,
  distributions_u
  
)
    
```


```{r}

# Plot!

p1 = distributions_cortico %>%
  # make it tidy for ggplot
  pivot_longer(
    cols = c(RECOVERY_not:Prior_u),
    names_to = "dist", values_to = "samples"
  ) %>%
  mutate(
    # Create new column to be able to use facet at the end
    subgroup = case_when(
      str_detect(dist, "_u") ~ "Using corticosteroids",
      str_detect(dist, "_not") ~ "Not using corticosteroids"
    ),

    # Set order of subgroups
    subgroup = factor(subgroup,
      levels = c(
        "Not using corticosteroids",
        "Using corticosteroids"
      )
    ),

    # Remove "_u" and "_not"
    dist = case_when(
      str_detect(dist, "RECOVERY") ~ "RECOVERY",
      str_detect(dist, "Prior") ~ "Priors",
    ),
    # Set order of distributions
    dist = factor(dist,
      levels = c(
        "RECOVERY",
        "Priors"
      )
    )
  ) %>%
  # exp() to convert log-odds ratio into odds ratio
  ggplot(aes(
    x = exp(samples), y = dist,
    fill = dist
  )) +

  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(position = "dodge",
               point_interval = median_qi, # Quantile interval 
               .width = c(0.95)) +
  geom_vline(xintercept = 1, linetype = 2, size = 0.6) +
  scale_fill_manual(' ',
                    breaks=c("Priors","RECOVERY"),
                    values = c(
    "#F8D08D", # Prior
     "#67B8D5" # RECOVERY
  )) +
  labs(
    x = "\nOdds Ratio",
    y = " "
  ) +
  scale_x_continuous(breaks = seq(from = 0, to = 3, 0.5)) +
  coord_cartesian(xlim = c(0.25, 3),
                  clip = 'off') +
  scale_y_discrete(expand = c(0, 0.5)) +
  theme(
    strip.background = element_rect(fill = "#E4E6E7"),
    strip.text.x = element_text(size = 12),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    legend.position = 'right',
    legend.text = element_text(size=12),
    legend.key= element_blank(),
    plot.margin = margin(20, 0, 25, 25)
  ) +
  facet_wrap(~subgroup, ncol = 1)
  
```

```{r}
## Respiratory support

# Create data frame

# Simple oxygen subgroup

distributions_s =
  posteriors_simple_discharge %>%
  filter(type == "evidence-based") %>%
  summarise(
    RECOVERY_s = list(rnorm(10e4,
      mean = data.mean,
      sd = data.sd
    )),
    Prior_s = list(rnorm(10e4,
      mean = prior.mean,
      sd = prior.sd
    ))
  ) %>%
  unnest(RECOVERY_s:Prior_s)

# Non-invasive ventilation

distributions_n =
  posteriors_noninvasive_discharge %>%
  filter(type == "evidence-based") %>%
  summarise(
    RECOVERY_n = list(rnorm(10e4,
      mean = data.mean,
      sd = data.sd
    )),
    Prior_n = list(rnorm(10e4,
      mean = prior.mean,
      sd = prior.sd
    ))
  ) %>%
  unnest(RECOVERY_n:Prior_n)

# Invasive mechanical ventilation subgroup

distributions_i =
  posteriors_invasive_discharge %>%
  filter(type == "evidence-based") %>%
  summarise(
    RECOVERY_i = list(rnorm(10e4,
      mean = data.mean,
      sd = data.sd
    )),
    Prior_i = list(rnorm(10e4,
      mean = prior.mean,
      sd = prior.sd
    ))
  ) %>%
  unnest(RECOVERY_i:Prior_i)

# Bind altogether

distributions_respiratory = bind_cols(
  distributions_i,
  distributions_n,
  distributions_s
)
```

```{r}

# Plot!

p2 = distributions_respiratory %>%
  # make it tidy for ggplot
  pivot_longer(
    cols = c(RECOVERY_i:Prior_s),
    names_to = "dist", values_to = "samples"
  ) %>%
  mutate(
    # Create new column to be able to use facet at the end
    subgroup = case_when(
      str_detect(dist, "_s") ~ "Simple oxygen only",
      str_detect(dist, "_n") ~ "Non-invasive ventilation",
      str_detect(dist, "_i") ~ "Invasive mechanical ventilation"
    ),

    # Set order of subgroups
    subgroup = factor(subgroup,
      levels = c(
        "Simple oxygen only",
        "Non-invasive ventilation",
        "Invasive mechanical ventilation"
      )
    ),

    # Remove "_i", "_n" and "_s"
    dist = case_when(
      str_detect(dist, "RECOVERY") ~ "RECOVERY",
      str_detect(dist, "Prior") ~ "Priors",
    ),
    # Set order of distributions
    dist = factor(dist,
      levels = c(
        "RECOVERY",
        "Priors"
      )
    )
  ) %>%
  # exp() to convert log-odds ratio into odds ratio
  ggplot(aes(
    x = exp(samples), y = dist,
    fill = dist
  )) +

  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(position = "dodge",
               point_interval = median_qi, # Quantile interval
               .width = c(0.95)) +
  scale_fill_manual(values = c(
    "#67B8D5", # RECOVERY
    "#F8D08D" # Priors
  )) +
  geom_vline(xintercept = 1, linetype = 2, size = 0.6) +
  labs(
    x = "\nOdds Ratio",
    y = " "
  ) +
  scale_x_continuous(breaks = seq(0.5, 3.5, 0.5)) +
  coord_cartesian(xlim = c(0.5, 3.2)) +
  scale_y_discrete(expand = c(0, 0.5)) +
  theme(
    strip.background = element_rect(fill = "#E4E6E7"),
    strip.text.x = element_text(size = 12),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    legend.position = 'none',
    plot.margin = margin(20, 15, 0, 0)
  ) +
  facet_wrap(~subgroup, ncol = 1)
```

```{r, fig.align='center', fig.width=10, fig.height = 6, fig.cap="Point estimates depict the median and interval bars depict 95th quantiles."}
p1 + p2 + plot_annotation(tag_levels = 'A')
```

```{r}
# ggsave(width = 10,
#        height = 6,
#        here("final_analyses", "output", "plots", "appendix", # File path
#                  "SFigure14_discharge_figure1.pdf")) # File name
```


<br><br>

Here are the 95% quantile intervals in *odds ratio* for each distribution from
the figure above.

```{r}
distributions_cortico %>% 
  # make it tidy to be able to use group_by()
  pivot_longer(
    cols = c(RECOVERY_not:Prior_u),
    names_to = "Subgroup", values_to = "samples"
  ) %>% 
  # Group by distribution so we can apply median_qi
  group_by(Subgroup) %>% 
  # Calculate the median and 95% quantile interval in log-odds ratio
  ggdist::median_qi(.width = 0.95) %>% 
  # Select only the relevant columns
  select(Subgroup:.upper) %>% 
  # Exponentiate to transform log-odds ratio into odds ratio
  mutate(across(samples:.upper, ~exp(.))) %>%
  mutate(across(samples:.upper, ~round(., 2))) %>%
  mutate(
    Subgroup = case_when(
      str_detect(Subgroup, "_u") ~ "Using",
      str_detect(Subgroup, "_not") ~ "Not using"
    )) %>%
  rename("Median" = samples,
         "Upper limit" = .upper,
         "Lower limit" = .lower) %>%
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  pack_rows("Priors", 1, 2) %>% 
  pack_rows("RECOVERY", 3, 4) %>% 
  add_header_above(c("Use of corticosteroids" = 4))
```

<br>

```{r}
# https://stackoverflow.com/questions/26548495/reorder-rows-using-custom-order
# create a vector with letters in the desired order
x = c("Prior_s", "Prior_n", "Prior_i",
      "RECOVERY_s", "RECOVERY_n", "RECOVERY_i")

distributions_respiratory %>% 
  # make it tidy to be able to use group_by()
  pivot_longer(
    cols = c(RECOVERY_i:Prior_s),
    names_to = "Subgroup", values_to = "samples"
  ) %>% 
  # Group by distribution so we can apply median_qi
  group_by(Subgroup) %>% 
  # Calculate the median and 95% quantile interval in log-odds ratio
  ggdist::median_qi(.width = 0.95) %>% 
  # Select only the relevant columns
  select(Subgroup:.upper) %>% 
  # Exponentiate to transform log-odds ratio into odds ratio
  mutate(across(samples:.upper, ~exp(.))) %>% 
  mutate(across(samples:.upper, ~round(., 2))) %>%
  # Define order
  mutate(Subgroup = factor(Subgroup, levels = x)) %>% 
  arrange(Subgroup) %>% 
  mutate(
    Subgroup = case_when(
      str_detect(Subgroup, "_s") ~ "Simple oxygen only",
      str_detect(Subgroup, "_n") ~ "Non-invasive ventilation",
      str_detect(Subgroup, "_i") ~ "Invasive mechanical ventilation"
    )) %>% 
  rename("Median" = samples,
         "Upper limit" = .upper,
         "Lower limit" = .lower) %>%
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  pack_rows("Priors", 1, 3) %>% 
  pack_rows("RECOVERY", 4, 6) %>% 
  add_header_above(c("Respiratory support" = 4))
```

### Posteriors distributions

```{r}
# Create data frame

posterior_not_using = 
  samples_posteriors_not_using_discharge %>% 
  filter(`Underlying_Prior` == "Evidence-based") %>% 
  select(`RD`) %>% 
  rename("RD_not" = `RD`)

posterior_using = 
  samples_posteriors_using_discharge %>% 
  filter(`Underlying_Prior` == "Evidence-based") %>% 
  select(`RD`) %>% 
  rename("RD_u" = `RD`)

distributions_cortico_posterior =
  bind_cols(posterior_not_using,
            posterior_using)
```

```{r}
p1 = distributions_cortico_posterior %>%
  # make it tidy for ggplot
  pivot_longer(
    cols = c(RD_not:RD_u),
    names_to = "dist", values_to = "samples"
  ) %>%
  mutate(
    # Create new column to be able to use facet at the end
    subgroup = case_when(
      str_detect(dist, "_u") ~ "Using corticosteroids",
      str_detect(dist, "_not") ~ "Not using corticosteroids"
    ),

    # Set order of subgroups
    subgroup = factor(subgroup,
      levels = c(
        "Not using corticosteroids",
        "Using corticosteroids"
      )
    )) %>%
  
  # Plot!
  ggplot(aes(
    # Multiply by 100 to report in percentage
    x = 100 * samples, y = dist,
    fill = subgroup
  )) +

  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(point_interval = median_hdi, # Highest density interval
               .width = c(0.50, 0.95),
               # https://github.com/mjskay/ggdist/issues/70
               interval_size_range = c(1.1,1.9)) +
  scale_fill_manual(values = c("#9EA45B", "#A65041")) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.6) +
  labs(
    x = "\nRisk Difference (%)",
    y = " "
  ) +
  scale_x_continuous(breaks = seq(from = -15, to = 5, 2.5)) +
  coord_cartesian(xlim = c(-15, 5)) +
  scale_y_discrete(expand = c(0, 0.5)) +
  theme(
    strip.background = element_rect(fill = "#E4E6E7"),
    strip.text.x = element_text(size = 12),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    legend.position = 'none',
    plot.margin = margin(20, 10, 20, 10)
  ) +
  facet_wrap(~subgroup, ncol = 1, scales = "free_y")
```

```{r warning=FALSE, include=FALSE}
p2 = distributions_cortico_posterior %>%
  # make it tidy for ggplot
  pivot_longer(
    cols = c(RD_not:RD_u),
    names_to = "dist", values_to = "samples"
  ) %>%
  mutate(
    # Create new column to be able to use facet at the end
    subgroup = case_when(
      str_detect(dist, "_u") ~ "Using corticosteroids",
      str_detect(dist, "_not") ~ "Not using corticosteroids"
    ),

    # Set order of subgroups
    subgroup = factor(subgroup,
      levels = c(
        "Not using corticosteroids",
        "Using corticosteroids"
      )
    )) %>% 
  
# Multiply by 100 to report in percentage
ggplot(aes(100 * samples, colour = subgroup)) +
  stat_ecdf(geom = "step", size = 1.2) +
  scale_color_manual(' ',
                    values = c("#9EA45B", "#A65041")) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.6) +
    labs(
      x = "\nRisk Difference (%)",
      y = "Probability RD \u2264 X\n"
      ) +
    scale_x_continuous(
      breaks = seq(from = -15, to = 10, 1),
      limits = c(-15, 10)) +
    scale_y_continuous(
      breaks = seq(from = 0, to = 1, .1),
      expand = c(0, .03)
    ) +
  theme(
      axis.ticks.x = element_blank(),
      panel.background = element_blank(),
      panel.grid.major.x = element_line(color = "gray80", size = 0.3),
      panel.grid.major.y = element_line(color = "gray80", size = 0.3),
      legend.position = 'none',
      plot.margin = margin(20, 10, 20, 10)
     ) +
  coord_cartesian(x = c(-12.5,0.1))
  
```


```{r}
# Create data frame

# Simple oxygen only

posterior_s = 
  samples_posteriors_simple_discharge %>% 
  filter(`Underlying_Prior` == "Evidence-based") %>% 
  select(`RD`) %>% 
  rename("RD_s" = `RD`)

# Non-invasive ventilation

posterior_n = 
  samples_posteriors_noninvasive_discharge %>% 
  filter(`Underlying_Prior` == "Evidence-based") %>% 
  select(`RD`) %>% 
  rename("RD_n" = `RD`)

# Invasive mechanical ventilation

posterior_i = 
  samples_posteriors_invasive_discharge %>% 
  filter(`Underlying_Prior` == "Evidence-based") %>% 
  select(`RD`) %>% 
  rename("RD_i" = `RD`)

# Bind altogether

distributions_respiratory_posterior = bind_cols(
  posterior_i,
  posterior_n,
  posterior_s
)

```

```{r}

p3 = distributions_respiratory_posterior %>%
  # make it tidy for ggplot
  pivot_longer(
    cols = c(RD_i:RD_s),
    names_to = "dist", values_to = "samples"
  ) %>%
  mutate(
    # Create new column to be able to use facet at the end
    subgroup = case_when(
      str_detect(dist, "_s") ~ "Simple oxygen only",
      str_detect(dist, "_n") ~ "Non-invasive ventilation",
      str_detect(dist, "_i") ~ "Invasive mechanical ventilation"
    ),

    # Set order of subgroups
    subgroup = factor(subgroup,
      levels = c(
        "Simple oxygen only",
        "Non-invasive ventilation",
        "Invasive mechanical ventilation"
      ))
    ) %>%
  # Plot!
  ggplot(aes(
    # Multiply by 100 to report in percentage
    x = 100 * samples, y = dist,
    fill = subgroup
  )) +

  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(point_interval = median_hdi, # Highest density interval
               .width = c(0.50, 0.95),
               # https://github.com/mjskay/ggdist/issues/70
               interval_size_range = c(1.1,1.9)) +
  scale_fill_manual(values = c("#D9BC8C", # Simple oxyge
                               "#9d95c6", # Non-invasive
                               "#7D8D87") # Invasive
                    ) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.6) +
  labs(
    x = "\nRisk Difference (%)",
    y = " "
  ) +
  scale_x_continuous(breaks = seq(from = -15, to = 5, 2.5)) +
  coord_cartesian(xlim = c(-15, 5)) +
  scale_y_discrete(expand = c(0, 0.5)) +
  theme(
    strip.background = element_rect(fill = "#E4E6E7"),
    strip.text.x = element_text(size = 12),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    legend.position = 'none',
    plot.margin = margin(20, 10, 20, 10)
  ) +
  facet_wrap(~ subgroup, ncol = 1, scales = "free_y")

```

```{r warning=FALSE}
p4 = distributions_respiratory_posterior %>%
  # make it tidy for ggplot
  pivot_longer(
    cols = c(RD_i:RD_s),
    names_to = "dist", values_to = "samples"
  ) %>%
  mutate(
    # Create new column to be able to use facet at the end
    subgroup = case_when(
      str_detect(dist, "_s") ~ "Simple oxygen only",
      str_detect(dist, "_n") ~ "Non-invasive ventilation",
      str_detect(dist, "_i") ~ "Invasive mechanical ventilation"
    ),

    # Set order of subgroups
    subgroup = factor(subgroup,
      levels = c(
        "Simple oxygen only",
        "Non-invasive ventilation",
        "Invasive mechanical ventilation"
      ))
    ) %>%
# Multiply by 100 to report in percentage
ggplot(aes(100*samples, colour = subgroup)) +
  stat_ecdf(geom = "step", size = 1.2) +
  scale_color_manual(' ',
                    values = c("#D9BC8C", # Simple oxyge
                               "#9d95c6", # Non-invasive
                               "#7D8D87") # Invasive
                    ) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.6) +
    labs(
      x = "\nRisk Difference (%)",
      y = "Probability RD \u2264 X\n"
      ) +
    scale_x_continuous(
      breaks = seq(from = -15, to = 10, 1),
      limits = c(-15, 10)) +
    scale_y_continuous(
      breaks = seq(from = 0, to = 1, .1),
      expand = c(0, .03)
    ) +
  theme(
      axis.ticks.x = element_blank(),
      panel.background = element_blank(),
      panel.grid.major.x = element_line(color = "gray80", size = 0.3),
      panel.grid.major.y = element_line(color = "gray80", size = 0.3),
      legend.position = 'none',
      plot.margin = margin(20, 10, 20, 10)
    ) +
  coord_cartesian(x = c(-12.5,0.1))
```

```{r , fig.align='center', fig.width=10, fig.height = 8.5, warning=FALSE, fig.cap="Panels A and C: Point estimates depict the median. Interval bars depict the 50 and 95% highest density intervals. Panels B and D: Cumulative posterior distributions correspond to the probabilities that the risk difference (RD) is less than or equal to the effect size on the Xaxis."}
(p1 + p2) / (p3 + p4) + plot_annotation(tag_levels = 'A')
```

```{r}
# ggsave(width = 10,
#        height = 8.5,
#  #https://stackoverflow.com/questions/12768176/unicode-characters-in-ggplot2-pdf-output
#         device=cairo_pdf, 
#         here("final_analyses", "output", "plots", "appendix", # File path
#                   "SFigure15_discharge_figure2.pdf")) # File name
```


<br><br>

```{r}
multiply100 = function(x){x*100}

t1 = distributions_cortico_posterior %>%
  # make it tidy to be able to use group_by()
  pivot_longer(
    cols = c(RD_not:RD_u),
    names_to = "Subgroup", values_to = "samples"
  ) %>% 
  group_by(Subgroup) %>% 
  summarise("Pr(\u2264 0%)" = (sum( samples <= 0))/ n(),
            "Pr(\u2264 -1%)" = (sum( samples <= -0.01))/ n(),
            "Pr(\u2264 -2%)" = (sum( samples <= -0.02))/ n(),
            "Pr(\u2264 -5%)" = (sum( samples <= -0.05))/ n()) %>% 
  mutate(across(-Subgroup, ~multiply100(.))) %>% 
  mutate(across(-Subgroup, ~round(.,1))) %>% 
  mutate(
    Subgroup = case_when(
      str_detect(Subgroup, "_u") ~ "Using",
      str_detect(Subgroup, "_not") ~ "Not using"
    ))

```


```{r}
multiply100 = function(x){x*100}
t2 = distributions_cortico_posterior %>% 
  # make it tidy to be able to use group_by()
  pivot_longer(
    cols = c(RD_not:RD_u),
    names_to = "Subgroup", values_to = "samples"
  ) %>% 
  # Group by distribution so we can apply median_hdi
  group_by(Subgroup) %>% 
  # Calculate the median and 95% quantile interval in log-odds ratio
  ggdist::median_hdi(.width = 0.95) %>% 
  # Select only the relevant columns
  select(Subgroup:.upper) %>%
  mutate(across(samples:.upper, ~multiply100(.))) %>%
  mutate(across(samples:.upper, ~round(., 2))) %>%
  rename("Median" = samples,
         "Upper limit" = .upper,
         "Lower limit" = .lower) %>% 
  mutate(
    Subgroup = case_when(
      str_detect(Subgroup, "_u") ~ "Using",
      str_detect(Subgroup, "_not") ~ "Not using"
    ))
```

```{r}
multiply100 = function(x){x*100}

t3 = distributions_respiratory_posterior %>%
  # make it tidy to be able to use group_by()
  pivot_longer(
    cols = c(RD_i:RD_s),
    names_to = "Subgroup", values_to = "samples"
  ) %>% 
  group_by(Subgroup) %>% 
  summarise("Pr(\u2264 0%)" = (sum( samples <= 0))/ n(),
            "Pr(\u2264 -1%)" = (sum( samples <= -0.01))/ n(),
            "Pr(\u2264 -2%)" = (sum( samples <= -0.02))/ n(),
            "Pr(\u2264 -5%)" = (sum( samples <= -0.05))/ n()) %>% 
  mutate(across(-Subgroup, ~multiply100(.))) %>% 
  mutate(across(-Subgroup, ~round(.,1))) %>%
  arrange(desc(Subgroup)) %>% 
  mutate(
    Subgroup = case_when(
      str_detect(Subgroup, "_s") ~ "Simple oxygen only",
      str_detect(Subgroup, "_n") ~ "Non-invasive ventilation",
      str_detect(Subgroup, "_i") ~ "Invasive mechanical ventilation"
    ))

```

```{r}
multiply100 = function(x){x*100}

t4 = distributions_respiratory_posterior %>% 
  # make it tidy to be able to use group_by()
  pivot_longer(
    cols = c(RD_i:RD_s),
    names_to = "Subgroup", values_to = "samples"
  ) %>% 
  # Group by distribution so we can apply median_hdi
  group_by(Subgroup) %>% 
  # Calculate the median and 95% quantile interval in log-odds ratio
  ggdist::median_hdi(.width = 0.95) %>% 
  # Select only the relevant columns
  select(Subgroup:.upper) %>%
  mutate(across(samples:.upper, ~multiply100(.))) %>%
  mutate(across(samples:.upper, ~round(., 2))) %>%
  rename("Median" = samples,
         "Upper limit" = .upper,
         "Lower limit" = .lower) %>% 
  arrange(desc(Subgroup)) %>% 
  mutate(
    Subgroup = case_when(
      str_detect(Subgroup, "_s") ~ "Simple oxygen only",
      str_detect(Subgroup, "_n") ~ "Non-invasive ventilation",
      str_detect(Subgroup, "_i") ~ "Invasive mechanical ventilation"
    ))
```

Here are the posterior probabilities for each posterior distribution.

```{r}
bind_rows(t1,t3) %>% 
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  pack_rows("Use of corticosteroids", 1, 2) %>% 
  pack_rows("Respiratory support", 3, 5) %>% 
  add_header_above(c(" " = 1,
                     "Probability of Risk Difference \u2265 X%" = 4))
```

<br><br>

Here are the 95% HDI in *risk difference* of each posterior distribution.

```{r}
bind_rows(t2,t4) %>% 
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  pack_rows("Use of corticosteroids", 1, 2) %>% 
  pack_rows("Respiratory support", 3, 5) %>% 
  add_header_above(c(" " = 1,
                     "95% Highest Density Interval" = 3))
```

<br><br>


## Sensitivity analyses: different priors

### Not using corticosteroids

#### Prior and likelihood distributions

```{r}

distributions =
  tibble(
    
    "RECOVERY (likelihood)" = list(
      rnorm(
        10e4,
        mean = (posteriors_not_using_discharge %>%
                # Data.mean and data.sd are all the same in every row
                # So it doesn't matter what row I slice
                slice(1) %>% 
                pull(data.mean)),
        sd = (posteriors_not_using_discharge %>%
              slice(1) %>% 
              pull(data.sd))
    )),
    
    "Non-informative prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_not_using_discharge %>%
                filter(type == "non-informative") %>%
                pull(prior.mean)),
        sd = (posteriors_not_using_discharge %>%
              filter(type == "non-informative") %>%
              pull(prior.sd))
    )),
    
    "Evidence-based prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_not_using_discharge %>%
                filter(type == "evidence-based") %>%
                pull(prior.mean)),
        sd = (posteriors_not_using_discharge %>%
              filter(type == "evidence-based") %>%
              pull(prior.sd))
    )),
    
    "Skeptical prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_not_using_discharge %>%
                filter(type == "skeptical") %>%
                pull(prior.mean)),
        sd = (posteriors_not_using_discharge %>%
              filter(type == "skeptical") %>%
              pull(prior.sd))
    )),
    
    "Optimistic prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_not_using_discharge %>%
                filter(type == "optimistic") %>%
                pull(prior.mean)),
        sd = (posteriors_not_using_discharge %>%
              filter(type == "optimistic") %>%
              pull(prior.sd))
    )),
    
    "Pessimistic prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_not_using_discharge %>%
                filter(type == "pessimistic") %>%
                pull(prior.mean)),
        sd = (posteriors_not_using_discharge %>%
              filter(type == "pessimistic") %>%
              pull(prior.sd))
    ))
  ) %>% 
  unnest(everything())

    
```


```{r, fig.height=5.5, fig.width = 5.5, fig.align='center'}

# Plot!

distributions %>%
  # make it tidy for ggplot
  pivot_longer(
    cols = c(everything()),
    names_to = "dist", values_to = "samples"
  ) %>%
  # Set order of priors
  mutate(dist = factor(dist, levels =
                         c("RECOVERY (likelihood)",
                           "Non-informative prior",
                           "Evidence-based prior",
                           "Skeptical prior",
                           "Optimistic prior",
                           "Pessimistic prior")
                       )
         ) %>%
  # exp() to transform log(OR) to OR
  ggplot(aes(
    x = exp(samples), y = dist,
    fill = dist
  )) +

  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(position = "dodge",
               point_interval = median_qi, # Quantile interval 
               .width = c(0.95)) +
  geom_vline(xintercept = 1, linetype = 2, size = 0.6) +
  scale_fill_manual(' ',
                    values = c(
    carto_pal(12, "Pastel")[1], # RECOVERY
    carto_pal(12, "Pastel")[12], # Non-informative,
    carto_pal(12, "Pastel")[2], # Evidence-based
    "gray70", # Skeptical
    carto_pal(12, "Pastel")[5], # Optimistic
    carto_pal(12, "Pastel")[10]  # Pessimistc
  )) +
  labs(
    x = "\nOdds Ratio",
    y = " "
  ) +
  scale_x_continuous(breaks = seq(from = 0, to = 3, 0.5)) +
  scale_y_discrete(expand = c(0, 0.5)) +
  theme(
    strip.background = element_rect(fill = "#E4E6E7"),
    strip.text.x = element_text(size = 12),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    legend.position = 'none',
    legend.text = element_text(size=12),
    legend.key= element_blank(),
    plot.margin = margin(20, 20, 20, 20)
  ) +
  coord_cartesian(x = c(0, 3)) +
  facet_wrap(~dist, ncol = 1, scales = "free_y")
  
```

#### Posterior distributions

```{r, , fig.align='center', fig.width=7, fig.height = 4.5, fig.cap="Point estimates depict the median. Interval bars depict the 50 and 95% highest density intervals."}

level_order = c("Pessimistic",
                "Optimistic",
                "Skeptical",
                "Evidence-based",
                "Non-informative")

samples_posteriors_not_using_discharge %>%
  
  ggplot(aes(
    # Multiply by 100 to report in percentage
    x = 100 * RD,
    y = factor(`Underlying_Prior`, level = level_order),
    fill = `Underlying_Prior`)) +

  # https://mjskay.github.io/ggdist/articles/slabinterval.html
    stat_halfeye(aes(fill = stat(x < 0)),
                 position = "dodge",
               point_interval = median_hdi, # Highest density interval
               .width = c(0.5, 0.95),
               # https://github.com/mjskay/ggdist/issues/70
               interval_size_range = c(1.1,1.9)
  ) +
  scale_fill_manual(values = c("gray85", "#64A37E")) +
  labs(x = "\nRisk Difference (%)",
       y = "Underlying Prior\n"
  ) +
  scale_x_continuous(breaks = seq(from = -12.5, to = 10, 2.5)) +
  scale_y_discrete(expand = c(0, 0.3)) +
  theme(axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 13.5),
    axis.text.y = element_text(size = 12),
    axis.text.x = element_text(size = 12),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    legend.position = "none",
    plot.title.position = 'plot',
    plot.margin = margin(20, 25, 10, 20)
  ) +
  coord_cartesian(xlim = c(-12.5, 10))

# ggsave(width = 7,
#        height = 4.5,
#         here("final_analyses", "output", "plots", "appendix", # File path
#                   "SFigure16_discharge_posteriors_not_using.pdf")) # File name
```

<br><br>


```{r}

t = tibble(
  
  "Underlying Prior" = c(
    "Non-informative",
    "Evidence-based",
    "Skeptical",
    "Optimistic",
    "Pessimistic"
  ),
  
  
  "Pr(< -5%)" = c(round((samples_posteriors_not_using_discharge %>%
                           filter(`Underlying_Prior` == "Non-informative") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_not_using_discharge %>%
                           filter(`Underlying_Prior` == "Evidence-based") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_not_using_discharge %>%
                           filter(`Underlying_Prior` == "Skeptical") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_not_using_discharge %>%
                           filter(`Underlying_Prior` == "Optimistic") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_not_using_discharge %>%
                           filter(`Underlying_Prior` == "Pessimistic") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100
  ),
  
  "Pr(< -2%)" = c(round((samples_posteriors_not_using_discharge %>%
                           filter(`Underlying_Prior` == "Non-informative") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_not_using_discharge %>%
                           filter(`Underlying_Prior` == "Evidence-based") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_not_using_discharge %>%
                           filter(`Underlying_Prior` == "Skeptical") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_not_using_discharge %>%
                           filter(`Underlying_Prior` == "Optimistic") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_not_using_discharge %>%
                           filter(`Underlying_Prior` == "Pessimistic") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100
  ),
  
  "Pr(< -1%)" = c(round((samples_posteriors_not_using_discharge %>%
                           filter(`Underlying_Prior` == "Non-informative") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_not_using_discharge %>%
                           filter(`Underlying_Prior` == "Evidence-based") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_not_using_discharge %>%
                           filter(`Underlying_Prior` == "Skeptical") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_not_using_discharge %>%
                           filter(`Underlying_Prior` == "Optimistic") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_not_using_discharge %>%
                           filter(`Underlying_Prior` == "Pessimistic") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100
  ),
  
  
  "Pr(< 0%)" = c(round((samples_posteriors_not_using_discharge %>%
                          filter(`Underlying_Prior` == "Non-informative") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_not_using_discharge %>%
                          filter(`Underlying_Prior` == "Evidence-based") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_not_using_discharge %>%
                          filter(`Underlying_Prior` == "Skeptical") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_not_using_discharge %>%
                          filter(`Underlying_Prior` == "Optimistic") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_not_using_discharge %>%
                          filter(`Underlying_Prior` == "Pessimistic") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100
  ),
  
  "Pr(> 1%)" = c(round((samples_posteriors_not_using_discharge %>%
                          filter(`Underlying_Prior` == "Non-informative") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_not_using_discharge %>%
                          filter(`Underlying_Prior` == "Evidence-based") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_not_using_discharge %>%
                          filter(`Underlying_Prior` == "Skeptical") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_not_using_discharge %>%
                          filter(`Underlying_Prior` == "Optimistic") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_not_using_discharge %>%
                          filter(`Underlying_Prior` == "Pessimistic") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100
  ),
  
  "Pr(> 2%)" = c(round((samples_posteriors_not_using_discharge %>%
                          filter(`Underlying_Prior` == "Non-informative") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_not_using_discharge %>%
                          filter(`Underlying_Prior` == "Evidence-based") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_not_using_discharge %>%
                          filter(`Underlying_Prior` == "Skeptical") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_not_using_discharge %>%
                          filter(`Underlying_Prior` == "Optimistic") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_not_using_discharge %>%
                          filter(`Underlying_Prior` == "Pessimistic") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100
  ),
  
  "Pr(> 5%)" = c(round((samples_posteriors_not_using_discharge %>%
                          filter(`Underlying_Prior` == "Non-informative") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_not_using_discharge %>%
                          filter(`Underlying_Prior` == "Evidence-based") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_not_using_discharge %>%
                          filter(`Underlying_Prior` == "Skeptical") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_not_using_discharge %>%
                          filter(`Underlying_Prior` == "Optimistic") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_not_using_discharge %>%
                          filter(`Underlying_Prior` == "Pessimistic") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100
  )
) 

t1 = t %>% 
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1,
                     "Probability of Benefit" = 4,
                     "Probability of Harm" = 3))

t1

t1 %>% 
  save_kable(here("final_analyses", "output", "plots", "appendix", # File path
                  "STable14_discharge_probabilities_not_using.pdf")) # File name
```

##### HDI for each posterior distribution

Here are the 95% HDI in *risk difference* of each distribution.

```{r}
multiply100 = function(x){x*100}

samples_posteriors_not_using_discharge %>%
  select("Underlying_Prior", "RD") %>% 
  # Group by distribution so we can apply median_hdi
  group_by(`Underlying_Prior`) %>% 
  # Calculate the median and 95% quantile interval in log-odds ratio
  ggdist::median_hdi(.width = 0.95) %>% 
  # Select only the relevant columns
  # Arrange order
  arrange(factor(`Underlying_Prior`, levels = c(
    "Non-informative",
    "Evidence-based",
    "Skeptical",
    "Optimistic",
    "Pessimistic"
    ))) %>% 
  select("Underlying_Prior":.upper) %>%
  mutate(across(RD:.upper, ~multiply100(.))) %>%
  mutate(across(RD:.upper, ~round(., 2))) %>%
  rename("Underlying Prior" = Underlying_Prior,
         "Median" = RD,
         "Upper limit" = .upper,
         "Lower limit" = .lower) %>% 
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1,
                     "95% Highest Density Interval" = 3))
```

<br><br>

### Using corticosteroids

#### Prior and likelihood distributions

```{r}

distributions =
  tibble(
    
    "RECOVERY (likelihood)" = list(
      rnorm(
        10e4,
        mean = (posteriors_using_discharge %>%
                  # Data.mean and data.sd are all the same in every row
                  # So it doesn't matter what row I slice
                  slice(1) %>% 
                  pull(data.mean)),
        sd = (posteriors_using_discharge %>%
                slice(1) %>% 
                pull(data.sd))
      )),
    
    "Non-informative prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_using_discharge %>%
                  filter(type == "non-informative") %>%
                  pull(prior.mean)),
        sd = (posteriors_using_discharge %>%
                filter(type == "non-informative") %>%
                pull(prior.sd))
      )),
    
    "Evidence-based prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_using_discharge %>%
                  filter(type == "evidence-based") %>%
                  pull(prior.mean)),
        sd = (posteriors_using_discharge %>%
                filter(type == "evidence-based") %>%
                pull(prior.sd))
      )),
    
    "Skeptical prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_using_discharge %>%
                  filter(type == "skeptical") %>%
                  pull(prior.mean)),
        sd = (posteriors_using_discharge %>%
                filter(type == "skeptical") %>%
                pull(prior.sd))
      )),
    
    "Optimistic prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_using_discharge %>%
                  filter(type == "optimistic") %>%
                  pull(prior.mean)),
        sd = (posteriors_using_discharge %>%
                filter(type == "optimistic") %>%
                pull(prior.sd))
      )),
    
    "Pessimistic prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_using_discharge %>%
                  filter(type == "pessimistic") %>%
                  pull(prior.mean)),
        sd = (posteriors_using_discharge %>%
                filter(type == "pessimistic") %>%
                pull(prior.sd))
      ))
  ) %>% 
  unnest(everything())


```


```{r, fig.height=5.5, fig.width = 5.5, fig.align='center'}

# Plot!

distributions %>%
  # make it tidy for ggplot
  pivot_longer(
    cols = c(everything()),
    names_to = "dist", values_to = "samples"
  ) %>%
  # Set order of priors
  mutate(dist = factor(dist, levels =
                         c("RECOVERY (likelihood)",
                           "Non-informative prior",
                           "Evidence-based prior",
                           "Skeptical prior",
                           "Optimistic prior",
                           "Pessimistic prior")
  )
  ) %>%
  # exp() to transform log(OR) to OR
  ggplot(aes(
    x = exp(samples), y = dist,
    fill = dist
  )) +
  
  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(position = "dodge",
               point_interval = median_qi, # Quantile interval 
               .width = c(0.95)) +
  geom_vline(xintercept = 1, linetype = 2, size = 0.6) +
  scale_fill_manual(' ',
                    values = c(
                      carto_pal(12, "Pastel")[1], # RECOVERY
                      carto_pal(12, "Pastel")[12], # Non-informative,
                      carto_pal(12, "Pastel")[2], # Evidence-based
                      "gray70", # Skeptical
                      carto_pal(12, "Pastel")[5], # Optimistic
                      carto_pal(12, "Pastel")[10]  # Pessimistc
                    )) +
  labs(
    x = "\nOdds Ratio",
    y = " "
  ) +
  scale_x_continuous(breaks = seq(from = 0, to = 3, 0.5)) +
  scale_y_discrete(expand = c(0, 0.5)) +
  theme(
    strip.background = element_rect(fill = "#E4E6E7"),
    strip.text.x = element_text(size = 12),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    legend.position = 'none',
    legend.text = element_text(size=12),
    legend.key= element_blank(),
    plot.margin = margin(20, 20, 20, 20)
  ) +
  coord_cartesian(x = c(0, 3)) +
  facet_wrap(~dist, ncol = 1, scales = "free_y")

```

#### Posterior distributions

```{r, , fig.align='center', fig.width=7, fig.height = 4.5, fig.cap="Point estimates depict the median. Interval bars depict the 50 and 95% highest density intervals."}

level_order = c("Pessimistic",
                "Optimistic",
                "Skeptical",
                "Evidence-based",
                "Non-informative")

samples_posteriors_using_discharge %>%
  
  ggplot(aes(
    # Multiply by 100 to report in percentage
    x = 100 * RD,
    y = factor(`Underlying_Prior`, level = level_order),
    fill = `Underlying_Prior`)) +
  
  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(aes(fill = stat(x < 0)),
               position = "dodge",
               point_interval = median_hdi, # Highest density interval
               .width = c(0.5, 0.95),
               # https://github.com/mjskay/ggdist/issues/70
               interval_size_range = c(1.1,1.9)
  ) +
  scale_fill_manual(values = c("gray85", "#64A37E")) +
  labs(x = "\nRisk Difference (%)",
       y = "Underlying Prior\n"
  ) +
  scale_x_continuous(breaks = seq(from = -12.5, to = 10, 2.5)) +
  scale_y_discrete(expand = c(0, 0.3)) +
  theme(axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 13.5),
        axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 12),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_blank(),
        panel.grid.major.x = element_line(color = "gray80", size = 0.3),
        legend.position = "none",
        plot.title.position = 'plot',
        plot.margin = margin(20, 25, 10, 20)
  ) +
  coord_cartesian(xlim = c(-12.5, 10))

# ggsave(width = 7,
#        height = 4.5,
#         here("final_analyses", "output", "plots", "appendix", # File path
#                   "SFigure17_discharge_posteriors_using.pdf")) # File name
```

<br><br>
  
  
```{r}

t = tibble(
  
  "Underlying Prior" = c(
    "Non-informative",
    "Evidence-based",
    "Skeptical",
    "Optimistic",
    "Pessimistic"
  ),
  
  
  "Pr(< -5%)" = c(round((samples_posteriors_using_discharge %>%
                           filter(`Underlying_Prior` == "Non-informative") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_using_discharge %>%
                           filter(`Underlying_Prior` == "Evidence-based") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_using_discharge %>%
                           filter(`Underlying_Prior` == "Skeptical") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_using_discharge %>%
                           filter(`Underlying_Prior` == "Optimistic") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_using_discharge %>%
                           filter(`Underlying_Prior` == "Pessimistic") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100
  ),
  
  "Pr(< -2%)" = c(round((samples_posteriors_using_discharge %>%
                           filter(`Underlying_Prior` == "Non-informative") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_using_discharge %>%
                           filter(`Underlying_Prior` == "Evidence-based") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_using_discharge %>%
                           filter(`Underlying_Prior` == "Skeptical") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_using_discharge %>%
                           filter(`Underlying_Prior` == "Optimistic") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_using_discharge %>%
                           filter(`Underlying_Prior` == "Pessimistic") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100
  ),
  
  "Pr(< -1%)" = c(round((samples_posteriors_using_discharge %>%
                           filter(`Underlying_Prior` == "Non-informative") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_using_discharge %>%
                           filter(`Underlying_Prior` == "Evidence-based") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_using_discharge %>%
                           filter(`Underlying_Prior` == "Skeptical") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_using_discharge %>%
                           filter(`Underlying_Prior` == "Optimistic") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_using_discharge %>%
                           filter(`Underlying_Prior` == "Pessimistic") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100
  ),
  
  
  "Pr(< 0%)" = c(round((samples_posteriors_using_discharge %>%
                          filter(`Underlying_Prior` == "Non-informative") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_using_discharge %>%
                          filter(`Underlying_Prior` == "Evidence-based") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_using_discharge %>%
                          filter(`Underlying_Prior` == "Skeptical") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_using_discharge %>%
                          filter(`Underlying_Prior` == "Optimistic") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_using_discharge %>%
                          filter(`Underlying_Prior` == "Pessimistic") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100
  ),
  
  "Pr(> 1%)" = c(round((samples_posteriors_using_discharge %>%
                          filter(`Underlying_Prior` == "Non-informative") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_using_discharge %>%
                          filter(`Underlying_Prior` == "Evidence-based") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_using_discharge %>%
                          filter(`Underlying_Prior` == "Skeptical") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_using_discharge %>%
                          filter(`Underlying_Prior` == "Optimistic") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_using_discharge %>%
                          filter(`Underlying_Prior` == "Pessimistic") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100
  ),
  
  "Pr(> 2%)" = c(round((samples_posteriors_using_discharge %>%
                          filter(`Underlying_Prior` == "Non-informative") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_using_discharge %>%
                          filter(`Underlying_Prior` == "Evidence-based") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_using_discharge %>%
                          filter(`Underlying_Prior` == "Skeptical") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_using_discharge %>%
                          filter(`Underlying_Prior` == "Optimistic") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_using_discharge %>%
                          filter(`Underlying_Prior` == "Pessimistic") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100
  ),
  
  "Pr(> 5%)" = c(round((samples_posteriors_using_discharge %>%
                          filter(`Underlying_Prior` == "Non-informative") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_using_discharge %>%
                          filter(`Underlying_Prior` == "Evidence-based") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_using_discharge %>%
                          filter(`Underlying_Prior` == "Skeptical") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_using_discharge %>%
                          filter(`Underlying_Prior` == "Optimistic") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_using_discharge %>%
                          filter(`Underlying_Prior` == "Pessimistic") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100
  )
) 

t1 = t %>% 
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1,
                     "Probability of Benefit" = 4,
                     "Probability of Harm" = 3))

t1

#t1 %>% 
#  save_kable(here("final_analyses", "output", "plots", "appendix", # File path
#                  "STable15_discharge_probabilities_using.pdf")) # File name
```

##### HDI for each posterior distribution

Here are the 95% HDI in *risk difference* of each distribution.

```{r}
multiply100 = function(x){x*100}

samples_posteriors_using_discharge %>%
  select("Underlying_Prior", "RD") %>% 
  # Group by distribution so we can apply median_hdi
  group_by(`Underlying_Prior`) %>% 
  # Calculate the median and 95% quantile interval in log-odds ratio
  ggdist::median_hdi(.width = 0.95) %>% 
  # Select only the relevant columns
  # Arrange order
  arrange(factor(`Underlying_Prior`, levels = c(
    "Non-informative",
    "Evidence-based",
    "Skeptical",
    "Optimistic",
    "Pessimistic"
    ))) %>% 
  select("Underlying_Prior":.upper) %>%
  mutate(across(RD:.upper, ~multiply100(.))) %>%
  mutate(across(RD:.upper, ~round(., 2))) %>%
  rename("Underlying Prior" = Underlying_Prior,
         "Median" = RD,
         "Upper limit" = .upper,
         "Lower limit" = .lower) %>% 
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1,
                     "95% Highest Density Interval" = 3))
```

### Simple oxygen only

#### Prior and likelihood distributions

```{r}

distributions =
  tibble(
    
    "RECOVERY (likelihood)" = list(
      rnorm(
        10e4,
        mean = (posteriors_simple_discharge %>%
                  # Data.mean and data.sd are all the same in every row
                  # So it doesn't matter what row I slice
                  slice(1) %>% 
                  pull(data.mean)),
        sd = (posteriors_simple_discharge %>%
                slice(1) %>% 
                pull(data.sd))
      )),
    
    "Non-informative prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_simple_discharge %>%
                  filter(type == "non-informative") %>%
                  pull(prior.mean)),
        sd = (posteriors_simple_discharge %>%
                filter(type == "non-informative") %>%
                pull(prior.sd))
      )),
    
    "Evidence-based prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_simple_discharge %>%
                  filter(type == "evidence-based") %>%
                  pull(prior.mean)),
        sd = (posteriors_simple_discharge %>%
                filter(type == "evidence-based") %>%
                pull(prior.sd))
      )),
    
    "Skeptical prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_simple_discharge %>%
                  filter(type == "skeptical") %>%
                  pull(prior.mean)),
        sd = (posteriors_simple_discharge %>%
                filter(type == "skeptical") %>%
                pull(prior.sd))
      )),
    
    "Optimistic prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_simple_discharge %>%
                  filter(type == "optimistic") %>%
                  pull(prior.mean)),
        sd = (posteriors_simple_discharge %>%
                filter(type == "optimistic") %>%
                pull(prior.sd))
      )),
    
    "Pessimistic prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_simple_discharge %>%
                  filter(type == "pessimistic") %>%
                  pull(prior.mean)),
        sd = (posteriors_simple_discharge %>%
                filter(type == "pessimistic") %>%
                pull(prior.sd))
      ))
  ) %>% 
  unnest(everything())


```


```{r, fig.height=5.5, fig.width = 5.5, fig.align='center'}

# Plot!

distributions %>%
  # make it tidy for ggplot
  pivot_longer(
    cols = c(everything()),
    names_to = "dist", values_to = "samples"
  ) %>%
  # Set order of priors
  mutate(dist = factor(dist, levels =
                         c("RECOVERY (likelihood)",
                           "Non-informative prior",
                           "Evidence-based prior",
                           "Skeptical prior",
                           "Optimistic prior",
                           "Pessimistic prior")
  )
  ) %>%
  # exp() to transform log(OR) to OR
  ggplot(aes(
    x = exp(samples), y = dist,
    fill = dist
  )) +
  
  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(position = "dodge",
               point_interval = median_qi, # Quantile interval 
               .width = c(0.95)) +
  geom_vline(xintercept = 1, linetype = 2, size = 0.6) +
  scale_fill_manual(' ',
                    values = c(
                      carto_pal(12, "Pastel")[1], # RECOVERY
                      carto_pal(12, "Pastel")[12], # Non-informative,
                      carto_pal(12, "Pastel")[2], # Evidence-based
                      "gray70", # Skeptical
                      carto_pal(12, "Pastel")[5], # Optimistic
                      carto_pal(12, "Pastel")[10]  # Pessimistc
                    )) +
  labs(
    x = "\nOdds Ratio",
    y = " "
  ) +
  scale_x_continuous(breaks = seq(from = 0, to = 3, 0.5)) +
  scale_y_discrete(expand = c(0, 0.5)) +
  theme(
    strip.background = element_rect(fill = "#E4E6E7"),
    strip.text.x = element_text(size = 12),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    legend.position = 'none',
    legend.text = element_text(size=12),
    legend.key= element_blank(),
    plot.margin = margin(20, 20, 20, 20)
  ) +
  coord_cartesian(x = c(0, 3)) +
  facet_wrap(~dist, ncol = 1, scales = "free_y")

```

#### Posterior distributions

```{r, , fig.align='center', fig.width=7, fig.height = 4.5, fig.cap="Point estimates depict the median. Interval bars depict the 50 and 95% highest density intervals."}

level_order = c("Pessimistic",
                "Optimistic",
                "Skeptical",
                "Evidence-based",
                "Non-informative")

samples_posteriors_simple_discharge %>%
  
  ggplot(aes(
    # Multiply by 100 to report in percentage
    x = 100 * RD,
    y = factor(`Underlying_Prior`, level = level_order),
    fill = `Underlying_Prior`)) +
  
  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(aes(fill = stat(x < 0)),
               position = "dodge",
               point_interval = median_hdi, # Highest density interval
               .width = c(0.5, 0.95),
               # https://github.com/mjskay/ggdist/issues/70
               interval_size_range = c(1.1,1.9)
  ) +
  scale_fill_manual(values = c("gray85", "#64A37E")) +
  labs(x = "\nRisk Difference (%)",
       y = "Underlying Prior\n"
  ) +
  scale_x_continuous(breaks = seq(from = -12.5, to = 10, 2.5)) +
  scale_y_discrete(expand = c(0, 0.3)) +
  theme(axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 13.5),
        axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 12),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_blank(),
        panel.grid.major.x = element_line(color = "gray80", size = 0.3),
        legend.position = "none",
        plot.title.position = 'plot',
        plot.margin = margin(20, 25, 10, 20)
  ) +
  coord_cartesian(xlim = c(-12.5, 10))

# ggsave(width = 7,
#        height = 4.5,
#         here("final_analyses", "output", "plots", "appendix", # File path
#                   "SFigure18_discharge_posteriors_simple.pdf")) # File name
```

<br><br>
  

```{r}

t = tibble(
  
  "Underlying Prior" = c(
    "Non-informative",
    "Evidence-based",
    "Skeptical",
    "Optimistic",
    "Pessimistic"
  ),
  
  
  "Pr(< -5%)" = c(round((samples_posteriors_simple_discharge %>%
                           filter(`Underlying_Prior` == "Non-informative") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_simple_discharge %>%
                           filter(`Underlying_Prior` == "Evidence-based") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_simple_discharge %>%
                           filter(`Underlying_Prior` == "Skeptical") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_simple_discharge %>%
                           filter(`Underlying_Prior` == "Optimistic") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_simple_discharge %>%
                           filter(`Underlying_Prior` == "Pessimistic") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100
  ),
  
  "Pr(< -2%)" = c(round((samples_posteriors_simple_discharge %>%
                           filter(`Underlying_Prior` == "Non-informative") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_simple_discharge %>%
                           filter(`Underlying_Prior` == "Evidence-based") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_simple_discharge %>%
                           filter(`Underlying_Prior` == "Skeptical") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_simple_discharge %>%
                           filter(`Underlying_Prior` == "Optimistic") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_simple_discharge %>%
                           filter(`Underlying_Prior` == "Pessimistic") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100
  ),
  
  "Pr(< -1%)" = c(round((samples_posteriors_simple_discharge %>%
                           filter(`Underlying_Prior` == "Non-informative") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_simple_discharge %>%
                           filter(`Underlying_Prior` == "Evidence-based") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_simple_discharge %>%
                           filter(`Underlying_Prior` == "Skeptical") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_simple_discharge %>%
                           filter(`Underlying_Prior` == "Optimistic") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_simple_discharge %>%
                           filter(`Underlying_Prior` == "Pessimistic") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100
  ),
  
  
  "Pr(< 0%)" = c(round((samples_posteriors_simple_discharge %>%
                          filter(`Underlying_Prior` == "Non-informative") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_simple_discharge %>%
                          filter(`Underlying_Prior` == "Evidence-based") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_simple_discharge %>%
                          filter(`Underlying_Prior` == "Skeptical") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_simple_discharge %>%
                          filter(`Underlying_Prior` == "Optimistic") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_simple_discharge %>%
                          filter(`Underlying_Prior` == "Pessimistic") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100
  ),
  
  "Pr(> 1%)" = c(round((samples_posteriors_simple_discharge %>%
                          filter(`Underlying_Prior` == "Non-informative") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_simple_discharge %>%
                          filter(`Underlying_Prior` == "Evidence-based") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_simple_discharge %>%
                          filter(`Underlying_Prior` == "Skeptical") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_simple_discharge %>%
                          filter(`Underlying_Prior` == "Optimistic") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_simple_discharge %>%
                          filter(`Underlying_Prior` == "Pessimistic") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100
  ),
  
  "Pr(> 2%)" = c(round((samples_posteriors_simple_discharge %>%
                          filter(`Underlying_Prior` == "Non-informative") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_simple_discharge %>%
                          filter(`Underlying_Prior` == "Evidence-based") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_simple_discharge %>%
                          filter(`Underlying_Prior` == "Skeptical") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_simple_discharge %>%
                          filter(`Underlying_Prior` == "Optimistic") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_simple_discharge %>%
                          filter(`Underlying_Prior` == "Pessimistic") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100
  ),
  
  "Pr(> 5%)" = c(round((samples_posteriors_simple_discharge %>%
                          filter(`Underlying_Prior` == "Non-informative") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_simple_discharge %>%
                          filter(`Underlying_Prior` == "Evidence-based") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_simple_discharge %>%
                          filter(`Underlying_Prior` == "Skeptical") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_simple_discharge %>%
                          filter(`Underlying_Prior` == "Optimistic") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_simple_discharge %>%
                          filter(`Underlying_Prior` == "Pessimistic") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100
  )
) 

t1 = t %>% 
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1,
                     "Probability of Benefit" = 4,
                     "Probability of Harm" = 3))

t1

# t1 %>% 
#   save_kable(here("final_analyses", "output", "plots", "appendix", # File path
#                   "STable16_discharge_probabilities_simple.pdf")) # File name
```

##### HDI for each posterior distribution

Here are the 95% HDI in *risk difference* of each distribution.

```{r}
multiply100 = function(x){x*100}

samples_posteriors_simple_discharge %>%
  select("Underlying_Prior", "RD") %>% 
  # Group by distribution so we can apply median_hdi
  group_by(`Underlying_Prior`) %>% 
  # Calculate the median and 95% quantile interval in log-odds ratio
  ggdist::median_hdi(.width = 0.95) %>% 
  # Select only the relevant columns
  # Arrange order
  arrange(factor(`Underlying_Prior`, levels = c(
    "Non-informative",
    "Evidence-based",
    "Skeptical",
    "Optimistic",
    "Pessimistic"
    ))) %>% 
  select("Underlying_Prior":.upper) %>%
  mutate(across(RD:.upper, ~multiply100(.))) %>%
  mutate(across(RD:.upper, ~round(., 2))) %>%
  rename("Underlying Prior" = Underlying_Prior,
         "Median" = RD,
         "Upper limit" = .upper,
         "Lower limit" = .lower) %>% 
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1,
                     "95% Highest Density Interval" = 3))
```

### Non-invasive ventilation

#### Prior and likelihood distributions

```{r}

distributions =
  tibble(
    
    "RECOVERY (likelihood)" = list(
      rnorm(
        10e4,
        mean = (posteriors_noninvasive_discharge %>%
                  # Data.mean and data.sd are all the same in every row
                  # So it doesn't matter what row I slice
                  slice(1) %>% 
                  pull(data.mean)),
        sd = (posteriors_noninvasive_discharge %>%
                slice(1) %>% 
                pull(data.sd))
      )),
    
    "Non-informative prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_noninvasive_discharge %>%
                  filter(type == "non-informative") %>%
                  pull(prior.mean)),
        sd = (posteriors_noninvasive_discharge %>%
                filter(type == "non-informative") %>%
                pull(prior.sd))
      )),
    
    "Evidence-based prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_noninvasive_discharge %>%
                  filter(type == "evidence-based") %>%
                  pull(prior.mean)),
        sd = (posteriors_noninvasive_discharge %>%
                filter(type == "evidence-based") %>%
                pull(prior.sd))
      )),
    
    "Skeptical prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_noninvasive_discharge %>%
                  filter(type == "skeptical") %>%
                  pull(prior.mean)),
        sd = (posteriors_noninvasive_discharge %>%
                filter(type == "skeptical") %>%
                pull(prior.sd))
      )),
    
    "Optimistic prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_noninvasive_discharge %>%
                  filter(type == "optimistic") %>%
                  pull(prior.mean)),
        sd = (posteriors_noninvasive_discharge %>%
                filter(type == "optimistic") %>%
                pull(prior.sd))
      )),
    
    "Pessimistic prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_noninvasive_discharge %>%
                  filter(type == "pessimistic") %>%
                  pull(prior.mean)),
        sd = (posteriors_noninvasive_discharge %>%
                filter(type == "pessimistic") %>%
                pull(prior.sd))
      ))
  ) %>% 
  unnest(everything())


```


```{r, fig.height=5.5, fig.width = 5.5, fig.align='center'}

# Plot!

distributions %>%
  # make it tidy for ggplot
  pivot_longer(
    cols = c(everything()),
    names_to = "dist", values_to = "samples"
  ) %>%
  # Set order of priors
  mutate(dist = factor(dist, levels =
                         c("RECOVERY (likelihood)",
                           "Non-informative prior",
                           "Evidence-based prior",
                           "Skeptical prior",
                           "Optimistic prior",
                           "Pessimistic prior")
  )
  ) %>%
  # exp() to transform log(OR) to OR
  ggplot(aes(
    x = exp(samples), y = dist,
    fill = dist
  )) +
  
  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(position = "dodge",
               point_interval = median_qi, # Quantile interval 
               .width = c(0.95)) +
  geom_vline(xintercept = 1, linetype = 2, size = 0.6) +
  scale_fill_manual(' ',
                    values = c(
                      carto_pal(12, "Pastel")[1], # RECOVERY
                      carto_pal(12, "Pastel")[12], # Non-informative,
                      carto_pal(12, "Pastel")[2], # Evidence-based
                      "gray70", # Skeptical
                      carto_pal(12, "Pastel")[5], # Optimistic
                      carto_pal(12, "Pastel")[10]  # Pessimistc
                    )) +
  labs(
    x = "\nOdds Ratio",
    y = " "
  ) +
  scale_x_continuous(breaks = seq(from = 0, to = 3, 0.5)) +
  scale_y_discrete(expand = c(0, 0.5)) +
  theme(
    strip.background = element_rect(fill = "#E4E6E7"),
    strip.text.x = element_text(size = 12),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    legend.position = 'none',
    legend.text = element_text(size=12),
    legend.key= element_blank(),
    plot.margin = margin(20, 20, 20, 20)
  ) +
  coord_cartesian(x = c(0, 3)) +
  facet_wrap(~dist, ncol = 1, scales = "free_y")

```

#### Posterior distributions

```{r, , fig.align='center', fig.width=7, fig.height = 4.5, fig.cap="Point estimates depict the median. Interval bars depict the 50 and 95% highest density intervals."}

level_order = c("Pessimistic",
                "Optimistic",
                "Skeptical",
                "Evidence-based",
                "Non-informative")

samples_posteriors_noninvasive_discharge %>%
  
  ggplot(aes(
    # Multiply by 100 to report in percentage
    x = 100 * RD,
    y = factor(`Underlying_Prior`, level = level_order),
    fill = `Underlying_Prior`)) +
  
  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(aes(fill = stat(x < 0)),
               position = "dodge",
               point_interval = median_hdi, # Highest density interval
               .width = c(0.5, 0.95),
               # https://github.com/mjskay/ggdist/issues/70
               interval_size_range = c(1.1,1.9)
  ) +
  scale_fill_manual(values = c("gray85", "#64A37E")) +
  labs(x = "\nRisk Difference (%)",
       y = "Underlying Prior\n"
  ) +
  scale_x_continuous(breaks = seq(from = -12.5, to = 10, 2.5)) +
  scale_y_discrete(expand = c(0, 0.3)) +
  theme(axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 13.5),
        axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 12),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_blank(),
        panel.grid.major.x = element_line(color = "gray80", size = 0.3),
        legend.position = "none",
        plot.title.position = 'plot',
        plot.margin = margin(20, 25, 10, 20)
  ) +
  coord_cartesian(xlim = c(-12.5, 10))

# ggsave(width = 7,
#        height = 4.5,
#         here("final_analyses", "output", "plots", "appendix", # File path
#                   "SFigure19_discharge_posteriors_noninvasive.pdf")) # File name
```

<br><br>
  
  
```{r}

t = tibble(
  
  "Underlying Prior" = c(
    "Non-informative",
    "Evidence-based",
    "Skeptical",
    "Optimistic",
    "Pessimistic"
  ),
  
  
  "Pr(< -5%)" = c(round((samples_posteriors_noninvasive_discharge %>%
                           filter(`Underlying_Prior` == "Non-informative") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_noninvasive_discharge %>%
                           filter(`Underlying_Prior` == "Evidence-based") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_noninvasive_discharge %>%
                           filter(`Underlying_Prior` == "Skeptical") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_noninvasive_discharge %>%
                           filter(`Underlying_Prior` == "Optimistic") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_noninvasive_discharge %>%
                           filter(`Underlying_Prior` == "Pessimistic") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100
  ),
  
  "Pr(< -2%)" = c(round((samples_posteriors_noninvasive_discharge %>%
                           filter(`Underlying_Prior` == "Non-informative") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_noninvasive_discharge %>%
                           filter(`Underlying_Prior` == "Evidence-based") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_noninvasive_discharge %>%
                           filter(`Underlying_Prior` == "Skeptical") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_noninvasive_discharge %>%
                           filter(`Underlying_Prior` == "Optimistic") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_noninvasive_discharge %>%
                           filter(`Underlying_Prior` == "Pessimistic") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100
  ),
  
  "Pr(< -1%)" = c(round((samples_posteriors_noninvasive_discharge %>%
                           filter(`Underlying_Prior` == "Non-informative") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_noninvasive_discharge %>%
                           filter(`Underlying_Prior` == "Evidence-based") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_noninvasive_discharge %>%
                           filter(`Underlying_Prior` == "Skeptical") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_noninvasive_discharge %>%
                           filter(`Underlying_Prior` == "Optimistic") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_noninvasive_discharge %>%
                           filter(`Underlying_Prior` == "Pessimistic") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100
  ),
  
  
  "Pr(< 0%)" = c(round((samples_posteriors_noninvasive_discharge %>%
                          filter(`Underlying_Prior` == "Non-informative") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_noninvasive_discharge %>%
                          filter(`Underlying_Prior` == "Evidence-based") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_noninvasive_discharge %>%
                          filter(`Underlying_Prior` == "Skeptical") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_noninvasive_discharge %>%
                          filter(`Underlying_Prior` == "Optimistic") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_noninvasive_discharge %>%
                          filter(`Underlying_Prior` == "Pessimistic") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100
  ),
  
  "Pr(> 1%)" = c(round((samples_posteriors_noninvasive_discharge %>%
                          filter(`Underlying_Prior` == "Non-informative") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_noninvasive_discharge %>%
                          filter(`Underlying_Prior` == "Evidence-based") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_noninvasive_discharge %>%
                          filter(`Underlying_Prior` == "Skeptical") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_noninvasive_discharge %>%
                          filter(`Underlying_Prior` == "Optimistic") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_noninvasive_discharge %>%
                          filter(`Underlying_Prior` == "Pessimistic") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100
  ),
  
  "Pr(> 2%)" = c(round((samples_posteriors_noninvasive_discharge %>%
                          filter(`Underlying_Prior` == "Non-informative") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_noninvasive_discharge %>%
                          filter(`Underlying_Prior` == "Evidence-based") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_noninvasive_discharge %>%
                          filter(`Underlying_Prior` == "Skeptical") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_noninvasive_discharge %>%
                          filter(`Underlying_Prior` == "Optimistic") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_noninvasive_discharge %>%
                          filter(`Underlying_Prior` == "Pessimistic") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100
  ),
  
  "Pr(> 5%)" = c(round((samples_posteriors_noninvasive_discharge %>%
                          filter(`Underlying_Prior` == "Non-informative") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_noninvasive_discharge %>%
                          filter(`Underlying_Prior` == "Evidence-based") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_noninvasive_discharge %>%
                          filter(`Underlying_Prior` == "Skeptical") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_noninvasive_discharge %>%
                          filter(`Underlying_Prior` == "Optimistic") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_noninvasive_discharge %>%
                          filter(`Underlying_Prior` == "Pessimistic") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100
  )
) 

t1 = t %>% 
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1,
                     "Probability of Benefit" = 4,
                     "Probability of Harm" = 3))

t1

# t1 %>% 
#   save_kable(here("final_analyses", "output", "plots", "appendix", # File path
#                   "STable17_discharge_probabilities_noninvasive.pdf")) # File name
```

##### HDI for each posterior distribution

Here are the 95% HDI in *risk difference* of each distribution.

```{r}
multiply100 = function(x){x*100}

samples_posteriors_noninvasive_discharge %>%
  select("Underlying_Prior", "RD") %>% 
  # Group by distribution so we can apply median_hdi
  group_by(`Underlying_Prior`) %>% 
  # Calculate the median and 95% quantile interval in log-odds ratio
  ggdist::median_hdi(.width = 0.95) %>% 
  # Select only the relevant columns
  # Arrange order
  arrange(factor(`Underlying_Prior`, levels = c(
    "Non-informative",
    "Evidence-based",
    "Skeptical",
    "Optimistic",
    "Pessimistic"
    ))) %>% 
  select("Underlying_Prior":.upper) %>%
  mutate(across(RD:.upper, ~multiply100(.))) %>%
  mutate(across(RD:.upper, ~round(., 2))) %>%
  rename("Underlying Prior" = Underlying_Prior,
         "Median" = RD,
         "Upper limit" = .upper,
         "Lower limit" = .lower) %>% 
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1,
                     "95% Highest Density Interval" = 3))
```

### Invasive mechanical ventilation

#### Prior and likelihood distributions

```{r}

distributions =
  tibble(
    
    "RECOVERY (likelihood)" = list(
      rnorm(
        10e4,
        mean = (posteriors_invasive_discharge %>%
                  # Data.mean and data.sd are all the same in every row
                  # So it doesn't matter what row I slice
                  slice(1) %>% 
                  pull(data.mean)),
        sd = (posteriors_invasive_discharge %>%
                slice(1) %>% 
                pull(data.sd))
      )),
    
    "Non-informative prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_invasive_discharge %>%
                  filter(type == "non-informative") %>%
                  pull(prior.mean)),
        sd = (posteriors_invasive_discharge %>%
                filter(type == "non-informative") %>%
                pull(prior.sd))
      )),
    
    "Evidence-based prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_invasive_discharge %>%
                  filter(type == "evidence-based") %>%
                  pull(prior.mean)),
        sd = (posteriors_invasive_discharge %>%
                filter(type == "evidence-based") %>%
                pull(prior.sd))
      )),
    
    "Skeptical prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_invasive_discharge %>%
                  filter(type == "skeptical") %>%
                  pull(prior.mean)),
        sd = (posteriors_invasive_discharge %>%
                filter(type == "skeptical") %>%
                pull(prior.sd))
      )),
    
    "Optimistic prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_invasive_discharge %>%
                  filter(type == "optimistic") %>%
                  pull(prior.mean)),
        sd = (posteriors_invasive_discharge %>%
                filter(type == "optimistic") %>%
                pull(prior.sd))
      )),
    
    "Pessimistic prior" = list(
      rnorm(
        10e4,
        mean = (posteriors_invasive_discharge %>%
                  filter(type == "pessimistic") %>%
                  pull(prior.mean)),
        sd = (posteriors_invasive_discharge %>%
                filter(type == "pessimistic") %>%
                pull(prior.sd))
      ))
  ) %>% 
  unnest(everything())


```


```{r, fig.height=5.5, fig.width = 5.5, fig.align='center'}

# Plot!

distributions %>%
  # make it tidy for ggplot
  pivot_longer(
    cols = c(everything()),
    names_to = "dist", values_to = "samples"
  ) %>%
  # Set order of priors
  mutate(dist = factor(dist, levels =
                         c("RECOVERY (likelihood)",
                           "Non-informative prior",
                           "Evidence-based prior",
                           "Skeptical prior",
                           "Optimistic prior",
                           "Pessimistic prior")
  )
  ) %>%
  # exp() to transform log(OR) to OR
  ggplot(aes(
    x = exp(samples), y = dist,
    fill = dist
  )) +
  
  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(position = "dodge",
               point_interval = median_qi, # Quantile interval 
               .width = c(0.95)) +
  geom_vline(xintercept = 1, linetype = 2, size = 0.6) +
  scale_fill_manual(' ',
                    values = c(
                      carto_pal(12, "Pastel")[1], # RECOVERY
                      carto_pal(12, "Pastel")[12], # Non-informative,
                      carto_pal(12, "Pastel")[2], # Evidence-based
                      "gray70", # Skeptical
                      carto_pal(12, "Pastel")[5], # Optimistic
                      carto_pal(12, "Pastel")[10]  # Pessimistc
                    )) +
  labs(
    x = "\nOdds Ratio",
    y = " "
  ) +
  scale_x_continuous(breaks = seq(from = 0, to = 3, 0.5)) +
  scale_y_discrete(expand = c(0, 0.5)) +
  theme(
    strip.background = element_rect(fill = "#E4E6E7"),
    strip.text.x = element_text(size = 12),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", size = 0.3),
    legend.position = 'none',
    legend.text = element_text(size=12),
    legend.key= element_blank(),
    plot.margin = margin(20, 20, 20, 20)
  ) +
  coord_cartesian(x = c(0, 3)) +
  facet_wrap(~dist, ncol = 1, scales = "free_y")

```

#### Posterior distributions

```{r, , fig.align='center', fig.width=7, fig.height = 4.5, fig.cap="Point estimates depict the median. Interval bars depict the 50 and 95% highest density intervals."}

level_order = c("Pessimistic",
                "Optimistic",
                "Skeptical",
                "Evidence-based",
                "Non-informative")

samples_posteriors_invasive_discharge %>%
  
  ggplot(aes(
    # Multiply by 100 to report in percentage
    x = 100 * RD,
    y = factor(`Underlying_Prior`, level = level_order),
    fill = `Underlying_Prior`)) +
  
  # https://mjskay.github.io/ggdist/articles/slabinterval.html
  stat_halfeye(aes(fill = stat(x < 0)),
               position = "dodge",
               point_interval = median_hdi, # Highest density interval
               .width = c(0.5, 0.95),
               # https://github.com/mjskay/ggdist/issues/70
               interval_size_range = c(1.1,1.9)
  ) +
  scale_fill_manual(values = c("gray85", "#64A37E")) +
  labs(x = "\nRisk Difference (%)",
       y = "Underlying Prior\n"
  ) +
  scale_x_continuous(breaks = seq(from = -12.5, to = 10, 2.5)) +
  scale_y_discrete(expand = c(0, 0.3)) +
  theme(axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 13.5),
        axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 12),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_blank(),
        panel.grid.major.x = element_line(color = "gray80", size = 0.3),
        legend.position = "none",
        plot.title.position = 'plot',
        plot.margin = margin(20, 25, 10, 20)
  ) +
  coord_cartesian(xlim = c(-12.5, 10))

# ggsave(width = 7,
#        height = 4.5,
#         here("final_analyses", "output", "plots", "appendix", # File path
#                   "SFigure20_discharge_posteriors_invasive.pdf")) # File name
```

<br><br>
  
  
```{r}

t = tibble(
  
  "Underlying Prior" = c(
    "Non-informative",
    "Evidence-based",
    "Skeptical",
    "Optimistic",
    "Pessimistic"
  ),
  
  
  "Pr(< -5%)" = c(round((samples_posteriors_invasive_discharge %>%
                           filter(`Underlying_Prior` == "Non-informative") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_invasive_discharge %>%
                           filter(`Underlying_Prior` == "Evidence-based") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_invasive_discharge %>%
                           filter(`Underlying_Prior` == "Skeptical") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_invasive_discharge %>%
                           filter(`Underlying_Prior` == "Optimistic") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_invasive_discharge %>%
                           filter(`Underlying_Prior` == "Pessimistic") %>%
                           summarise(n = sum(RD < -0.05) / n()) %>%
                           pull()), 2) * 100
  ),
  
  "Pr(< -2%)" = c(round((samples_posteriors_invasive_discharge %>%
                           filter(`Underlying_Prior` == "Non-informative") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_invasive_discharge %>%
                           filter(`Underlying_Prior` == "Evidence-based") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_invasive_discharge %>%
                           filter(`Underlying_Prior` == "Skeptical") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_invasive_discharge %>%
                           filter(`Underlying_Prior` == "Optimistic") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_invasive_discharge %>%
                           filter(`Underlying_Prior` == "Pessimistic") %>%
                           summarise(n = sum(RD < -0.02) / n()) %>%
                           pull()), 2) * 100
  ),
  
  "Pr(< -1%)" = c(round((samples_posteriors_invasive_discharge %>%
                           filter(`Underlying_Prior` == "Non-informative") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_invasive_discharge %>%
                           filter(`Underlying_Prior` == "Evidence-based") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_invasive_discharge %>%
                           filter(`Underlying_Prior` == "Skeptical") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_invasive_discharge %>%
                           filter(`Underlying_Prior` == "Optimistic") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100,
                  
                  round((samples_posteriors_invasive_discharge %>%
                           filter(`Underlying_Prior` == "Pessimistic") %>%
                           summarise(n = sum(RD < -0.01) / n()) %>%
                           pull()), 2) * 100
  ),
  
  
  "Pr(< 0%)" = c(round((samples_posteriors_invasive_discharge %>%
                          filter(`Underlying_Prior` == "Non-informative") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_invasive_discharge %>%
                          filter(`Underlying_Prior` == "Evidence-based") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_invasive_discharge %>%
                          filter(`Underlying_Prior` == "Skeptical") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_invasive_discharge %>%
                          filter(`Underlying_Prior` == "Optimistic") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_invasive_discharge %>%
                          filter(`Underlying_Prior` == "Pessimistic") %>%
                          summarise(n = sum(RD < 0) / n()) %>%
                          pull()), 2) * 100
  ),
  
  "Pr(> 1%)" = c(round((samples_posteriors_invasive_discharge %>%
                          filter(`Underlying_Prior` == "Non-informative") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_invasive_discharge %>%
                          filter(`Underlying_Prior` == "Evidence-based") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_invasive_discharge %>%
                          filter(`Underlying_Prior` == "Skeptical") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_invasive_discharge %>%
                          filter(`Underlying_Prior` == "Optimistic") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_invasive_discharge %>%
                          filter(`Underlying_Prior` == "Pessimistic") %>%
                          summarise(n = sum(RD > 0.01) / n()) %>%
                          pull()), 2) * 100
  ),
  
  "Pr(> 2%)" = c(round((samples_posteriors_invasive_discharge %>%
                          filter(`Underlying_Prior` == "Non-informative") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_invasive_discharge %>%
                          filter(`Underlying_Prior` == "Evidence-based") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_invasive_discharge %>%
                          filter(`Underlying_Prior` == "Skeptical") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_invasive_discharge %>%
                          filter(`Underlying_Prior` == "Optimistic") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_invasive_discharge %>%
                          filter(`Underlying_Prior` == "Pessimistic") %>%
                          summarise(n = sum(RD > 0.02) / n()) %>%
                          pull()), 2) * 100
  ),
  
  "Pr(> 5%)" = c(round((samples_posteriors_invasive_discharge %>%
                          filter(`Underlying_Prior` == "Non-informative") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_invasive_discharge %>%
                          filter(`Underlying_Prior` == "Evidence-based") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_invasive_discharge %>%
                          filter(`Underlying_Prior` == "Skeptical") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_invasive_discharge %>%
                          filter(`Underlying_Prior` == "Optimistic") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100,
                 
                 round((samples_posteriors_invasive_discharge %>%
                          filter(`Underlying_Prior` == "Pessimistic") %>%
                          summarise(n = sum(RD > 0.05) / n()) %>%
                          pull()), 2) * 100
  )
) 

t1 = t %>% 
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1,
                     "Probability of Benefit" = 4,
                     "Probability of Harm" = 3))

t1

# t1 %>% 
#   save_kable(here("final_analyses", "output", "plots", "appendix", # File path
#                   "STable18_discharge_probabilities_invasive.pdf")) # File name
```

##### HDI for each posterior distribution

Here are the 95% HDI in *risk difference* of each distribution.

```{r}
multiply100 = function(x){x*100}

samples_posteriors_invasive_discharge %>%
  select("Underlying_Prior", "RD") %>% 
  # Group by distribution so we can apply median_hdi
  group_by(`Underlying_Prior`) %>% 
  # Calculate the median and 95% quantile interval in log-odds ratio
  ggdist::median_hdi(.width = 0.95) %>% 
  # Select only the relevant columns
  # Arrange order
  arrange(factor(`Underlying_Prior`, levels = c(
    "Non-informative",
    "Evidence-based",
    "Skeptical",
    "Optimistic",
    "Pessimistic"
    ))) %>% 
  select("Underlying_Prior":.upper) %>%
  mutate(across(RD:.upper, ~multiply100(.))) %>%
  mutate(across(RD:.upper, ~round(., 2))) %>%
  rename("Underlying Prior" = Underlying_Prior,
         "Median" = RD,
         "Upper limit" = .upper,
         "Lower limit" = .lower) %>% 
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1,
                     "95% Highest Density Interval" = 3))
```

```{r}
sessionInfo()
```

