---
title: "07_Hospital_Discharge_Varying_Baseline_Risk"
author: "Arthur M. Albuquerque"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
          code_folding: hide
          toc: yes
          toc_float: yes
---

If you are interested in the code, you can select the "Show all code" option
on the upper-right corner.

In this document, we will show sensitivity analyses on the hospital discharge
outcome. We will re-calculate the posterior distribution in risk difference while
varying the baseline risk. Please check this document regarding the mortality
outcome for further explanation.

**Of note, for the hospital discharge outcome, negative risk differences mean benefit.**

```{r setup, include=FALSE}
knitr::opts_chunk$set()
```

```{r include=FALSE}
# Ensures the package "pacman" is installed
if (!require("pacman")) install.packages("pacman")

# p_load() installs (if necessary) and loads the following packages

pacman::p_load(rio, # To import data
               here, # To find file paths within R project
               janitor, # To change column names
               tidyverse, # Data wrangling and plotting
               flextable, # For tables
               patchwork, # To arrange plots
               kableExtra, # To make tables
               ggdist, # To plot distributions
               Cairo, # To export PDF files
               tidytable, # To work with data frames + tidyverse synthax (fast)
               PNWColors # Color palettes
               )
```


```{r}

## Load posterior distributions' samples with logOR, OR and RD

# I uploaded these data objects to OSF since the .RData file is 54MB.
# Here I load all data files directly from OSF without having to download it
# to my/your PC

samples = url("https://osf.io/7t32f/download?version=1")
load(gzcon(samples))


# Load original data extraction table

d1 = import((here("final_analyses", "output", "data", # file path
                                "respiratory-data.csv")),           # file name
                          header = T)
d1 = d1 %>% 
  as_tibble() %>% 
  select(!starts_with("X")) 

# Load corticosteroids raw data

d2 = import(here("final_analyses", "data", # file path
                            "corticosteroids_subgroup_extracted-data.xlsx"))

d2 = clean_names(d2)

```

```{r}

# Adapted function version to be able to apply it in the code chunk below
RD_fun_mod = function(x) {
  z = ( BR*(BR-1)*(x$OR-1) ) / ( BR*x$OR - BR+1)
  z
}

```

```{r}
##### BE AWARE THESE ARE A LOT OF CALCULATIONS AND IT MIGHT TAKE SOME TIME
# I suppressed this code chunk after I ran it for the first time and
# saved the outputs. Feel free to run it.

# I will first assign the original fixed baseline risk
# Then, I will use this baseline risk as a reference to create a range -20/+20%
# Lastly, I will apply the function above to create a new data frame with
# separate columns for risk differences, one from each of these baseline risk.
# These new columns will be named "RD_'baseline risk used'", for example:
# RD_0.30, RD_0.31... etc


# I asked for help to the R4DS Online Learning Community on Slack
# Thus, who solved the script in this code chunk was ARNAB PANJA (thank you)

# Let's do this cycle of calculations for each of the subgroups

#  ### Use of corticosteroids

# Not using
  
#   original_fixed_BR =  d2 %>% 
#       filter(trial == "RECOVERY",
#              corticosteroids == 0, # Not using
#              outcome == "discharge") %>% 
#         summarise(n = events_control/total_control) %>%
#         pull()
#   
#   # Range from ~20% below and ~20% above the original fixed Baseline Risk (BR)
#   lower_range = round(original_fixed_BR - 0.2, 2)
#   upper_range = round(original_fixed_BR + 0.2,2)
#   
#   # Vector with multiples BRs
#   BR = seq(lower_range, upper_range, 0.01)
#   
#   # Select only the OR column from the original tibble and transform into DF
#   d = samples_posteriors_not_using_discharge %>% select(OR) %>% as.data.frame()
#   
#   # Run the function (lots of calculations)
#   dBR = plyr::adply(.data = d, 
#               .margins = 1, 
#               .fun = function(x) RD_fun_mod(x)) %>% 
#     setNames(c(colnames(d)[1], paste0("RD_", BR)))
#   
#   # Get the "Underlying_Prior" and "log(OR)" columns back again and bind with dBR
#   multiple_baseline_risks_not_using_discharge = 
#     bind_cols(samples_posteriors_not_using_discharge[1:2] %>% as.data.frame(),
#               dBR)
#   
#   # Using
#     
#   original_fixed_BR =  d2 %>% 
#       filter(trial == "RECOVERY",
#              corticosteroids == 1, # Using
#              outcome == "discharge") %>% 
#         summarise(n = events_control/total_control) %>%
#         pull()
#   
#   # Range from ~20% below and ~20% above the original fixed Baseline Risk (BR)
#   lower_range = round(original_fixed_BR - 0.2, 2)
#   upper_range = round(original_fixed_BR + 0.2,2)
#   
#   # Vector with multiples BRs
#   BR = seq(lower_range, upper_range, 0.01)
#   
#   # Select only the OR column from the original tibble and transform into DF
#   d = samples_posteriors_using_discharge %>% select(OR) %>% as.data.frame()
#   
#   # Run the function (lots of calculations)
#   dBR = plyr::adply(.data = d, 
#               .margins = 1, 
#               .fun = function(x) RD_fun_mod(x)) %>% 
#     setNames(c(colnames(d)[1], paste0("RD_", BR)))
#   
#   # Get the "Underlying_Prior" and "log(OR)" columns back again and bind with dBR
#   multiple_baseline_risks_using_discharge = 
#     bind_cols(samples_posteriors_using_discharge[1:2] %>% as.data.frame(),
#               dBR)
#   
#   ## Respiratory support
#   
#   # Simple oxygen only
#   
#   original_fixed_BR = d1 %>% 
#     filter(trial == "RECOVERY",
#            oxygen == "simple oxygen",
#            outcome == "discharge") %>% 
#     summarise(n = events_control/total_control) %>%
#     pull()
#   
#   # Range from ~20% below and ~20% above the original fixed Baseline Risk (BR)
#   lower_range = round(original_fixed_BR - 0.2, 2)
#   upper_range = round(original_fixed_BR + 0.2,2)
#   
#   # Vector with multiples BRs
#   BR = seq(lower_range, upper_range, 0.01)
#   
#   # Select only the OR column from the original tibble and transform into DF
#   d = samples_posteriors_simple_discharge %>% select(OR) %>% as.data.frame()
#   
#   # Run the function (lots of calculations)
#   dBR = plyr::adply(.data = d, 
#               .margins = 1, 
#               .fun = function(x) RD_fun_mod(x)) %>% 
#     setNames(c(colnames(d)[1], paste0("RD_", BR)))
#   
#   # Get the "Underlying_Prior" and "log(OR)" columns back again and bind with dBR
#   multiple_baseline_risks_simple_discharge = 
#     bind_cols(samples_posteriors_simple_discharge[1:2] %>% as.data.frame(),
#               dBR)
#   
#   # Non-invasive ventilation
#   
#   original_fixed_BR = d1 %>% 
#     filter(trial == "RECOVERY",
#            oxygen == "non-invasive ventilation",
#            outcome == "discharge") %>% 
#     summarise(n = events_control/total_control) %>%
#     pull()
#   
#   # Range from ~20% below and ~20% above the original fixed Baseline Risk (BR)
#   lower_range = round(original_fixed_BR - 0.2, 2)
#   upper_range = round(original_fixed_BR + 0.2,2)
#   
#   # Vector with multiples BRs
#   BR = seq(lower_range, upper_range, 0.01)
#   
#   # Select only the OR column from the original tibble and transform into DF
#   d = samples_posteriors_noninvasive_discharge %>% select(OR) %>% as.data.frame()
#   
#   # Run the function (lots of calculations)
#   dBR = plyr::adply(.data = d, 
#               .margins = 1, 
#               .fun = function(x) RD_fun_mod(x)) %>% 
#     setNames(c(colnames(d)[1], paste0("RD_", BR)))
#   
#   # Get the "Underlying_Prior" and "log(OR)" columns back again and bind with dBR
#   multiple_baseline_risks_noninvasive_discharge = 
#     bind_cols(samples_posteriors_noninvasive_discharge[1:2] %>% as.data.frame(),
#               dBR)
#   
#   # Invasive mechanical ventilation
#   
#   original_fixed_BR = d1 %>% 
#     filter(trial == "RECOVERY",
#            oxygen == "invasive ventilation",
#            outcome == "discharge") %>% 
#     summarise(n = events_control/total_control) %>%
#     pull()
#   
#   # Range from ~20% below and ~20% above the original fixed Baseline Risk (BR)
#   lower_range = round(original_fixed_BR - 0.2, 2)
#   upper_range = round(original_fixed_BR + 0.2,2)
#   
#   # Vector with multiples BRs
#   BR = seq(lower_range, upper_range, 0.01)
#   
#   # Select only the OR column from the original tibble and transform into DF
#   d = samples_posteriors_invasive_discharge %>% select(OR) %>% as.data.frame()
#   
#   # Run the function (lots of calculations)
#   dBR = plyr::adply(.data = d, 
#               .margins = 1, 
#               .fun = function(x) RD_fun_mod(x)) %>% 
#     setNames(c(colnames(d)[1], paste0("RD_", BR)))
#   
#   # Get the "Underlying_Prior" and "log(OR)" columns back again and bind with dBR
#   multiple_baseline_risks_invasive_discharge = 
#     bind_cols(samples_posteriors_invasive_discharge[1:2] %>% as.data.frame(),
#               dBR)

#  Remove large objects with samples that was loaded in this document and has no
#  use after this code chunk

#  rm(samples_posteriors_not_using_discharge,
#     samples_posteriors_using_discharge,
#     samples_posteriors_simple_discharge,
#     samples_posteriors_noninvasive_discharge,
#     samples_posteriors_invasive_discharge)
```

```{r}
# Code to save the output from above in different files since
# they are huge data frames

# saveRDS(multiple_baseline_risks_not_using_discharge,
#         file = here("final_analyses", "output", "data", "analyses", # file path
#                     "multiple_baseline_risks_not_using_discharge.rds"))
# saveRDS(multiple_baseline_risks_using_discharge,
#         file = here("final_analyses", "output", "data", "analyses", # file path
#                     "multiple_baseline_risks_using_discharge.rds"))
# saveRDS(multiple_baseline_risks_simple_discharge,
#         file = here("final_analyses", "output", "data", "analyses", # file path
#                     "multiple_baseline_risks_simple_discharge.rds"))
# saveRDS(multiple_baseline_risks_noninvasive_discharge,
#         file = here("final_analyses", "output", "data", "analyses", # file path
#                     "multiple_baseline_risks_noninvasive_discharge.rds"))
# saveRDS(multiple_baseline_risks_invasive_discharge,
#         file = here("final_analyses", "output", "data", "analyses", # file path
#                     "multiple_baseline_risks_invasive_discharge.rds"))
```

```{r}
## I uploaded all the .rds files above into OSF
## here is the link for one of them https://osf.io/7t4hm/

## Run this code chunk if you have downloaded the files from OSF into your PC


# Load the files from the code chunks above

# multiple_baseline_risks_not_using_discharge = 
#   readRDS(file = here("final_analyses", "output", # "data", "analyses", # file path
#                     # "multiple_baseline_risks_not_using_discharge.rds"))
# 
# multiple_baseline_risks_using_discharge = 
# readRDS(file = here("final_analyses", "output", "data", # "analyses", # file path
#                     # "multiple_baseline_risks_using_discharge.rds"))
# 
# multiple_baseline_risks_simple_discharge = 
#   readRDS(file = here("final_analyses", "output", # "data", "analyses", # file path
#                     # "multiple_baseline_risks_simple_discharge.rds"))
# 
# multiple_baseline_risks_noninvasive_discharge = 
#   readRDS(file = here("final_analyses", "output", # "data", "analyses", # file path
#                     # "multiple_baseline_risks_noninvasive_discharge.rds"))
# 
# multiple_baseline_risks_invasive_discharge = 
#   readRDS(file = here("final_analyses", "output", # "data", "analyses", # file path
#                     # "multiple_baseline_risks_invasive_discharge.rds"))
```

```{r}
# In case you did not download the files from OSF, run this code chunk 
# Here, you can load the .rds files directly from OSF, without having to
# download it

# I adapted the code from https://osf.io/73thx/ to be able to load files in
# OSF into RStudio without having to download it

# This should take some time, since each file has ~165MB
# If it the loading "times out", try it again, it should work
# If it doesn't work, then download the files from OSF and run the code chunk above

## Use of corticosteroids

# Not using

not_using = url("https://osf.io/vja24/download?version=1")

multiple_baseline_risks_not_using_discharge = readRDS(gzcon(not_using))
```

```{r}
# Using

using = url("https://osf.io/p8nes/download?version=1")

multiple_baseline_risks_using_discharge = readRDS(gzcon(using))
```

```{r}
## Respiratory support

# Simple oxygen only

simple = url("https://osf.io/q25z4/download?version=1")

multiple_baseline_risks_simple_discharge = readRDS(gzcon(simple))

```

```{r}
# Non-invasive ventilation

noninvasive = url("https://osf.io/muxaj/download?version=1")

multiple_baseline_risks_noninvasive_discharge = readRDS(gzcon(noninvasive))
```

```{r}
# Invasive mechanical ventilation

invasive = url("https://osf.io/y8ruc/download?version=1")

multiple_baseline_risks_invasive_discharge = readRDS(gzcon(invasive))
```

## Plotting

For our primary analyses, we used the baseline risks below for each subgroup to
derive the posterior distribution in the risk difference scale.

```{r echo=FALSE}
tibble(
  
  "Subgroup" = c("Not using",
                 "Using",
                 
                 "Simple oxygen only",
                 "Non-invasive ventilation",
                 "Invasive mechanical"
                 ),
  
  "Baseline Risk in Control Group (%)" = c(
    
    d2 %>% 
    filter(trial == "RECOVERY",
           corticosteroids == 0,
           outcome == "discharge") %>% 
      summarise(n = 100*(events_control/total_control)) %>% 
      round(., 1) %>% 
      pull(),
    d2 %>% 
    filter(trial == "RECOVERY",
           corticosteroids == 1,
           outcome == "discharge") %>% 
      summarise(n = 100*(events_control/total_control)) %>% 
      round(., 1) %>% 
      pull(),
    
    d1 %>% 
    filter(trial == "RECOVERY",
           oxygen == "simple oxygen",
           outcome == "discharge") %>% 
      summarise(n = 100*(events_control/total_control)) %>% 
      round(., 1) %>% 
      pull(),
    d1 %>% 
    filter(trial == "RECOVERY",
           oxygen == "non-invasive ventilation",
           outcome == "discharge") %>% 
      summarise(n = 100*(events_control/total_control)) %>% 
      round(., 1) %>% 
      pull(),
    d1 %>% 
    filter(trial == "RECOVERY",
           oxygen == "invasive ventilation",
           outcome == "discharge") %>% 
      summarise(n = 100*(events_control/total_control)) %>% 
      round(., 1) %>% 
      pull()
  )
  
) %>% 
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  pack_rows("Use of corticosteroids", 1, 2) %>% 
  pack_rows("Respiratory support", 3, 5)
```

```{r}
plot_baseline_risks = function(data # Data Object
                               ){
# Note the "." in each function. This is from {tidytable}
t1 = data %>% 
  as.data.frame() %>% 
  filter.(`Underlying_Prior` == "Evidence-based") %>% 
  select.(starts_with("RD")) %>% 
  pivot_longer.(
    cols = everything(),
    names_to = "Baseline_risk", values_to = "Risk_difference"
  ) %>%
  # Isolate the Baseline risk from the string (it takes a long time)
  separate.(Baseline_risk,
           sep = "_",
           c("NA","BR")
  ) %>% 
  select.(!"NA") %>% 
  # as.numeric to be able to multiply by 100
  mutate.(BR = as.numeric(BR)) %>% 
  mutate.(BR = BR*100) %>% 
  # as.character to be able to use stat_pointinterval()
  mutate.(BR = as.character(BR))
  
  # Plot!
  t1 %>% 
  ggplot(aes(x = 100*Risk_difference, y = BR))+
    geom_hline(yintercept = 21, linetype = 2)+
  stat_pointinterval(point_interval = median_hdi, # Highest density interval
                     .width = 0.95) +
  geom_vline(xintercept = 0, linetype = 2, size = 1, color = "firebrick")+
  labs(x = "Risk Difference (%)",
       y = "Baseline Risk (%) \n") +
    
  theme(plot.title.position = 'plot',
      axis.title.x = element_text(size = 12),
      axis.title.y = element_text(size = 12),
      axis.text.y = element_text(size = 12),
      axis.text.x = element_text(size = 10),
      axis.ticks.x = element_blank(),
      axis.ticks.y = element_blank(),
      panel.background = element_blank(),
      panel.grid.major.x = element_line(color = "gray80", size = 0.3),
      panel.grid.major.y = element_line(color = "gray80", size = 0.3)) +
    scale_x_continuous(breaks = seq(-16, 16, 4))+
    coord_cartesian(x = c(-16,16))
  
}
```

Now, let's plot the posterior distributions for all subgroups using 40 different
baseline risks

```{r}
p1 = plot_baseline_risks(multiple_baseline_risks_not_using_discharge) +
  scale_y_discrete(breaks = c(26, 46, 66))
```

```{r}
p2 = plot_baseline_risks(multiple_baseline_risks_using_discharge) +
  labs(y = " ") +
  scale_y_discrete(breaks = c(31, 51, 71))
```

```{r}
p3 = plot_baseline_risks(multiple_baseline_risks_simple_discharge) +
  scale_y_discrete(breaks = c(48, 68, 88))
```

```{r}
p4 = plot_baseline_risks(multiple_baseline_risks_noninvasive_discharge) +
  labs(y = " ") +
  scale_y_discrete(breaks = c(22, 42, 62))
```

```{r}
# Full code in this code chunk because I had to add an extra line to set the order
p5 = multiple_baseline_risks_invasive_discharge %>% 
  as.data.frame() %>% 
  filter.(`Underlying_Prior` == "Evidence-based") %>% 
  select.(starts_with("RD")) %>% 
  pivot_longer.(
    cols = everything(),
    names_to = "Baseline_risk", values_to = "Risk_difference"
  ) %>%
  # Isolate the Baseline risk from the string (it takes a long time)
  separate.(Baseline_risk,
           sep = "_",
           c("NA","BR")
  ) %>% 
  select.(!"NA") %>% 
  # as.numeric to be able to multiply by 100
  mutate.(BR = as.numeric(BR)) %>% 
  mutate.(BR = BR*100) %>% 
  # as.character to be able to use stat_pointinterval()
  mutate.(BR = as.character(BR)) %>% 
  # Set order
  mutate.(BR = factor(BR, levels = seq(1, 36, 1))) %>% 
  filter.(BR != "NA") %>% 
  
  ggplot(aes(x = 100*Risk_difference, y = BR))+
  geom_hline(yintercept = 16, linetype = 2)+
  stat_pointinterval(point_interval = median_hdi, # Highest density interval
                     .width = 0.95) +
  geom_vline(xintercept = 0, linetype = 2, size = 1, color = "firebrick")+
  labs(x = "Risk Difference (%)",
       y =  " ") +
    
  theme(plot.title.position = 'plot',
      axis.title.x = element_text(size = 12),
      axis.title.y = element_text(size = 12),
      axis.text.y = element_text(size = 12),
      axis.text.x = element_text(size = 10),
      axis.ticks.x = element_blank(),
      axis.ticks.y = element_blank(),
      panel.background = element_blank(),
      panel.grid.major.x = element_line(color = "gray80", size = 0.3),
      panel.grid.major.y = element_line(color = "gray80", size = 0.3)) +
    scale_x_continuous(breaks = seq(-16, 16, 4))+
    coord_cartesian(x = c(-16,16))+
  scale_y_discrete(breaks = c(1, 16, 36))
```

```{r, fig.width = 10, fig.height=13}
(p1 + p2) / (p3 + p4 + p5) + plot_annotation(tag_levels = 'A')

# ggsave(width = 10,
#        height = 13,
#        here("final_analyses", "output", "plots", "appendix", # File path
#                   "SFigure7_discharge_varying_baseline_risk_difference.pdf")) # # File name
```

```{r}
# Function to generate tibble with probability of benefit vs. baseline risk

probability_by_baseline_risk = function(data, # "multiple_baseline_risks..." data object
                                         type, # Underlying Prior (within quotes)
                                         all_probs # Tibble output name
) {
  prob1 = data %>%
    # Filter by underlying prior
    filter(`Underlying_Prior` == type) %>%
    # Remove Underlying Prior, log(OR) and OR columns
    select(-(`Underlying_Prior`:OR)) %>%
    # To calculate proportion of values lower than the assigned risk difference
    # This is analogous to the (posterior) probability of benefit, since
    # RD > 0 equals benefit
    mutate(across(everything(), ~ sum(. < 0) / n())) %>%
    # Select just the first row, since all rows are now equal to each other
    slice(1) %>%
    # Transform into long format
    pivot_longer(
      cols = everything(),
      names_to = "Baseline_risk", values_to = "Pr_0"
    ) %>%
    # Isolate the Baseline risk from the string
    separate(Baseline_risk,
      sep = "_",
      c(NA, "Baseline_risk")
    ) %>%
    # Transform this column into "double" for ggplot() later
    mutate(Baseline_risk = as.numeric(Baseline_risk))

  # Now repeat the process several times, just changing the cutoff
  prob2 = data %>%
    filter(`Underlying_Prior` == type) %>%
    select(-(`Underlying_Prior`:OR)) %>%
    mutate(across(everything(), ~ sum(. < -0.01) / n())) %>%
    slice(1) %>%
    pivot_longer(
      cols = everything(),
      names_to = "Baseline_risk", values_to = "Pr_0.01"
    ) %>%
    separate(Baseline_risk,
      sep = "_",
      c(NA, "Baseline_risk")
    ) %>%
    mutate(Baseline_risk = as.numeric(Baseline_risk))

  prob3 = data %>%
    filter(`Underlying_Prior` == type) %>%
    select(-(`Underlying_Prior`:OR)) %>%
    mutate(across(everything(), ~ sum(. < -0.02) / n())) %>%
    slice(1) %>%
    pivot_longer(
      cols = everything(),
      names_to = "Baseline_risk", values_to = "Pr_0.02"
    ) %>%
    separate(Baseline_risk,
      sep = "_",
      c(NA, "Baseline_risk")
    ) %>%
    mutate(Baseline_risk = as.numeric(Baseline_risk))

  prob4 = data %>%
    filter(`Underlying_Prior` == type) %>%
    select(-(`Underlying_Prior`:OR)) %>%
    mutate(across(everything(), ~ sum(. < -0.03) / n())) %>%
    slice(1) %>%
    pivot_longer(
      cols = everything(),
      names_to = "Baseline_risk", values_to = "Pr_0.03"
    ) %>%
    separate(Baseline_risk,
      sep = "_",
      c(NA, "Baseline_risk")
    ) %>%
    mutate(Baseline_risk = as.numeric(Baseline_risk))

  # Join all data frames just adding the columns "Pr_..."
  all_probs = left_join(prob1, prob2)

  all_probs = left_join(all_probs, prob3)

  all_probs = left_join(all_probs, prob4)
}
```

```{r message=FALSE, warning=FALSE}
# Generate tibbles per subgroup

## Use of corticosteroids

# Not using

benefit_not_using_discharge =
  probability_by_baseline_risk(
  multiple_baseline_risks_not_using_discharge, # data object
  "Evidence-based", # Underlying Prior (within quotes)
  benefit_not_using_discharge) # Tibble output name

# Using

benefit_using_discharge =
  probability_by_baseline_risk(
  multiple_baseline_risks_using_discharge, # data object
  "Evidence-based", # Underlying Prior (within quotes)
  benefit_using_discharge) # Tibble output name

## Respiratory support

# Simple oxygen only

benefit_simple_discharge =
  probability_by_baseline_risk(
  multiple_baseline_risks_simple_discharge, # data object
  "Evidence-based", # Underlying Prior (within quotes)
  benefit_simple_discharge) # Tibble output name

# Non-invasive ventilation

benefit_noninvasive_discharge =
  probability_by_baseline_risk(
  multiple_baseline_risks_noninvasive_discharge, # data object
  "Evidence-based", # Underlying Prior (within quotes)
  benefit_noninvasive_discharge) # Tibble output name

# Invasive mechanical ventilation

benefit_invasive_discharge =
  probability_by_baseline_risk(
  multiple_baseline_risks_invasive_discharge, # data object
  "Evidence-based", # Underlying Prior (within quotes)
  benefit_invasive_discharge) # Tibble output name
```

```{r}
# Plot!

p1 = benefit_not_using_discharge %>% 
  # Make it tidy for ggplot
  pivot_longer(
    cols = Pr_0:last_col(),
    names_to = "Risk Difference", values_to = "Probabilities"
  ) %>%
  ggplot(aes(x = 100*Baseline_risk, y = 100*Probabilities))+
  geom_line(aes(color = `Risk Difference`), size = 1.15) +
  
  # https://github.com/jakelawlor/PNWColors#building-palettes
  scale_color_manual(values= pnw_palette(name="Starfish",n=4)) +
  
  # Dashed line corresponding to the fixed baseline risk used in the primary
  # analyses
  geom_vline(xintercept = benefit_not_using_discharge[[21,1]]*100, linetype = 2) +
  scale_x_continuous("Baseline Risk (%)",
                     seq((benefit_not_using_discharge[[1,1]]*100),
                         (benefit_not_using_discharge[[41,1]]*100),
                         5)) +
  scale_y_continuous("Posterior Probability of Benefit (%)\n",
                     seq(0, 100, 10))+
  coord_cartesian(y = c(0, 100)) +
  
  theme(legend.position = 'none',
        plot.title.position = 'plot',
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 11),
        axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 10),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_blank(),
        panel.grid.major.x = element_line(color = "gray80", size = 0.3),
        panel.grid.major.y = element_line(color = "gray80", size = 0.3))
  

p2 = benefit_using_discharge %>%
  rename("<   0%" = Pr_0,
         "< -1%" = Pr_0.01,
         "< -2%" = Pr_0.02,
         "< -3%" = Pr_0.03) %>% 
  # Make it tidy for ggplot
  pivot_longer(
    cols = "<   0%":last_col(),
    names_to = "Risk Difference", values_to = "Probabilities"
  ) %>%
  mutate(`Risk Difference` = factor(`Risk Difference`,
      levels = c(
        "<   0%",
        "< -1%",
        "< -2%",
        "< -3%"
        )
    )) %>% 
  ggplot(aes(x = 100*Baseline_risk, y = 100*Probabilities))+
  geom_line(aes(color = `Risk Difference`), size = 1.15)+
  
  # https://github.com/jakelawlor/PNWColors#building-palettes
  scale_color_manual(values= pnw_palette(name="Starfish",n=4)) +
  
  # Dashed line corresponding to the fixed baseline risk used in the primary
  # analyses
  geom_vline(xintercept = benefit_using_discharge[[21,1]]*100, linetype = 2) +
  scale_x_continuous("Baseline Risk (%)", 
                     seq((benefit_using_discharge[[1,1]]*100),
                         (benefit_using_discharge[[41,1]]*100),
                         5)) +
  scale_y_continuous(" ",
                     seq(0, 100, 10))+
  coord_cartesian(y = c(0, 100)) +
  labs(y = " ") +
  
  theme(legend.key = element_blank(),
        plot.title.position = 'plot',
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 13.5),
        axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 10),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_blank(),
        panel.grid.major.x = element_line(color = "gray80", size = 0.3),
        panel.grid.major.y = element_line(color = "gray80", size = 0.3))

p3 = benefit_simple_discharge %>% 
  # Make it tidy for ggplot
  pivot_longer(
    cols = Pr_0:last_col(),
    names_to = "Risk Difference", values_to = "Probabilities"
  ) %>%
  ggplot(aes(x = 100*Baseline_risk, y = 100*Probabilities))+
  geom_line(aes(color = `Risk Difference`), size = 1.15) +
  
  # https://github.com/jakelawlor/PNWColors#building-palettes
  scale_color_manual(values= pnw_palette(name="Starfish",n=4)) +
  
  # Dashed line corresponding to the fixed baseline risk used in the primary
  # analyses
  geom_vline(xintercept = benefit_simple_discharge[[21,1]]*100, linetype = 2) +
  scale_x_continuous("Baseline Risk (%)",
                     seq((benefit_simple_discharge[[1,1]]*100),
                         (benefit_simple_discharge[[41,1]]*100),
                         8)) +
  scale_y_continuous("Posterior Probability of Benefit (%)\n",
                     seq(0, 100, 10))+
  coord_cartesian(y = c(0,100)) +
  theme(legend.position = 'none') +
  
  theme(legend.position = 'none',
        plot.title.position = 'plot',
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 11),
        axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 10),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_blank(),
        panel.grid.major.x = element_line(color = "gray80", size = 0.3),
        panel.grid.major.y = element_line(color = "gray80", size = 0.3))

p4 = benefit_noninvasive_discharge %>% 
  # Make it tidy for ggplot
  pivot_longer(
    cols = Pr_0:last_col(),
    names_to = "Risk Difference", values_to = "Probabilities"
  ) %>%
  ggplot(aes(x = 100*Baseline_risk, y = 100*Probabilities))+
  geom_line(aes(color = `Risk Difference`), size = 1.15) +
  
  # https://github.com/jakelawlor/PNWColors#building-palettes
  scale_color_manual(values= pnw_palette(name="Starfish",n=4)) +
  
  # Dashed line corresponding to the fixed baseline risk used in the primary
  # analyses
  geom_vline(xintercept = benefit_noninvasive_discharge[[21,1]]*100, linetype = 2) +
  scale_x_continuous("Baseline Risk (%)",
                     seq((benefit_noninvasive_discharge[[1,1]]*100),
                         (benefit_noninvasive_discharge[[41,1]]*100),
                         8)) +
  scale_y_continuous(" ",
                     seq(0, 100, 10))+
  coord_cartesian(y = c(0, 100)) +
  theme(legend.position = 'none') +
  
  theme(legend.position = 'none',
        plot.title.position = 'plot',
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 13.5),
        axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 10),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_blank(),
        panel.grid.major.x = element_line(color = "gray80", size = 0.3),
        panel.grid.major.y = element_line(color = "gray80", size = 0.3))

p5 = benefit_invasive_discharge %>% 
  # Remove negative/zero baseline risks
  slice(6:41) %>% 
  rename("<   0%" = Pr_0,
         "< -1%" = Pr_0.01,
         "< -2%" = Pr_0.02,
         "< -3%" = Pr_0.03) %>%
  # Make it tidy for ggplot
  pivot_longer(
    cols = "<   0%":last_col(),
    names_to = "Risk Difference", values_to = "Probabilities"
  ) %>%
  mutate(`Risk Difference` = factor(`Risk Difference`,
      levels = c(
        "<   0%",
        "< -1%",
        "< -2%",
        "< -3%"
        )
    )) %>% 
  ggplot(aes(x = 100*Baseline_risk, y = 100*Probabilities))+
  geom_line(aes(color = `Risk Difference`), size = 1.15) +
  
  # https://github.com/jakelawlor/PNWColors#building-palettes
  scale_color_manual(values= pnw_palette(name="Starfish",n=4)) +
  
  # Dashed line corresponding to the fixed baseline risk used in the primary
  # analyses
  geom_vline(xintercept = benefit_invasive_discharge[[21,1]]*100, linetype = 2) +
  scale_x_continuous("Baseline Risk (%)",
                     seq((benefit_invasive_discharge[[6,1]]*100),
                         (benefit_invasive_discharge[[41,1]]*100),
                         7)) +
  scale_y_continuous(" ",
                     seq(0, 100, 10))+
  coord_cartesian(x = c(2, 36),
                  y = c(0, 100)) +
  
  theme(legend.key = element_blank(),
        plot.title.position = 'plot',
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 13.5),
        axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 10),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_blank(),
        panel.grid.major.x = element_line(color = "gray80", size = 0.3),
        panel.grid.major.y = element_line(color = "gray80", size = 0.3))
```

```{r, fig.width = 10, fig.height = 10, fig.cap = "Sensitivity analyses using multiple different baseline risks for subgroups on use of corticosteroids. Each line represents the posterior probability of benefit  for a specific cutoff, such as risk difference greater or equal to 0%, 1%, 2% and 5%. Vertical dashed lines represent the respective baseline risk (Table 1) used in other analyses. Panel A shows results for patients not using corticosteroids; Panel B shows results for patients using corticosteroids. Panel C shows results for simple oxygen only; Panel D shows results for non-invasive ventilation; Panel E shows results for invasive mechanical ventilation."}
(p1 + p2) / (p3 + p4 + p5) +
  plot_annotation(tag_levels = 'A') +
  plot_layout(guides = "collect") &
  theme(legend.title = element_text(size = 13),
        legend.text = element_text(size = 14))

# ggsave(width = 10,
#        height = 10, 
#        here("final_analyses", "output", "plots", "appendix", # File path
#                   "SFigure8_discharge_figure4.pdf")) # File name
```

## Tables

Next, we are going to put in tables what are the minimum + maximum "Posterior
Probability of Benefit" and their corresponding "Baseline Risk" for each RD
cutoff.

```{r}
# Create function to make tables

values = tibble(Values = c("Min", "Max"))
multiply100 = function(x){x*100}

tables_fun = function(data){ # Data object
  
t1 = benefit_not_using_discharge %>%
  # make it tidy to use filter()
  pivot_longer(
    cols = Pr_0:last_col(),
    names_to = "Cutoff", values_to = "Pr of Benefit"
  ) %>% 
  # filter by Pr of Benefit >= 0%
  filter(Cutoff == "Pr_0") %>%
  # Multiply by 100
  mutate(Baseline_risk = Baseline_risk*100,
         `Pr of Benefit` = `Pr of Benefit`*100) %>% 
  # round the probability of benefit
  mutate(`Pr of Benefit` = round(`Pr of Benefit`, 2)) %>% 
  # select rows with minimum and maximum Pr of Benefit value
  slice(which.min(`Pr of Benefit`),
        which.max(`Pr of Benefit`)) %>%
  # Add new colum with "Min" and "Max"
  bind_cols(values) %>% 
  # Re-arrange the order of columns
  select(Cutoff, Values, Baseline_risk, "Pr of Benefit") %>%
  # Reverse back to wide format
  pivot_wider(names_from = "Values", values_from = Baseline_risk:`Pr of Benefit`) %>% 
  # Rename columns
  rename("min(Baseline Risk)" = Baseline_risk_Min,
         "max(Baseline Risk)" = Baseline_risk_Max,
         "min(Pr of Benefit)" = `Pr of Benefit_Min`,
         "max(Pr of Benefit)" = `Pr of Benefit_Max`) %>% 
  # Reorder
  select(Cutoff,
         "min(Pr of Benefit)", "min(Baseline Risk)",
         "max(Pr of Benefit)", "max(Baseline Risk)")

t2 = data %>%
  # make it tidy to use filter()
  pivot_longer(
    cols = Pr_0:last_col(),
    names_to = "Cutoff", values_to = "Pr of Benefit"
  ) %>% 
  # filter by Pr of Benefit >= 0%
  filter(Cutoff == "Pr_0.01") %>% 
  # Multiply by 100
  mutate(Baseline_risk = Baseline_risk*100,
         `Pr of Benefit` = `Pr of Benefit`*100) %>% 
  # round the probability of benefit
  mutate(`Pr of Benefit` = round(`Pr of Benefit`, 2)) %>% 
  # select rows with minimum and maximum Pr of Benefit value
  slice(which.min(`Pr of Benefit`),
        which.max(`Pr of Benefit`)) %>%
  # Add new colum with "Min" and "Max"
  bind_cols(values) %>% 
  # Re-arrange the order of columns
  select(Cutoff, Values, Baseline_risk, "Pr of Benefit") %>%
  # Reverse back to wide format
  pivot_wider(names_from = "Values", values_from = Baseline_risk:`Pr of Benefit`) %>% 
  # Rename columns
  rename("min(Baseline Risk)" = Baseline_risk_Min,
         "max(Baseline Risk)" = Baseline_risk_Max,
         "min(Pr of Benefit)" = `Pr of Benefit_Min`,
         "max(Pr of Benefit)" = `Pr of Benefit_Max`) %>% 
  # Reorder
  select(Cutoff,
         "min(Pr of Benefit)", "min(Baseline Risk)",
         "max(Pr of Benefit)", "max(Baseline Risk)")

t3 = data %>%
  # make it tidy to use filter()
  pivot_longer(
    cols = Pr_0:last_col(),
    names_to = "Cutoff", values_to = "Pr of Benefit"
  ) %>% 
  # filter by Pr of Benefit >= 0%
  filter(Cutoff == "Pr_0.02") %>% 
  # Multiply by 100
  mutate(Baseline_risk = Baseline_risk*100,
         `Pr of Benefit` = `Pr of Benefit`*100) %>% 
  # round the probability of benefit
  mutate(`Pr of Benefit` = round(`Pr of Benefit`, 2)) %>% 
  # select rows with minimum and maximum Pr of Benefit value
  slice(which.min(`Pr of Benefit`),
        which.max(`Pr of Benefit`)) %>%
  # Add new colum with "Min" and "Max"
  bind_cols(values) %>% 
  # Re-arrange the order of columns
  select(Cutoff, Values, Baseline_risk, "Pr of Benefit") %>%
  # Reverse back to wide format
  pivot_wider(names_from = "Values", values_from = Baseline_risk:`Pr of Benefit`) %>% 
  # Rename columns
  rename("min(Baseline Risk)" = Baseline_risk_Min,
         "max(Baseline Risk)" = Baseline_risk_Max,
         "min(Pr of Benefit)" = `Pr of Benefit_Min`,
         "max(Pr of Benefit)" = `Pr of Benefit_Max`) %>% 
  #Reorder
  select(Cutoff,
         "min(Pr of Benefit)", "min(Baseline Risk)",
         "max(Pr of Benefit)", "max(Baseline Risk)")

t4 = data %>%
  # make it tidy to use filter()
  pivot_longer(
    cols = Pr_0:last_col(),
    names_to = "Cutoff", values_to = "Pr of Benefit"
  ) %>% 
  # filter by Pr of Benefit >= 0%
  filter(Cutoff == "Pr_0.03") %>% 
  # Multiply by 100
  mutate(Baseline_risk = Baseline_risk*100,
         `Pr of Benefit` = `Pr of Benefit`*100) %>% 
  # round the probability of benefit
  mutate(`Pr of Benefit` = round(`Pr of Benefit`, 2)) %>% 
  # select rows with minimum and maximum Pr of Benefit value
  slice(which.min(`Pr of Benefit`),
        which.max(`Pr of Benefit`)) %>%
  # Add new colum with "Min" and "Max"
  bind_cols(values) %>% 
  # Re-arrange the order of columns
  select(Cutoff, Values, Baseline_risk, "Pr of Benefit") %>%
  # Reverse back to wide format
  pivot_wider(names_from = "Values", values_from = Baseline_risk:`Pr of Benefit`) %>% 
  # Rename columns
  rename("min(Baseline Risk)" = Baseline_risk_Min,
         "max(Baseline Risk)" = Baseline_risk_Max,
         "min(Pr of Benefit)" = `Pr of Benefit_Min`,
         "max(Pr of Benefit)" = `Pr of Benefit_Max`) %>% 
  # Reorder
  select(Cutoff,
         "min(Pr of Benefit)", "min(Baseline Risk)",
         "max(Pr of Benefit)", "max(Baseline Risk)")

tt = bind_rows(t1,t2)
tt = bind_rows(tt,t3)
tt = bind_rows(tt,t4) %>% 
  kbl(booktabs = T, align = 'c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F)

return(tt)
}
```

### Not using corticosteroids

```{r}
tables_fun(benefit_not_using_discharge)
```

### Using corticosteroids

```{r}
tables_fun(benefit_using_discharge)
```

### Simple oxygen only

```{r}
tables_fun(benefit_simple_discharge)
```

### Non-invasive ventilation

```{r}
tables_fun(benefit_noninvasive_discharge)
```

### Invasive mechanical ventilation

```{r}
tables_fun(
  benefit_invasive_discharge %>% 
  # Remove negative/zero baseline risks
  slice(6:41)
  )
```

